### 2025-01-03 paper/main.tex
added structure

\documentclass{article}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{LoRA}
Among the different techniques for parameter-efficient fine-tuning of LLMs, one of the most relevant approaches of the last years has been LoRA (Low-Rank Adaptation of Large Language Models) \cite{hu2021lora}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ZKML}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{ZKLoRA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Concluding Remarks}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}

### 2025-01-03 paper/main.tex
updated paper

@@
 \subsection{LoRA}
-Among the different techniques for parameter-efficient fine-tuning of LLMs, one of the most relevant approaches of the last years has been LoRA (Low-Rank Adaptation of Large Language Models) \cite{hu2021lora}.
+Among the different techniques for parameter-efficient fine-tuning of LLMs, one of the most relevant approaches of the last years has been LoRA (Low-Rank Adaptation of Large Language Models) \cite{hu2022lora}.
+The idea behind LoRA is
 

### 2025-01-03 sample_script.py
Add stats to proof generation and proof verification (#16)
* moved verify_proof

* updated .gitignore

* batch verification

* updated gitignore

* added comments and refactor

* deleted unnecesary models

* uncommented main

* measured times

* fix

* private model

* adding csv writing

* return instead of csv

* update

* added time to verification

* refactor

* added params count

* fix

* stats

* updated gitignore

* one run

* removes the proving key after use

* fix verification batched times (#17)

* added base model and lora model names

* last run

---------

Co-authored-by: ppotas

@@ -4,16 +4,23 @@ import asyncio
 from transformers import AutoModelForCausalLM, AutoTokenizer
 from peft import PeftModel
 
+import os
+import csv
+
 
 def main():
+    base_model_name = "distilgpt2"
+    #base_model_name = "openai-community/gpt2"
+    lora_model_name = "q1e123/peft-starcoder-lora-a100"
+    #lora_model_name = "palsp/gpt2-lora"
     # 1) Load base & LoRA model
-    base_model = AutoModelForCausalLM.from_pretrained("distilgpt2")
+    base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
     lora_model = PeftModel.from_pretrained(
-        base_model, "q1e123/peft-starcoder-lora-a100"
+        base_model, lora_model_name
     )
     lora_model.eval()
 
-    tokenizer = AutoTokenizer.from_pretrained("distilgpt2")
+    tokenizer = AutoTokenizer.from_pretrained(base_model_name)
 
     # multiple text
     texts = ["Hello from LoRA", "And another test", "One more line..."]
@@ -25,25 +32,67 @@ def main():
         tokenizer=tokenizer,
         input_texts=texts,  # pass list of strings
         output_dir="lora_onnx_params",
-        json_dir="intermediate_activations",
-        submodule_key="attn.c_attn"
+        json_dir="intermediate_activations"
     )
+
+    csv_path = "proof_metrics.csv"
+    columns = [
+        "base_model", "lora", "number_of_loras", "total_params", "avg_params",
+        "total_settings", "total_witness", "total_prove", 
+        "avg_settings", "avg_witness", "avg_prove",
+        "total_verify", "avg_verify"
+    ]
+
+    if not os.path.exists(csv_path):
+        with open(csv_path, 'w', newline='') as f:
+            writer = csv.writer(f)
+            writer.writerow(columns)
 
     # 3) Generate proofs for each ONNX+JSON pair
     # We'll store circuit artifacts, keys, proofs, etc., in "proof_artifacts".
     # Only the submodules named 'attn.c_attn' will appear in lora_onnx_params + intermediate_activations
     # because that's what we filtered in step 2.
-    asyncio.run(
-        generate_proofs_async(
-            onnx_dir="lora_onnx_params",
-            json_dir="intermediate_activations",
-            output_dir="proof_artifacts",
+    total_settings_time, total_witness_time, total_prove_time, total_params, count_onnx_files = (
+        asyncio.run(
+            generate_proofs_async(
[…]

### 2025-01-03 zklora/generate_proofs.py

@@ -55,12 +55,14 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
         proof_dir (str): Directory containing proof artifacts (proofs, verification keys, etc.)
 
     Returns:
-        None: Prints verification results for each proof to stdout
+        tuple[float, int]: Total time spent verifying proofs, number of proofs verified
     """
     onnx_files = glob.glob(os.path.join(onnx_dir, "*.onnx"))
     if not onnx_files:
         print(f"No ONNX files found in {onnx_dir}.")
-        return
+        return 0.0, 0  # or return None
+
+    total_verify_time = 0.0
 
     for onnx_path in onnx_files:
         base_name = os.path.splitext(os.path.basename(onnx_path))[0]
@@ -76,19 +78,28 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
             witness_file,
             proof_file,
         ) = names
+        
         print(f"Verifying proof for {base_name}...")
         start_time = time.time()
         verify_ok = ezkl.verify(proof_file, settings_file, vk_file, srs_file)
         end_time = time.time()
-        print(f"Verification took {end_time - start_time:.2f} seconds")
+        
+        duration = end_time - start_time
+        total_verify_time += duration
+        print(f"Verification took {duration:.2f} seconds")
+        
         if verify_ok:
             print(f"Proof verified successfully for {base_name}!\n")
         else:
             print(f"Verification failed for {base_name}.\n")
+    
+    return total_verify_time, len(onnx_files)
 
 
 async def generate_proofs_async(
-    onnx_dir: str, json_dir: str, output_dir: str = ".", do_verify: bool = True
+    onnx_dir: str,
+    json_dir: str,
+    output_dir: str = "."
 ):
     """
     Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
@@ -101,6 +112,17 @@ async def generate_proofs_async(
     Since this function is fully async, you can call it once with:
       asyncio.run(generate_proofs_async(...))
     without hitting "no running event loop" in a loop.
+
+    ## Args:
+        onnx_dir (str): Directory containing ONNX model files
+        json_dir (str): Directory containing input JSON files
+        output_dir (str): Directory to store proof artifacts (default: current directory)
+
+    ## Returns:
+        - total_settings_time (float): Total time spent on settings/setup
+        - total_witness_time (float): Total time spent generating witnesses
[…]

### 2025-01-03 zklora/onnx_json_preparation.py
refactor nested functions

@@ -59,6 +59,55 @@ class LoraApplyOneRow(nn.Module):
         return out_2d
 
 
+def make_lora_hook(mod_name, activation_map):
+    """
+    Creates a forward hook function for LoRA modules that stores activations.
+    
+    :param mod_name: Name of the module to hook
+    :param activation_map: Dictionary to store activations
+    :return: Hook function
+    """
+    def hook(mod, layer_inputs, layer_output):
+        if not layer_inputs:
+            return
+        x = layer_inputs[0]  # shape: (batch, seq_len, hidden_dim)
+        print(f"shape in hook ({mod_name}):", x.size())
+        activation_map[mod_name] = x.detach().cpu().numpy()
+
+    return hook
+
+
+def register_lora_hooks(model, activation_map, submodule_key=None):
+    """
+    Recursively finds LoRA submodules and registers forward hooks.
+    
+    :param model: The model to register hooks on
+    :param activation_map: Dictionary to store activations
+    :param submodule_key: Optional key to filter submodules
+    :return: True if any wte/wpe warnings were issued
+    """
+    issued_wte_warning = False
+    
+    for full_name, module in model.named_modules():
+        # Check if this submodule has LoRA
+        if hasattr(module, "lora_A") and hasattr(module, "lora_B"):
+            # Skip embedding submodules
+            if "wte" in full_name or "wpe" in full_name:
+                if not issued_wte_warning:
+                    print(f"WARNING: Found LoRA submodule '{full_name}' (wte/wpe). Skipping hooking embeddings.")
+                    issued_wte_warning = True
+                continue
+
+            # If user wants to filter e.g. "attn.c_attn"
+            if submodule_key and submodule_key not in full_name:
+                continue
+
+            print(f"Registering hook on LoRA submodule: {full_name}")
+            module.register_forward_hook(make_lora_hook(full_name, activation_map))
+    
+    return issued_wte_warning
+
+
 def export_lora_submodules(
     model: PeftModel,
     tokenizer: PreTrainedTokenizer,
@@ -74,9 +123,6 @@ def export_lora_submodules(
        - Inside that submodule's forward pass, it reshapes back to (batch, seq_len, hidden_dim).
     4) Writes a JSON file containing a single row of floats ( shape => (1, total_size) ).
 
-    This function alone does not generate proofs; it only creates the ONNX/JSON pairs.
-    You can run your separate proof-generation code (like `generate_proofs_async`) on them.
-
[…]

### 2025-01-03 zklora/onnx_json_preparation.py
lint

@@ -62,11 +62,12 @@ class LoraApplyOneRow(nn.Module):
 def make_lora_hook(mod_name, activation_map):
     """
     Creates a forward hook function for LoRA modules that stores activations.
-    
+
     :param mod_name: Name of the module to hook
     :param activation_map: Dictionary to store activations
     :return: Hook function
     """
+
     def hook(mod, layer_inputs, layer_output):
         if not layer_inputs:
             return
@@ -80,21 +81,23 @@ def make_lora_hook(mod_name, activation_map):
 def register_lora_hooks(model, activation_map, submodule_key=None):
     """
     Recursively finds LoRA submodules and registers forward hooks.
-    
+
     :param model: The model to register hooks on
     :param activation_map: Dictionary to store activations
     :param submodule_key: Optional key to filter submodules
     :return: True if any wte/wpe warnings were issued
     """
     issued_wte_warning = False
-    
+
     for full_name, module in model.named_modules():
         # Check if this submodule has LoRA
         if hasattr(module, "lora_A") and hasattr(module, "lora_B"):
             # Skip embedding submodules
             if "wte" in full_name or "wpe" in full_name:
                 if not issued_wte_warning:
-                    print(f"WARNING: Found LoRA submodule '{full_name}' (wte/wpe). Skipping hooking embeddings.")
+                    print(
+                        f"WARNING: Found LoRA submodule '{full_name}' (wte/wpe). Skipping hooking embeddings."
+                    )
                     issued_wte_warning = True
                 continue
 
@@ -104,7 +107,7 @@ def register_lora_hooks(model, activation_map, submodule_key=None):
 
             print(f"Registering hook on LoRA submodule: {full_name}")
             module.register_forward_hook(make_lora_hook(full_name, activation_map))
-    
+
     return issued_wte_warning
 
 
@@ -155,7 +158,9 @@ def export_lora_submodules(
 
     # If no sub-layer activations were captured
     if len(activation_map) == 0:
-        print("No LoRA sub-layer activations captured. Possibly no triggers for these inputs.")
+        print(
+            "No LoRA sub-layer activations captured. Possibly no triggers for these inputs."
+        )
         return
 
     # For each submodule hooking
@@ -251,40 +256,3 @@ def export_lora_submodules(
 
         print(f"Exported ONNX for {full_name} -> {onnx_path}")
[…]

### 2025-01-03 zklora/generate_proofs.py
deleted unnecesary if-main

@@ -6,17 +6,17 @@ import time
 import numpy as np
 import json
 import onnxruntime
-import asyncio
+
 
 def get_filenames(proof_dir: str, base_name: str):
     """
     Retrieves paths for all required proof-related files given a directory and base name.
 
-    Args:
+    ## Args:
         proof_dir (str): Directory containing the proof artifacts
         base_name (str): Base name of the files (without extension)
 
-    Returns:
+    ## Returns:
         tuple | None: A 7-tuple containing paths to:
             - circuit file (.ezkl)
             - settings file (_settings.json)
@@ -50,11 +50,11 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
     """
     Batch verifies proofs for all ONNX models in the specified directory.
 
-    Args:
+    ## Args:
         onnx_dir (str): Directory containing ONNX model files
         proof_dir (str): Directory containing proof artifacts (proofs, verification keys, etc.)
 
-    Returns:
+    ## Returns:
         tuple[float, int]: Total time spent verifying proofs, number of proofs verified
     """
     onnx_files = glob.glob(os.path.join(onnx_dir, "*.onnx"))
@@ -78,39 +78,35 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
             witness_file,
             proof_file,
         ) = names
-        
+
         print(f"Verifying proof for {base_name}...")
         start_time = time.time()
         verify_ok = ezkl.verify(proof_file, settings_file, vk_file, srs_file)
         end_time = time.time()
-        
+
         duration = end_time - start_time
         total_verify_time += duration
         print(f"Verification took {duration:.2f} seconds")
-        
+
         if verify_ok:
             print(f"Proof verified successfully for {base_name}!\n")
         else:
             print(f"Verification failed for {base_name}.\n")
-    
+
     return total_verify_time, len(onnx_files)
 
 
-async def generate_proofs_async(
-    onnx_dir: str,
-    json_dir: str,
-    output_dir: str = "."
-):
+async def generate_proofs_async(onnx_dir: str, json_dir: str, output_dir: str = "."):
     """
     Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
     For each matching pair, runs:
-      1) gen_settings + compile_circuit
-      2) gen_srs + setup
-      3) gen_witness (async)
[…]

### 2025-01-06 zklora/lora_onnx_exporter.py
refactor

@@ -1,10 +1,12 @@
-import os
 import json
+import os
+from typing import List
+
+import numpy as np
 import torch
 import torch.nn as nn
-import numpy as np
 from peft import PeftModel
-from transformers import PreTrainedTokenizer, AutoTokenizer, AutoModelForCausalLM
+from transformers import PreTrainedTokenizer
 
 
 # A helper to fix shapes for A, B

### 2025-01-06 zklora/zk_proof_generator.py

@@ -1,14 +1,15 @@
 import os
 import glob
-import onnx
-import ezkl
-import time
-import numpy as np
 import json
-import onnxruntime
+import time
 import asyncio
 
-def get_filenames(proof_dir: str, base_name: str):
+import numpy as np
+import onnx
+import onnxruntime
+import ezkl
+
+def resolve_proof_paths(proof_dir: str, base_name: str) -> tuple[str, str, str, str, str, str, str] | None:
     """
     Retrieves paths for all required proof-related files given a directory and base name.
 
@@ -46,7 +47,7 @@ def get_filenames(proof_dir: str, base_name: str):
     )
 
 
-def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
+def batch_verify_proofs(onnx_dir: str, proof_dir: str) -> tuple[float, int]:
     """
     Batch verifies proofs for all ONNX models in the specified directory.
 
@@ -66,18 +67,11 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
 
     for onnx_path in onnx_files:
         base_name = os.path.splitext(os.path.basename(onnx_path))[0]
-        names = get_filenames(proof_dir, base_name)
+        names = resolve_proof_paths(proof_dir, base_name)
         if names is None:
             continue
-        (
-            circuit_name,
-            settings_file,
-            srs_file,
-            vk_file,
-            pk_file,
-            witness_file,
-            proof_file,
-        ) = names
+        # Only unpack the variables we need
+        _, settings_file, srs_file, vk_file, _, _, proof_file = names
         
         print(f"Verifying proof for {base_name}...")
         start_time = time.time()
@@ -96,11 +90,11 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
     return total_verify_time, len(onnx_files)
 
 
-async def generate_proofs_async(
+async def generate_proofs(
     onnx_dir: str,
     json_dir: str,
     output_dir: str = "."
-):
+) -> tuple[float, float, float, int, int] | None:
     """
     Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
     For each matching pair, runs:
@@ -153,7 +147,7 @@ async def generate_proofs_async(
         print(f"Number of parameters: {param_count:,}")
         total_params += param_count
 
-        names = get_filenames(output_dir, base_name)
+        names = resolve_proof_paths(output_dir, base_name)
         if names is None:
[…]

### 2025-01-06 zklora/zk_proof_generator.py
more refactor

@@ -3,47 +3,34 @@ import glob
 import json
 import time
 import asyncio
+from typing import NamedTuple
 
 import numpy as np
 import onnx
 import onnxruntime
 import ezkl
 
-def resolve_proof_paths(proof_dir: str, base_name: str) -> tuple[str, str, str, str, str, str, str] | None:
+class ProofPaths(NamedTuple):
+    circuit: str
+    settings: str
+    srs: str
+    verification_key: str
+    proving_key: str
+    witness: str
+    proof: str
+
+def resolve_proof_paths(proof_dir: str, base_name: str) -> ProofPaths | None:
     """
     Retrieves paths for all required proof-related files given a directory and base name.
-
-    Args:
-        proof_dir (str): Directory containing the proof artifacts
-        base_name (str): Base name of the files (without extension)
-
-    Returns:
-        tuple | None: A 7-tuple containing paths to:
-            - circuit file (.ezkl)
-            - settings file (_settings.json)
-            - SRS file (kzg.srs)
-            - verification key file (.vk)
-            - proving key file (.pk)
-            - witness file (_witness.json)
-            - proof file (.pf)
-            Returns None if any required file is missing.
     """
-    circuit_name = os.path.join(proof_dir, f"{base_name}.ezkl")
-    settings_file = os.path.join(proof_dir, f"{base_name}_settings.json")
-    srs_file = os.path.join(proof_dir, "kzg.srs")
-    vk_file = os.path.join(proof_dir, f"{base_name}.vk")
-    pk_file = os.path.join(proof_dir, f"{base_name}.pk")
-    witness_file = os.path.join(proof_dir, f"{base_name}_witness.json")
-    proof_file = os.path.join(proof_dir, f"{base_name}.pf")
-
-    return (
-        circuit_name,
-        settings_file,
-        srs_file,
-        vk_file,
-        pk_file,
-        witness_file,
-        proof_file,
+    return ProofPaths(
+        circuit=os.path.join(proof_dir, f"{base_name}.ezkl"),
+        settings=os.path.join(proof_dir, f"{base_name}_settings.json"),
+        srs=os.path.join(proof_dir, "kzg.srs"),
+        verification_key=os.path.join(proof_dir, f"{base_name}.vk"),
+        proving_key=os.path.join(proof_dir, f"{base_name}.pk"),
+        witness=os.path.join(proof_dir, f"{base_name}_witness.json"),
+        proof=os.path.join(proof_dir, f"{base_name}.pf")
     )
 
 
[…]

### 2025-01-06 zklora/lora_onnx_exporter.py
more refactor

@@ -10,7 +10,7 @@ from transformers import PreTrainedTokenizer
 
 
 # A helper to fix shapes for A, B
-def fix_lora_shapes(A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray):
+def normalize_lora_matrices(A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray) -> tuple[torch.Tensor, torch.Tensor, int, int, int]:
     """
     x_data shape => (batch, seq_len, hidden_dim).
     We ensure A => [hidden_dim, r], B => [r, out_dim].
@@ -37,7 +37,7 @@ def fix_lora_shapes(A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray):
     return A, B, in_dim, r, out_dim
 
 
-class LoraApplyOneRow(nn.Module):
+class LoraShapeTransformer(nn.Module):
     """
     Expects shape (1, batch*seq_len*hidden_dim).
     Internal forward => reshape to (batch, seq_len, hidden_dim).
@@ -51,7 +51,7 @@ class LoraApplyOneRow(nn.Module):
         self.seq_len = seq_len
         self.hidden_dim = hidden_dim
 
-    def forward(self, x_1d):
+    def forward(self, x_1d: torch.Tensor) -> torch.Tensor:
         # x_1d => shape (1, total_size)
         x_3d = x_1d.view(self.batch_size, self.seq_len, self.hidden_dim)
         out_3d = (x_3d @ self.A) @ self.B
@@ -79,12 +79,13 @@ def export_lora_submodules(
     This function alone does not generate proofs; it only creates the ONNX/JSON pairs.
     You can run your separate proof-generation code (like `generate_proofs_async`) on them.
 
-    :param model:         A LoRA-augmented (PEFT) model, in eval mode.
-    :param tokenizer:     A tokenizer (from the same or compatible base model).
-    :param input_texts:   A list of strings for batched input. e.g. ["Hello", "More text", ...]
-    :param output_dir:    Where to save ONNX files.
-    :param json_dir:      Where to save JSON files.
-    :param submodule_key: If set (e.g. "attn.c_attn"), export only submodules containing that key.
+    Args:
+        model: A LoRA-augmented (PEFT) model, in eval mode.
+        tokenizer: A tokenizer (from the same or compatible base model).
+        input_texts: A list of strings for batched input. e.g. ["Hello", "More text", ...]
+        output_dir: Where to save ONNX files.
[…]

### 2025-01-06 zklora/zk_proof_generator.py

@@ -20,9 +20,7 @@ class ProofPaths(NamedTuple):
     proof: str
 
 def resolve_proof_paths(proof_dir: str, base_name: str) -> ProofPaths | None:
-    """
-    Retrieves paths for all required proof-related files given a directory and base name.
-    """
+    """Retrieves paths for all required proof-related files given a directory and base name."""
     return ProofPaths(
         circuit=os.path.join(proof_dir, f"{base_name}.ezkl"),
         settings=os.path.join(proof_dir, f"{base_name}_settings.json"),
@@ -35,12 +33,11 @@ def resolve_proof_paths(proof_dir: str, base_name: str) -> ProofPaths | None:
 
 
 def batch_verify_proofs(onnx_dir: str, proof_dir: str) -> tuple[float, int]:
-    """
-    Batch verifies proofs for all ONNX models in the specified directory.
+    """Batch verifies proofs for all ONNX models in the specified directory.
 
     Args:
-        onnx_dir (str): Directory containing ONNX model files
-        proof_dir (str): Directory containing proof artifacts (proofs, verification keys, etc.)
+        onnx_dir: Directory containing ONNX model files
+        proof_dir: Directory containing proof artifacts (proofs, verification keys, etc.)
 
     Returns:
         tuple[float, int]: Total time spent verifying proofs, number of proofs verified
@@ -82,28 +79,23 @@ async def generate_proofs(
     json_dir: str,
     output_dir: str = "."
 ) -> tuple[float, float, float, int, int] | None:
-    """
-    Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
+    """Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
     For each matching pair, runs:
       1) gen_settings + compile_circuit
       2) gen_srs + setup
       3) gen_witness (async)
       4) prove + optional verify
 
-    Since this function is fully async, you can call it once with:
-      asyncio.run(generate_proofs_async(...))
-    without hitting "no running event loop" in a loop.
+    Args:
+        onnx_dir: Directory containing ONNX model files
+        json_dir: Directory containing input JSON files
+        output_dir: Directory to store proof artifacts (default: current directory)
 
-    ## Args:
-        onnx_dir (str): Directory containing ONNX model files
-        json_dir (str): Directory containing input JSON files
-        output_dir (str): Directory to store proof artifacts (default: current directory)
-
-    ## Returns:
-        - total_settings_time (float): Total time spent on settings/setup
[…]

### 2025-01-06 zklora/generate_proofs.py
added versbose option

@@ -46,7 +46,7 @@ def get_filenames(proof_dir: str, base_name: str):
     )
 
 
-def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
+def verify_proof_batch(onnx_dir: str, proof_dir: str, verbose: bool = False) -> None:
     """
     Batch verifies proofs for all ONNX models in the specified directory.
 
@@ -64,6 +64,8 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
 
     total_verify_time = 0.0
 
+    print(f"Verifying {len(onnx_files)} proofs...")
+
     for onnx_path in onnx_files:
         base_name = os.path.splitext(os.path.basename(onnx_path))[0]
         names = get_filenames(proof_dir, base_name)
@@ -79,20 +81,25 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str) -> None:
             proof_file,
         ) = names
 
-        print(f"Verifying proof for {base_name}...")
+        if verbose:
+            print(f"Verifying proof for {base_name}...")
         start_time = time.time()
         verify_ok = ezkl.verify(proof_file, settings_file, vk_file, srs_file)
         end_time = time.time()
 
         duration = end_time - start_time
         total_verify_time += duration
-        print(f"Verification took {duration:.2f} seconds")
+        if verbose:
+            print(f"Verification took {duration:.2f} seconds")
 
         if verify_ok:
-            print(f"Proof verified successfully for {base_name}!\n")
+            if verbose:
+                print(f"Proof verified successfully for {base_name}!\n")
         else:
-            print(f"Verification failed for {base_name}.\n")
+            if verbose:
+                print(f"Verification failed for {base_name}.\n")
 
+    print(f"Total proofs verified: {len(onnx_files)}")
     return total_verify_time, len(onnx_files)
 
 

### 2025-01-06 sample_script.py
updated

@@ -10,9 +10,7 @@ import csv
 
 def main():
     base_model_name = "distilgpt2"
-    #base_model_name = "openai-community/gpt2"
     lora_model_name = "q1e123/peft-starcoder-lora-a100"
-    #lora_model_name = "palsp/gpt2-lora"
     # 1) Load base & LoRA model
     base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
     lora_model = PeftModel.from_pretrained(

### 2025-01-06 zklora/generate_proofs.py
added default directories

@@ -103,7 +103,7 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str, verbose: bool = False) -> 
     return total_verify_time, len(onnx_files)
 
 
-async def generate_proofs_async(onnx_dir: str, json_dir: str, output_dir: str = "."):
+async def generate_proofs_async(onnx_dir: str = "lora_onnx_params", json_dir: str = "intermediate_activations", output_dir: str = "proof_artifacts"):
     """
     Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
     For each matching pair, runs:

### 2025-01-06 zklora/generate_proofs.py
lint

@@ -103,7 +103,11 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str, verbose: bool = False) -> 
     return total_verify_time, len(onnx_files)
 
 
-async def generate_proofs_async(onnx_dir: str = "lora_onnx_params", json_dir: str = "intermediate_activations", output_dir: str = "proof_artifacts"):
+async def generate_proofs_async(
+    onnx_dir: str = "lora_onnx_params",
+    json_dir: str = "intermediate_activations",
+    output_dir: str = "proof_artifacts",
+):
     """
     Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
     For each matching pair, runs:

### 2025-01-06 zklora/generate_proofs.py
removed dependency on onnx files

@@ -46,7 +46,7 @@ def get_filenames(proof_dir: str, base_name: str):
     )
 
 
-def verify_proof_batch(onnx_dir: str, proof_dir: str, verbose: bool = False) -> None:
+def verify_proof_batch(proof_dir: str, verbose: bool = False) -> None:
     """
     Batch verifies proofs for all ONNX models in the specified directory.
 
@@ -57,17 +57,17 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str, verbose: bool = False) -> 
     ## Returns:
         tuple[float, int]: Total time spent verifying proofs, number of proofs verified
     """
-    onnx_files = glob.glob(os.path.join(onnx_dir, "*.onnx"))
-    if not onnx_files:
-        print(f"No ONNX files found in {onnx_dir}.")
+    proof_files = glob.glob(os.path.join(proof_dir, "*.pf"))
+    if not proof_files:
+        print(f"No proof files found in {proof_dir}.")
         return 0.0, 0  # or return None
 
     total_verify_time = 0.0
 
-    print(f"Verifying {len(onnx_files)} proofs...")
+    print(f"Verifying {len(proof_files)} proofs...")
 
-    for onnx_path in onnx_files:
-        base_name = os.path.splitext(os.path.basename(onnx_path))[0]
+    for proof_path in proof_files:
+        base_name = os.path.splitext(os.path.basename(proof_path))[0]
         names = get_filenames(proof_dir, base_name)
         if names is None:
             continue
@@ -99,8 +99,8 @@ def verify_proof_batch(onnx_dir: str, proof_dir: str, verbose: bool = False) -> 
             if verbose:
                 print(f"Verification failed for {base_name}.\n")
 
-    print(f"Total proofs verified: {len(onnx_files)}")
-    return total_verify_time, len(onnx_files)
+    print(f"Total proofs verified: {len(proof_files)}")
+    return total_verify_time, len(proof_files)
 
 
 async def generate_proofs_async(

### 2025-01-06 sample_script.py
updated

@@ -13,9 +13,7 @@ def main():
     lora_model_name = "q1e123/peft-starcoder-lora-a100"
     # 1) Load base & LoRA model
     base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
-    lora_model = PeftModel.from_pretrained(
-        base_model, lora_model_name
-    )
+    lora_model = PeftModel.from_pretrained(base_model, lora_model_name)
     lora_model.eval()
 
     tokenizer = AutoTokenizer.from_pretrained(base_model_name)
@@ -30,66 +28,79 @@ def main():
         tokenizer=tokenizer,
         input_texts=texts,  # pass list of strings
         output_dir="lora_onnx_params",
-        json_dir="intermediate_activations"
+        json_dir="intermediate_activations",
+        submodule_key="attn.c_attn",
     )
 
     csv_path = "proof_metrics.csv"
     columns = [
-        "base_model", "lora", "number_of_loras", "total_params", "avg_params",
-        "total_settings", "total_witness", "total_prove", 
-        "avg_settings", "avg_witness", "avg_prove",
-        "total_verify", "avg_verify"
+        "base_model",
+        "lora",
+        "number_of_loras",
+        "total_params",
+        "avg_params",
+        "total_settings",
+        "total_witness",
+        "total_prove",
+        "avg_settings",
+        "avg_witness",
+        "avg_prove",
+        "total_verify",
+        "avg_verify",
     ]
-
-    if not os.path.exists(csv_path):
-        with open(csv_path, 'w', newline='') as f:
-            writer = csv.writer(f)
-            writer.writerow(columns)
 
     # 3) Generate proofs for each ONNX+JSON pair
     # We'll store circuit artifacts, keys, proofs, etc., in "proof_artifacts".
     # Only the submodules named 'attn.c_attn' will appear in lora_onnx_params + intermediate_activations
     # because that's what we filtered in step 2.
-    total_settings_time, total_witness_time, total_prove_time, total_params, count_onnx_files = (
-        asyncio.run(
-            generate_proofs_async(
-                onnx_dir="lora_onnx_params",
-                json_dir="intermediate_activations",
-                output_dir="proof_artifacts",
-            )
+    (
+        total_settings_time,
+        total_witness_time,
+        total_prove_time,
+        total_params,
+        count_onnx_files,
+    ) = asyncio.run(
+        generate_proofs_async(
+            onnx_dir="lora_onnx_params",
[…]

### 2025-01-06 zklora/generate_proofs.py
updated comments

@@ -51,8 +51,8 @@ def verify_proof_batch(proof_dir: str, verbose: bool = False) -> None:
     Batch verifies proofs for all ONNX models in the specified directory.
 
     ## Args:
-        onnx_dir (str): Directory containing ONNX model files
         proof_dir (str): Directory containing proof artifacts (proofs, verification keys, etc.)
+        verbose (bool): Whether to print verbose output
 
     ## Returns:
         tuple[float, int]: Total time spent verifying proofs, number of proofs verified

### 2025-01-06 zklora/generate_proofs.py
added verbose option

@@ -107,6 +107,7 @@ async def generate_proofs_async(
     onnx_dir: str = "lora_onnx_params",
     json_dir: str = "intermediate_activations",
     output_dir: str = "proof_artifacts",
+    verbose: bool = False,
 ):
     """
     Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
@@ -124,7 +125,7 @@ async def generate_proofs_async(
         onnx_dir (str): Directory containing ONNX model files
         json_dir (str): Directory containing input JSON files
         output_dir (str): Directory to store proof artifacts (default: current directory)
-
+        verbose (bool): Whether to print verbose output
     ## Returns:
         - total_settings_time (float): Total time spent on settings/setup
         - total_witness_time (float): Total time spent generating witnesses
@@ -139,11 +140,15 @@ async def generate_proofs_async(
         print(f"No ONNX files found in {onnx_dir}.")
         return
 
+    if verbose:
+        print(f"Found {len(onnx_files)} ONNX files in {onnx_dir}.")
+
     total_settings_time = 0
     total_witness_time = 0
     total_prove_time = 0
     count_onnx_files = 0
     total_params = 0
+    print("Processing ONNX files for proof generation...")
     for onnx_path in onnx_files:
         base_name = os.path.splitext(os.path.basename(onnx_path))[0]
         json_path = os.path.join(json_dir, base_name + ".json")
@@ -151,13 +156,15 @@ async def generate_proofs_async(
             print(f"No matching JSON for {onnx_path}, skipping.")
             continue
 
-        print("==========================================")
-        print(f"Preparing to prove with ONNX: {onnx_path}")
-        print(f"Matching JSON: {json_path}")
+        if verbose:
+            print("==========================================")
+            print(f"Preparing to prove with ONNX: {onnx_path}")
+            print(f"Matching JSON: {json_path}")
 
         onnx_model = onnx.load(onnx_path)
         param_count = sum(np.prod(param.dims) for param in onnx_model.graph.initializer)
-        print(f"Number of parameters: {param_count:,}")
+        if verbose:
+            print(f"Number of parameters: {param_count:,}")
         total_params += param_count
 
         names = get_filenames(output_dir, base_name)
@@ -179,7 +186,8 @@ async def generate_proofs_async(
         py_args.param_visibility = "private"
         py_args.logrows = 20
 
-        print("Generating settings & compiling circuit...")
+        if verbose:
+            print("Generating settings & compiling circuit...")
[…]

### 2025-01-06 sample_script.py
fixed compatibility issues

@@ -1,4 +1,4 @@
-from zklora import export_lora_submodules, generate_proofs_async, verify_proof_batch
+from zklora import export_lora_submodules, generate_proofs, batch_verify_proofs
 
 import asyncio
 from transformers import AutoModelForCausalLM, AutoTokenizer
@@ -54,7 +54,7 @@ def main():
     # because that's what we filtered in step 2.
     total_settings_time, total_witness_time, total_prove_time, total_params, count_onnx_files = (
         asyncio.run(
-            generate_proofs_async(
+            generate_proofs(
                 onnx_dir="lora_onnx_params",
                 json_dir="intermediate_activations",
                 output_dir="proof_artifacts",
@@ -62,7 +62,7 @@ def main():
         )
     )
 
-    total_verify_time, count_proofs = verify_proof_batch(
+    total_verify_time, count_proofs = batch_verify_proofs(
         "lora_onnx_params", "proof_artifacts"
     )
 

### 2025-01-06 zklora/zk_proof_generator.py

@@ -3,7 +3,7 @@ import glob
 import json
 import time
 import asyncio
-from typing import NamedTuple
+from typing import NamedTuple, Optional
 
 import numpy as np
 import onnx
@@ -19,7 +19,7 @@ class ProofPaths(NamedTuple):
     witness: str
     proof: str
 
-def resolve_proof_paths(proof_dir: str, base_name: str) -> ProofPaths | None:
+def resolve_proof_paths(proof_dir: str, base_name: str) -> Optional[ProofPaths]:
     """Retrieves paths for all required proof-related files given a directory and base name."""
     return ProofPaths(
         circuit=os.path.join(proof_dir, f"{base_name}.ezkl"),
@@ -78,7 +78,7 @@ async def generate_proofs(
     onnx_dir: str,
     json_dir: str,
     output_dir: str = "."
-) -> tuple[float, float, float, int, int] | None:
+) -> Optional[tuple[float, float, float, int, int]]:
     """Asynchronously scans onnx_dir for .onnx files and json_dir for .json files.
     For each matching pair, runs:
       1) gen_settings + compile_circuit

### 2025-01-06 zklora/lora_onnx_exporter.py
Refactor (#20)
* refactor

* more refactor

* more refactor

* fixed compatibility issues

---------

Co-authored-by: mdvillagra <mdvillagra@gmail.com>

@@ -1,14 +1,16 @@
-import os
 import json
+import os
+from typing import List
+
+import numpy as np
 import torch
 import torch.nn as nn
-import numpy as np
 from peft import PeftModel
-from transformers import PreTrainedTokenizer, AutoTokenizer, AutoModelForCausalLM
+from transformers import PreTrainedTokenizer
 
 
 # A helper to fix shapes for A, B
-def fix_lora_shapes(A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray):
+def normalize_lora_matrices(A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray) -> tuple[torch.Tensor, torch.Tensor, int, int, int]:
     """
     x_data shape => (batch, seq_len, hidden_dim).
     We ensure A => [hidden_dim, r], B => [r, out_dim].
@@ -35,7 +37,7 @@ def fix_lora_shapes(A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray):
     return A, B, in_dim, r, out_dim
 
 
-class LoraApplyOneRow(nn.Module):
+class LoraShapeTransformer(nn.Module):
     """
     Expects shape (1, batch*seq_len*hidden_dim).
     Internal forward => reshape to (batch, seq_len, hidden_dim).
@@ -49,7 +51,7 @@ class LoraApplyOneRow(nn.Module):
         self.seq_len = seq_len
         self.hidden_dim = hidden_dim
 
-    def forward(self, x_1d):
+    def forward(self, x_1d: torch.Tensor) -> torch.Tensor:
         # x_1d => shape (1, total_size)
         x_3d = x_1d.view(self.batch_size, self.seq_len, self.hidden_dim)
         out_3d = (x_3d @ self.A) @ self.B
@@ -77,12 +79,13 @@ def export_lora_submodules(
     This function alone does not generate proofs; it only creates the ONNX/JSON pairs.
     You can run your separate proof-generation code (like `generate_proofs_async`) on them.
 
-    :param model:         A LoRA-augmented (PEFT) model, in eval mode.
-    :param tokenizer:     A tokenizer (from the same or compatible base model).
-    :param input_texts:   A list of strings for batched input. e.g. ["Hello", "More text", ...]
-    :param output_dir:    Where to save ONNX files.
-    :param json_dir:      Where to save JSON files.
-    :param submodule_key: If set (e.g. "attn.c_attn"), export only submodules containing that key.
+    Args:
[…]

### 2025-01-06 zklora/zk_proof_generator.py

@@ -1,58 +1,43 @@
 import os
 import glob
-import onnx
-import ezkl
-import time
-import numpy as np
 import json
-import onnxruntime
+import time
 import asyncio
+from typing import NamedTuple, Optional
 
-def get_filenames(proof_dir: str, base_name: str):
-    """
-    Retrieves paths for all required proof-related files given a directory and base name.
+import numpy as np
+import onnx
+import onnxruntime
+import ezkl
 
-    Args:
-        proof_dir (str): Directory containing the proof artifacts
-        base_name (str): Base name of the files (without extension)
+class ProofPaths(NamedTuple):
+    circuit: str
+    settings: str
+    srs: str
+    verification_key: str
+    proving_key: str
+    witness: str
+    proof: str
 
-    Returns:
-        tuple | None: A 7-tuple containing paths to:
-            - circuit file (.ezkl)
-            - settings file (_settings.json)
-            - SRS file (kzg.srs)
-            - verification key file (.vk)
-            - proving key file (.pk)
-            - witness file (_witness.json)
-            - proof file (.pf)
-            Returns None if any required file is missing.
-    """
-    circuit_name = os.path.join(proof_dir, f"{base_name}.ezkl")
-    settings_file = os.path.join(proof_dir, f"{base_name}_settings.json")
-    srs_file = os.path.join(proof_dir, "kzg.srs")
-    vk_file = os.path.join(proof_dir, f"{base_name}.vk")
-    pk_file = os.path.join(proof_dir, f"{base_name}.pk")
-    witness_file = os.path.join(proof_dir, f"{base_name}_witness.json")
-    proof_file = os.path.join(proof_dir, f"{base_name}.pf")
-
-    return (
-        circuit_name,
-        settings_file,
-        srs_file,
-        vk_file,
-        pk_file,
-        witness_file,
-        proof_file,
+def resolve_proof_paths(proof_dir: str, base_name: str) -> Optional[ProofPaths]:
+    """Retrieves paths for all required proof-related files given a directory and base name."""
+    return ProofPaths(
+        circuit=os.path.join(proof_dir, f"{base_name}.ezkl"),
+        settings=os.path.join(proof_dir, f"{base_name}_settings.json"),
+        srs=os.path.join(proof_dir, "kzg.srs"),
+        verification_key=os.path.join(proof_dir, f"{base_name}.vk"),
[…]

### 2025-01-07 zklora/lora_onnx_exporter.py
type casting in hook

@@ -70,7 +70,7 @@ def make_activation_hook(mod_name: str, activation_map: dict) -> callable:
         if not layer_inputs:
             return
         x = layer_inputs[0]  # shape: (batch, seq_len, hidden_dim)
-        activation_map[mod_name] = x.detach().cpu().numpy()
+        activation_map[mod_name] = x.detach().cpu().float().numpy()
 
     return hook
 

### 2025-01-08 sample_script.py
tested Llama-3.1-8B-Instruct

@@ -8,8 +8,8 @@ import os
 import csv
 
 
-base_model_name = "meta-llama/Llama-3.2-1B"
-lora_model_name = "Chryslerx10/Llama-3.2-1B-finetuned-generalQA-peft-4bit"
+base_model_name = "meta-llama/Llama-3.1-8B-Instruct"
+lora_model_name = "vtriple/Llama-3.1-8B-yara"
 base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
 lora_model = PeftModel.from_pretrained(base_model, lora_model_name)
 lora_model.eval()
@@ -26,6 +26,7 @@ export_lora_submodules(
     tokenizer=tokenizer,
     input_texts=texts,  # pass list of strings
     verbose=True,
+    submodule_key="k_proj",
 )
 
 csv_path = "proof_metrics.csv"

### 2025-01-08 split-inference/split_inference.py
initial split inference code

@@ -1,0 +1,393 @@
+import os
+import time
+import uuid
+import pickle
+import glob
+import threading
+
+import torch
+import torch.nn as nn
+from transformers import (
+    AutoConfig,
+    AutoModelForCausalLM,
+    AutoTokenizer,
+)
+from peft import PeftModel
+
+
+###############################
+# 1) LoRAServer (User A)
+###############################
+class LoRAServer:
+    """
+    Holds a base model + LoRA adapter (loaded from a pretrained checkpoint)
+    and can apply LoRA submodules on request.
+    """
+
+    def __init__(self, base_model_name="distilgpt2", lora_model_id="my-lora-distilgpt2"):
+        self.config = AutoConfig.from_pretrained(base_model_name)
+        base_model = AutoModelForCausalLM.from_config(self.config)
+        base_model.eval()
+
+        # Load LoRA-adapted model from PEFT
+        self.peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
+        self.peft_model.eval()
+
+        # Collect submodule references that have LoRA
+        self.lora_submodules = {}
+        for name, module in self.peft_model.named_modules():
+            # naive check: if any param name has 'lora'
+            if any("lora" in pname.lower() for pname, _ in module.named_parameters()):
+                self.lora_submodules[name] = module
+
+    def list_lora_injection_points(self):
+        return list(self.lora_submodules.keys())
+
+    def apply_lora(self, submodule_name: str, input_tensor: torch.Tensor) -> torch.Tensor:
+        if submodule_name not in self.lora_submodules:
+            raise ValueError(f"No LoRA submodule named '{submodule_name}'")
+        with torch.no_grad():
+            out = self.lora_submodules[submodule_name](input_tensor)
+        return out
+
+
+###############################
+# 2) UserAListener (Thread)
+###############################
+class UserAListener(threading.Thread):
+    """
+    Runs in a background thread, continuously scanning for request_*.pkl files.
+    When found, processes them via LoRAServer and writes response_*.pkl.
+
+    We also handle a special "init_request" to provide injection points.
+    """
+
+    def __init__(self, 
+                 lora_server: LoRAServer, 
+                 comm_folder="./temp_communication", 
+                 stop_event=None):
+        super().__init__()
+        self.lora_server = lora_server
+        self.comm_folder = comm_folder
+        os.makedirs(self.comm_folder, exist_ok=True)
+        self.stop_event = stop_event or threading.Event()
+
[…]

### 2025-01-08 split-inference/split_inference.py
fix submodule name mismatch

@@ -7,43 +7,65 @@ import threading
 
 import torch
 import torch.nn as nn
-from transformers import (
-    AutoConfig,
-    AutoModelForCausalLM,
-    AutoTokenizer,
-)
+from transformers import AutoConfig, AutoModelForCausalLM, AutoTokenizer
 from peft import PeftModel
 
 
-###############################
-# 1) LoRAServer (User A)
-###############################
+###################################
+# 1) Utility function for name-fixing
+###################################
+def strip_base_prefix(name: str) -> str:
+    """
+    If submodule name starts with 'base_model.model.', remove that prefix
+    so that it matches the underlying GPT2 submodule naming.
+    Example:
+      'base_model.model.transformer.h.0.attn.c_attn'
+      -> 'transformer.h.0.attn.c_attn'
+    """
+    prefix = "base_model.model."
+    if name.startswith(prefix):
+        return name[len(prefix):]  # remove the prefix
+    return name
+
+
+###################################
+# 2) LoRAServer (User A)
+###################################
 class LoRAServer:
     """
-    Holds a base model + LoRA adapter (loaded from a pretrained checkpoint)
-    and can apply LoRA submodules on request.
+    Holds a base model + LoRA adapter from PEFT and can apply LoRA submodules on request.
     """
 
     def __init__(self, base_model_name="distilgpt2", lora_model_id="my-lora-distilgpt2"):
+        # Load base config and model
         self.config = AutoConfig.from_pretrained(base_model_name)
         base_model = AutoModelForCausalLM.from_config(self.config)
         base_model.eval()
 
-        # Load LoRA-adapted model from PEFT
+        # Load LoRA
         self.peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
         self.peft_model.eval()
 
-        # Collect submodule references that have LoRA
+        # Build a dict of LoRA submodules
+        # BUT store them with 'base_model.model.' stripped,
+        # so we effectively have keys like 'transformer.h.0.attn.c_attn'.
         self.lora_submodules = {}
-        for name, module in self.peft_model.named_modules():
-            # naive check: if any param name has 'lora'
+        for raw_name, module in self.peft_model.named_modules():
+            # If we see a param containing 'lora', assume this submodule has LoRA
             if any("lora" in pname.lower() for pname, _ in module.named_parameters()):
-                self.lora_submodules[name] = module
+                fixed_name = strip_base_prefix(raw_name)
[…]

### 2025-01-08 split-inference/a_server.py
separate files for user A/B

@@ -1,0 +1,158 @@
+#!/usr/bin/env python3
+"""
+File: a_server.py
+
+User A's code:
+  - Loads a PEFT LoRAServer (distilgpt2 + LoRA adapter).
+  - Runs a 'UserAListener' thread that continuously scans for request_*.pkl
+    in a shared folder and writes response_*.pkl with results.
+
+Usage Example:
+  python a_server.py --base_model distilgpt2 --lora_model_id my-lora-distilgpt2
+"""
+
+import os
+import time
+import uuid
+import pickle
+import glob
+import threading
+import argparse
+
+import torch
+from transformers import AutoConfig, AutoModelForCausalLM
+from peft import PeftModel
+
+
+def strip_base_prefix(name: str) -> str:
+    """
+    If submodule name starts with 'base_model.model.', remove that prefix
+    so it aligns with the raw GPT2 submodule naming.
+    """
+    prefix = "base_model.model."
+    if name.startswith(prefix):
+        return name[len(prefix):]
+    return name
+
+
+class LoRAServer:
+    """
+    Loads a base model + LoRA adapter via PEFT, and stores submodule references
+    keyed by the *stripped* name (e.g., 'transformer.h.0.attn.c_attn').
+    """
+
+    def __init__(self, base_model_name, lora_model_id):
+        # 1) Load base config/model
+        config = AutoConfig.from_pretrained(base_model_name)
+        base_model = AutoModelForCausalLM.from_config(config)
+        base_model.eval()
+
+        # 2) Load LoRA adapter
+        self.peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
+        self.peft_model.eval()
+
+        # 3) Build submodule dict
+        self.lora_submodules = {}
+        for raw_name, module in self.peft_model.named_modules():
+            if any("lora" in pname.lower() for pname, _ in module.named_parameters()):
+                fixed_name = strip_base_prefix(raw_name)
+                self.lora_submodules[fixed_name] = module
+
+    def list_lora_injection_points(self):
+        return list(self.lora_submodules.keys())
+
+    def apply_lora(self, submodule_name: str, input_tensor: torch.Tensor) -> torch.Tensor:
+        if submodule_name not in self.lora_submodules:
+            raise ValueError(f"No LoRA submodule named '{submodule_name}'")
+        with torch.no_grad():
+            out = self.lora_submodules[submodule_name](input_tensor)
+        return out
+
+
[…]

### 2025-01-08 split-inference/b_server.py

@@ -1,0 +1,184 @@
+#!/usr/bin/env python3
+"""
+File: b_client.py
+
+User B's code:
+  - Loads the base distilgpt2 model (no LoRA).
+  - Asks User A (via file-based requests) for the LoRA injection points.
+  - Monkey-patches the relevant submodules to call A for LoRA transformations.
+  - Then does a forward pass to compute token-level loss on a sample text.
+
+Usage:
+  python b_client.py
+"""
+
+import os
+import time
+import uuid
+import pickle
+import argparse
+
+import torch
+import torch.nn as nn
+from transformers import AutoTokenizer, AutoModelForCausalLM
+
+
+class UserBFileHandler:
+    """
+    Creates request_*.pkl in a shared folder, waits for response_*.pkl from A.
+    """
+
+    def __init__(self, comm_folder="./temp_communication"):
+        self.comm_folder = comm_folder
+        os.makedirs(self.comm_folder, exist_ok=True)
+
+    def send_init_request(self) -> list:
+        request_id = str(uuid.uuid4())[:8]
+        request_path = os.path.join(self.comm_folder, f"request_{request_id}.pkl")
+        data = {
+            "request_id": request_id,
+            "request_type": "init_request",
+        }
+        with open(request_path, "wb") as f:
+            pickle.dump(data, f)
+
+        # Wait for response
+        response_path = os.path.join(self.comm_folder, f"response_{request_id}.pkl")
+        while not os.path.exists(response_path):
+            time.sleep(0.1)
+
+        with open(response_path, "rb") as f:
+            resp_data = pickle.load(f)
+        os.remove(response_path)
+
+        return resp_data["injection_points"]
+
+    def send_lora_request_and_wait(self, submodule_name: str, input_tensor: torch.Tensor) -> torch.Tensor:
+        request_id = str(uuid.uuid4())[:8]
+        req_path = os.path.join(self.comm_folder, f"request_{request_id}.pkl")
+        data = {
+            "request_id": request_id,
+            "request_type": "lora_forward",
+            "submodule_name": submodule_name,
+            "input_array": input_tensor.cpu().numpy(),
+        }
+        with open(req_path, "wb") as f:
+            pickle.dump(data, f)
+
+        # Wait for response
+        resp_path = os.path.join(self.comm_folder, f"response_{request_id}.pkl")
+        while not os.path.exists(resp_path):
+            time.sleep(0.1)
+
[…]

### 2025-01-08 sample_script.py
tested mixtral 8x7b

@@ -8,8 +8,8 @@ import os
 import csv
 
 
-base_model_name = "meta-llama/Llama-3.1-8B-Instruct"
-lora_model_name = "vtriple/Llama-3.1-8B-yara"
+base_model_name = "mistralai/Mixtral-8x7B-Instruct-v0.1"
+lora_model_name = "ruslanmv/Medical-Mixtral-7B-v1.5k"
 base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
 lora_model = PeftModel.from_pretrained(base_model, lora_model_name)
 lora_model.eval()

### 2025-01-09 split-inference/split_inference.py
updated split inference script (still loss discrepency)

@@ -1,317 +1,341 @@
+#!/usr/bin/env python3
+"""
+final_split_inference.py
+
+A concise, minimal script for split inference with:
+ - LoRA'd submodules in c_attn only,
+ - combine_mode=add_delta,
+ - verifying remote_out is smaller than base_out,
+ - printing final cross-entropy vs. direct local LoRA.
+
+Usage:
+  python final_split_inference.py \
+    --base_model distilgpt2 \
+    --lora_model ng0-k1/distilgpt2-finetuned-es \
+    --combine_mode add_delta \
+    --text "Hello world, this is a LoRA test."
+"""
+
+import threading
 import os
+import sys
 import time
 import uuid
 import pickle
 import glob
-import threading
-
+import argparse
+import random
+import numpy as np
 import torch
 import torch.nn as nn
-from transformers import AutoConfig, AutoModelForCausalLM, AutoTokenizer
+
+from transformers import (
+    AutoConfig,
+    AutoModelForCausalLM,
+    AutoTokenizer,
+)
 from peft import PeftModel
 
+###################################
+# Deterministic seed
+###################################
+SEED = 1234
+def set_global_seed(s=1234):
+    random.seed(s)
+    np.random.seed(s)
+    torch.manual_seed(s)
+    if torch.cuda.is_available():
+        torch.cuda.manual_seed_all(s)
 
-###################################
-# 1) Utility function for name-fixing
-###################################
-def strip_base_prefix(name: str) -> str:
-    """
-    If submodule name starts with 'base_model.model.', remove that prefix
-    so that it matches the underlying GPT2 submodule naming.
-    Example:
-      'base_model.model.transformer.h.0.attn.c_attn'
-      -> 'transformer.h.0.attn.c_attn'
-    """
-    prefix = "base_model.model."
-    if name.startswith(prefix):
-        return name[len(prefix):]  # remove the prefix
+set_global_seed(SEED)
+
+def strip_base_prefix(name: str):
+    p = "base_model.model."
+    if name.startswith(p):
+        return name[len(p):]
     return name
 
-
 ###################################
-# 2) LoRAServer (User A)
+# LoRAServer
 ###################################
 class LoRAServer:
-    """
-    Holds a base model + LoRA adapter from PEFT and can apply LoRA submodules on request.
-    """
+    def __init__(self, base_model, lora_model, debug=False):
+        config = AutoConfig.from_pretrained(base_model)
[…]

### 2025-01-09 activations_commit.py
deleted

@@ -1,28 +1,0 @@
-import merkle
-import json
-import numpy as np
-
-def get_merkle_root(activations_path: str) -> str:
-    """
-    Calculate the Merkle root hash of model activations stored in a JSON file.
-    
-    Args:
-        activations_path: Path to JSON file containing model activations under "input_data" key
-        
-    Returns:
-        str: Hexadecimal string of the Merkle root hash, prefixed with "0x"
-    """
-    # Load the intermediate activations from JSON file
-    with open(activations_path, 'r') as f:
-        activations = json.load(f)
-
-    # Convert nested data to numpy array and flatten
-    flattened_np = np.array(activations["input_data"]).reshape(-1)
-    
-    # Get and return the Merkle root hash
-    return merkle.insert_values(flattened_np.tolist())
-
-if __name__ == "__main__":
-    activations_path = "intermediate_activations/base_model_model_lm_head.json"
-    merkle_root = get_merkle_root(activations_path)
-    print("Merkle root:", merkle_root)

### 2025-01-09 compact_proof.py

@@ -1,21 +1,0 @@
-import ezkl
-import asyncio
-
-async def run_ezkl_proof():
-    model_onnx = "lora_onnx_params/base_model_model_transformer_h_2_attn_c_attn.onnx"
-    compiled_path = "model.ezkl"
-    input_data = "intermediate_activations/base_model_model_transformer_h_2_attn_c_attn.json"
-    # e.g. ...
-    ezkl.gen_settings(model_onnx)
-    ezkl.compile_circuit(model_onnx, compiled_path, "settings.json")
-    ezkl.gen_srs("kzg.srs", 20)
-    ezkl.setup(compiled_path, "vk.key", "pk.key", "kzg.srs")
-
-    await ezkl.gen_witness(
-        data=input_data,
-        model=compiled_path,
-        output="witness.json"
-    )
-
-if __name__=="__main__":
-    asyncio.run(run_ezkl_proof())

### 2025-01-09 forward_proof.py

@@ -1,91 +1,0 @@
-import onnx
-import ezkl
-import time
-import numpy as np
-import asyncio
-import json
-import onnxruntime
-
-def flatten_list(nested_list):
-    if not isinstance(nested_list, list):
-        return [nested_list]
-    if len(nested_list) == 0:
-        return []
-    if isinstance(nested_list[0], list):
-        return flatten_list(nested_list[0])
-    return nested_list
-
-async def main():
-    lora_path = "lora_onnx_params/base_model_model_transformer_h_2_attn_c_attn.onnx"
-    lora_ezkl = "model.ezkl"
-    activations_path = "intermediate_activations/base_model_model_transformer_h_2_attn_c_attn.json"
-    
-    onnx_model = onnx.load(lora_path)
-    param_count = sum(np.prod(param.dims) for param in onnx_model.graph.initializer)
-    print(f"Number of parameters in {lora_path}: {param_count:,}")
-
-    #
-    # Setup
-    #
-    py_run_args = ezkl.PyRunArgs()
-    py_run_args.input_visibility = "public"
-    py_run_args.output_visibility = "public"
-    py_run_args.param_visibility = "fixed"
-    py_run_args.logrows = 20
-
-    print("Generating settings...")
-    start_time = time.time()
-    ezkl.gen_settings(lora_path, py_run_args=py_run_args)
-    ezkl.compile_circuit(lora_path, lora_ezkl, "settings.json")
-    ezkl.gen_srs("kzg.srs", py_run_args.logrows)
-    ezkl.setup(lora_ezkl, "vk.key", "pk.key", "kzg.srs")
-    end_time = time.time()
-    print(f"Setup took {end_time - start_time:.2f} seconds")
-
-    #
-    # Prove
-    #
-    # Load the sub-layer activations
-    with open(activations_path, "r") as f:
-        activations_data = json.load(f)
-    
-    print("Raw JSON keys:", activations_data.keys())
-
-    # Convert to float32 array
-    float_data = np.array(activations_data["input_data"], dtype=np.float32)
-    print("Activations shape (from JSON):", float_data.shape)
-
-    # 1) Check if we have any NaN or Inf
-    has_invalid = not np.all(np.isfinite(float_data))
-    print("Any NaN/Inf in data?:", has_invalid)
-    if has_invalid:
-        # fix them
-        float_data = np.nan_to_num(float_data, nan=0.0, posinf=1e5, neginf=-1e5)
-
[…]

### 2025-01-09 simple_test.py

@@ -1,41 +1,0 @@
-import torch
-import torch.nn as nn
-import onnx
-
-class SimpleMultiInputModel(nn.Module):
-    def forward(self, x, A, B):
-        # Perform a computation that depends on all inputs:
-        # x: (B, S, in_dim)
-        # A, B: assume (in_dim, in_dim) for simplicity
-        out = torch.matmul(x, B)     # (B, S, in_dim)
-        out = torch.matmul(out, A)   # (B, S, in_dim)
-        out = out + x.mean()         # depends on x values
-        return out
-
-model = SimpleMultiInputModel().eval()
-
-# Create dummy inputs
-x = torch.randn(1, 5, 768)
-A = torch.randn(768, 768)
-B = torch.randn(768, 768)
-
-onnx_path = "test_multi_input.onnx"
-
-torch.onnx.export(
-    model,
-    (x, A, B),
-    onnx_path,
-    export_params=False,        # do not embed parameters as constants
-    do_constant_folding=False,  # do not fold constants
-    opset_version=11,
-    input_names=["input_x", "input_A", "input_B"],
-    output_names=["output"],
-    dynamic_axes={
-        "input_x": {0: "batch_size", 1: "seq_len"},
-        "output": {0: "batch_size", 1: "seq_len"}
-    }
-)
-
-onnx_model = onnx.load(onnx_path)
-print("ONNX Inputs:", onnx_model.graph.input)
-# Expected: Should see input_x, input_A, input_B as inputs.

### 2025-01-09 validation.py

@@ -1,336 +1,0 @@
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from torchvision import datasets, transforms
-from torch.utils.data import DataLoader
-import torch.onnx
-import onnx
-import ezkl
-import json
-import asyncio
-import onnx2torch
-import time
-
-import warnings
-
-warnings.filterwarnings("ignore")
-
-
-# Define the MLP model
-class MLP(nn.Module):
-    def __init__(self):
-        super(MLP, self).__init__()
-        self.flatten = nn.Flatten()
-        self.layers = nn.Sequential(
-            nn.Linear(28 * 28, 128), nn.ReLU(), nn.Linear(128, 10)
-        )
-
-    def forward(self, x):
-        x = self.flatten(x)
-        return self.layers(x)
-
-
-# Add this new wrapper class after the MLP class
-class MLPWithLoss(nn.Module):
-    def __init__(self, model):
-        super(MLPWithLoss, self).__init__()
-        self.model = model
-
-    def forward(self, x, target):
-        output = self.model(x)
-        loss = (target - output).pow(2).mean()
-        return loss, output  # Return both loss and predictions
-
-
-def train() -> None:
-    # Set device
-    device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
-
-    # Load and preprocess MNIST dataset
-    transform = transforms.Compose(
-        [transforms.ToTensor(), transforms.Normalize((0.1307,), (0.3081,))]
-    )
-
-    train_dataset = datasets.MNIST(
-        "./data", train=True, download=True, transform=transform
-    )
-    test_dataset = datasets.MNIST("./data", train=False, transform=transform)
-
-    train_loader = DataLoader(train_dataset, batch_size=64, shuffle=True)
-    test_loader = DataLoader(test_dataset, batch_size=1000)
-
-    # Initialize the model
-    model = MLP().to(device)
-    criterion = nn.MSELoss()
-    optimizer = optim.Adam(model.parameters(), lr=0.001)
-
-    epochs = 1
-
-    for epoch in range(epochs):
-        model.train()
-        for batch_idx, (data, target) in enumerate(train_loader):
-            data, target = data.to(device), target.to(device)
-            # Convert targets to one-hot encoding for MSE
-            target_one_hot = torch.zeros(target.size(0), 10, device=device)
-            target_one_hot.scatter_(1, target.unsqueeze(1), 1)
-
-            optimizer.zero_grad()
-            output = model(data)
[…]

### 2025-01-09 sample_script.py
Type casting in hook and test (#21)
* type casting in hook

* tested Llama-3.1-8B-Instruct

* tested mixtral 8x7b

* added more loras

* added gpt2

* added distillgpt2 again

@@ -8,8 +8,8 @@ import os
 import csv
 
 
-base_model_name = "meta-llama/Llama-3.2-1B"
-lora_model_name = "Chryslerx10/Llama-3.2-1B-finetuned-generalQA-peft-4bit"
+base_model_name = "mistralai/Mixtral-8x7B-Instruct-v0.1"
+lora_model_name = "ruslanmv/Medical-Mixtral-7B-v1.5k"
 base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
 lora_model = PeftModel.from_pretrained(base_model, lora_model_name)
 lora_model.eval()
@@ -26,6 +26,7 @@ export_lora_submodules(
     tokenizer=tokenizer,
     input_texts=texts,  # pass list of strings
     verbose=True,
+    submodule_key="k_proj",
 )
 
 csv_path = "proof_metrics.csv"

### 2025-01-09 save_onnx_and_json.py
Deleted unnecessary scripts (#23)
* deleted

* added commitments script

@@ -1,223 +1,0 @@
-import os
-import json
-import re
-import numpy as np
-import torch
-import torch.nn as nn
-import onnx
-from torch.onnx import TrainingMode
-from transformers import AutoModelForCausalLM, AutoTokenizer
-from peft import PeftModel
-from typing import Callable
-
-#############################################
-# Configuration
-#############################################
-base_model_name = "distilgpt2"
-lora_model_name = "ng0-k1/distilgpt2-finetuned-es"  # Adjust if different
-output_dir = "lora_onnx_params"
-json_dir = "intermediate_activations"
-params_dir = "lora_params"
-os.makedirs(output_dir, exist_ok=True)
-os.makedirs(json_dir, exist_ok=True)
-os.makedirs(params_dir, exist_ok=True)
-
-# Input text for generating intermediate activations
-input_text = "Hello, world!"
-batch_size = 1
-seq_len = 5   # Adjust if needed, or rely on actual input length
-hidden_dim = 768  # DistilGPT2 hidden size
-
-#############################################
-# Load LoRA model
-#############################################
-base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
-model = PeftModel.from_pretrained(base_model, lora_model_name)
-model.eval()
-
-tokenizer = AutoTokenizer.from_pretrained(base_model_name)
-if tokenizer.pad_token is None:
-    tokenizer.pad_token = tokenizer.eos_token
-input_ids = tokenizer(input_text, return_tensors='pt').input_ids
-
-#############################################
-# Identify LoRA Layers
-#############################################
-lora_layers = []
-for name, module in model.named_modules():
-    if hasattr(module, 'lora_A') and hasattr(module, 'lora_B'):
-        print(name, module)
-        lora_layers.append((name, module))
-
-if not lora_layers:
-    raise ValueError("No LoRA layers found in the model.")
-
-# We'll parse layer index from the name if possible. For DistilGPT2:
-# name might look like: base_model.model.transformer.h.0.attn.c_attn.lora_...
-layer_idx_pattern = re.compile(r"transformer\.h\.(\d+)\.attn\.c_attn")
-
-#############################################
-# Capture intermediate activations x
-# We'll register a hook on each transformer layer to capture its output
-#############################################
-intermediate_activations = {}
-
[…]

### 2025-01-09 save_onnx_json_only_x_input.py

@@ -1,250 +1,0 @@
-#!/usr/bin/env python
-
-import os
-import json
-import argparse
-import numpy as np
-import torch
-import torch.nn as nn
-import onnx
-from torch.onnx import TrainingMode
-from transformers import AutoModelForCausalLM, AutoTokenizer
-from peft import PeftModel
-
-def parse_args():
-    parser = argparse.ArgumentParser(
-        description="Capture LoRA submodule inputs, flatten them, export a flattened ONNX sub-module, and write JSON for EZKL."
-    )
-    parser.add_argument("--base_model", type=str, required=True,
-                        help="Base model name/path (e.g. 'distilgpt2').")
-    parser.add_argument("--lora_model", type=str, required=True,
-                        help="LoRA model name/path (e.g. 'some/lora-adapter').")
-    parser.add_argument("--input_text", type=str, default="Hello, world!",
-                        help="Sample text for capturing sub-layer activations.")
-    parser.add_argument("--output_dir", type=str, default="lora_onnx_params",
-                        help="Directory to save ONNX files.")
-    parser.add_argument("--json_dir", type=str, default="intermediate_activations",
-                        help="Directory to save JSON input files.")
-    parser.add_argument("--submodule_key", type=str, default=None,
-                        help="If provided, only export submodules whose name contains this key.")
-    return parser.parse_args()
-
-def main():
-    args = parse_args()
-
-    base_model_name = args.base_model
-    lora_model_name = args.lora_model
-    input_text = args.input_text
-    output_dir = args.output_dir
-    json_dir = args.json_dir
-    submodule_key = args.submodule_key
-
-    os.makedirs(output_dir, exist_ok=True)
-    os.makedirs(json_dir, exist_ok=True)
-
-    print(f"Loading base model: {base_model_name}")
-    base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
-    print(f"Loading LoRA model: {lora_model_name}")
-    model = PeftModel.from_pretrained(base_model, lora_model_name)
-    model.eval()
-
-    tokenizer = AutoTokenizer.from_pretrained(base_model_name)
-    if tokenizer.pad_token is None:
-        tokenizer.pad_token = tokenizer.eos_token
-
-    # Example input
-    inputs = tokenizer(input_text, return_tensors='pt')
-    input_ids = inputs["input_ids"]
-    print(f"Input IDs shape: {input_ids.shape}")  # e.g. (1, 4) if you have 4 tokens
-
[…]

### 2025-01-10 split-inference/loss_check.py
simple script for computing direct inference loss

@@ -1,0 +1,39 @@
+import torch
+from transformers import AutoTokenizer, AutoModelForCausalLM
+from peft import PeftModel
+
+def compute_loss(model, tokenizer, text: str) -> float:
+    """
+    Compute the cross-entropy loss of 'text' using the given LoRA-PEFT model.
+    """
+    # Tokenize the input
+    inputs = tokenizer(text, return_tensors="pt")
+    input_ids = inputs["input_ids"]
+    labels = input_ids.clone()  # the usual approach for causal LM loss
+
+    # Forward pass with labels => model computes cross-entropy for each token
+    with torch.no_grad():
+        outputs = model(input_ids, labels=labels)
+        loss = outputs.loss  # average cross-entropy over the sequence
+    return loss.item()
+
+def main():
+    # 1) Load the base model
+    base_model_name = "distilgpt2"
+    base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
+    tokenizer = AutoTokenizer.from_pretrained(base_model_name)
+
+    # 2) Load the LoRA PEFT adapter
+    lora_model_id = "ng0-k1/distilgpt2-finetuned-es"
+    peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
+    peft_model.eval()
+
+    # 3) Sample text (Spanish, given the fine-tuned es model)
+    text = "funky chunky monkey"
+
+    # 4) Compute and print the loss
+    loss_value = compute_loss(peft_model, tokenizer, text)
+    print(f"Loss on sample text: {loss_value:.4f}")
+
+if __name__ == "__main__":
+    main()

### 2025-01-10 paper/main.tex
added ivc section

@@
 \documentclass{article}
+
+\usepackage{amsmath,amsgen,latexsym}
+\usepackage{amstext,amssymb,amsfonts}
+
+\usepackage{hyperref}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{ZKML}
+\subsection{Incrementally Verifiable Computation}
+In a decentralized world, trust is a resource that is hard to achieve.
+In decentralized computation, we need to make sure the computation are being done, and are being correctly.
+In a seminal paper by Valiant (2008) \cite{valiant2008incrementally}, it was shown that proofs of knowledge can be used to assert the correct execution of general computations.
+That is, if $M$ is a machine that runs for $t$ steps producing a sequence of configurations $c_0,c_1,\dots,c_t$, then there exist an efficient and effective way to produce a computationally sound proof for the computation $c_0  \xrightarrow{t} c_t$.
+This idea is referred to as Incrementally Verifiable Computation or IVC.
+
+The main goal is IVC is to produce compact, updatable proofs of correctness for a sequence of computations, so that each new step in the computation can be verified on its own while building on the guarantees of the previous steps.
+This technique significantly reduces the verification overhead for long or evolving computations, which is invaluable in scenarios like decentralized networks, outsourced computation, and any application requiring frequent correctness checks.
+
+Kumar et al.
+(2021) \cite{kothapalli2022nova} introduced the proof system NOVA and the idea of recursive proofs, which are proofs that can ``prove the correctness of other proofs.'' Recursive proof composition is key to IVC where each proof attests to the correctness of both a step’s output and the validity of the previous step’s proof.
+
+HyperNova \cite{kothapalli2024hypernova} is a novel recursive argument system optimized for customizable constraint systems (CCS) that generalizes and improves upon prior approaches like Nova.
+It achieves efficiency through a folding scheme where the prover’s cryptographic costs are minimized and achieves zero-knowledge without relying on zkSNARKs.
 

### 2025-01-12 paper/main.tex
add paragraph on zk
1/10 peter paper draft

--- 2025-01-03 paper/main.tex
@@
-\documentclass{article}
+\documentclass[11pt]{article}
+
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\usepackage{booktabs}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{hyperref}
+\usepackage{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{arrows.meta, positioning, calc, fit}
+
+\title{\textbf{zklora: Verifiable Split Inference for Evaluating Private LoRA Weights}}
+\author{Anonymous Authors}
+\date{\today}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\maketitle
+
+\begin{abstract}
+In decentralized computing environments, one party may wish to fine-tune a publicly available base model with Low-Rank Adaptation (LoRA) but keep those adapter weights private, while another party wants to evaluate performance on new data.
+We introduce \texttt{zklora}, a library designed to help the \emph{Base Model User} \emph{verifiably assess} the quality of a private LoRA module for a target task---for instance, to run a validation experiment without directly accessing the private weights.
+By adopting a split inference approach and generating \emph{verifiable computations}, \texttt{zklora} enables the \emph{Base Model User} to confirm that remote LoRA computations are correct, all without seeing the private weights themselves.
+We demonstrate the feasibility of \texttt{zklora} via benchmark experiments, showing that our approach remains computationally viable across various model sizes, with notably fast verification times.
+\end{abstract}
+
 \section{Introduction}
+Large Language Models (LLMs) excel at a variety of tasks but come with significant computational and storage costs \cite{brown2020language, devlin2018bert}. 
+Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by introducing a small number of trainable parameters into the model, drastically reducing memory overhead for fine-tuning \cite{ding2022delta}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preliminaries}
+When two entities, a \emph{LoRA Owner} and a \emph{Base Model User}, collaborate on a shared LLM, they may have conflicting constraints.
+The \emph{LoRA Owner} wants to keep custom LoRA weights private (e.g., for competitive or regulatory reasons), while the \emph{Base Model User} wants to \emph{test} or \emph{validate} these LoRA weights on a target task before deciding whether to deploy them at scale.
+Under normal circumstances, either the LoRA must be fully shared (sacrificing privacy), or the Base Model User must trust the LoRA Owner’s claims about performance with little evidence.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{LoRA}
-Among the different techniques for parameter-efficient fine-tuning of LLMs, one of the most relevant approaches of the last years has been LoRA (Low-Rank Adaptation of Large Language Models) \cite{hu2021lora}.
+In this paper, we present \texttt{zklora}, a library that provides a \emph{verifiable computation} solution for the \emph{Base Model User} to \emph{evaluate} a private LoRA module.
+By orchestrating a split inference, \texttt{zklora} allows the Base Model User to run the base model locally while sending partial activations to the LoRA Owner.
+Crucially, the LoRA Owner returns not only updated activations but also a cryptographic \emph{proof} that the correct LoRA transformation was applied.
+In this way, the Base Model User can confirm the final outputs truly reflect the LoRA module’s capabilities.
+After verifying and measuring results on a validation dataset, the Base Model User can later choose how to adopt the LoRA at larger scale.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{ZKML}
+\section{Related Work}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{ZKLoRA}
+\subsection{Low-Rank Adaptation}
+LoRA \cite{hu2021lora} has emerged as a popular way to efficiently fine-tune LLMs by injecting small, low-rank matrices into specific layers.
+This approach scales well, requiring less GPU memory than full fine-tuning.
+Various frameworks build on LoRA for GPT-2, GPT-Neo, LLaMA, and others \cite{ding2022delta}.
+By confining most updated parameters to low-rank adapter matrices, LoRA drastically reduces memory overhead during fine-tuning.
+As a result, domain-specific LoRA modules can be swapped in or out of the same base model, avoiding the need to retrain or store complete copies of large networks.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Incrementally Verifiable Computation}
+Valiant~\cite{valiant2008incrementally} introduced the notion of Incrementally Verifiable Computation (IVC), which offers updatable, compact proofs of correctness over multi-step computations.
+Nova~\cite{kothapalli2022nova} and HyperNova~\cite{kothapalli2024hypernova} refine these ideas, leveraging folding schemes and zero-knowledge properties to enable scaling of verifiable computations in multi-step neural network inference.
+IVC-based approaches align well with repeated computations needing multiple checkpoints of trust, such as multiple forward passes or partial training loops.
+
+\section{Methodology: zklora for Verifiable Evaluation}
+Our aim is to enable the \emph{Base Model User} to run a \emph{validation experiment} on their local data, incorporating the private LoRA module from the \emph{LoRA Owner}.
+The Base Model User can measure task performance (e.g., cross-entropy loss, accuracy) to decide whether the LoRA meets performance requirements.
+Figure~\ref{fig:toy-mlp-lora} illustrates a simple scenario.
+
+\begin{enumerate}
+    \item \textbf{Base Model Forward Pass (Base Model User).}
+    The \emph{Base Model User} runs layers without LoRA parameters locally, generating partial activations.
+
+    \item \textbf{Forward to LoRA Adapter (Base Model User).}
+    Whenever the next layer includes a LoRA transform, the \emph{Base Model User} sends these partial activations to the \emph{LoRA Owner}, who holds the private LoRA module.
+
+    \item \textbf{LoRA Computation \& Proof Generation (LoRA Owner).}
+    The \emph{LoRA Owner} applies the LoRA transformation to the activations and returns the updated activations alongside a \emph{cryptographic proof} of correctness.
+In our setup, \texttt{zklora} interfaces with \texttt{ezkl} to produce these proofs.
+
+    \item \textbf{Resuming the Forward Pass (Base Model User).}
+    The \emph{Base Model User} injects the updated activations back into the local model state and continues the forward pass.
+
+    \item \textbf{Verification \& Validation (Base Model User).}
+    The \emph{Base Model User} verifies the LoRA proof.
+If valid, the outputs from the combined base + LoRA model are guaranteed to match the LoRA Owner’s claimed computation.
+The Base Model User can now measure final metrics (loss, accuracy, etc.) to assess \emph{quality} on the target task.
+\end{enumerate}
+
+\begin{figure}[ht]
+\centering
+\begin{tikzpicture}[
+    font=\small,
+    >=latex,
+    thick,
+    block/.style={
+      draw,
+      rounded corners,
+      align=center,
+      minimum width=1.8cm,
+      minimum height=0.9cm
+    },
+    dashedblock/.style={
+      draw,
+      dashed,
+      rounded corners,
+      align=center,
+      font=\footnotesize,
+      fill=white,
+      minimum width=1.8cm,
+      minimum height=0.9cm
+    },
+    arrow/.style={->, thick},
+    node distance=2.0cm
+]
+
+\node[block, label=above:\textbf{Input}] (input) {$\mathbf{x}$};
+\node[block, right=2.0cm of input] (W1) {$\mathbf{W}_1$};
+\node[dashedblock, above=1.6cm of W1, label=above:\textbf{LoRA Owner}] (LoRA) {LoRA for Layer 1};
+\node[block, right=2.0cm of W1] (act) {ReLU};
+\node[block, right=2.0cm of act] (W2) {$\mathbf{W}_2$};
+\node[block, label=above:\textbf{Output}, right=2.0cm of W2] (output) {$\mathbf{y}$};
+
+\draw[arrow] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
+\draw[->, dashed] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial activations} (LoRA.south);
+\draw[->, dashed] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
+\draw[arrow] (W1) -- node[above, font=\scriptsize]{$\mathbf{z}'$} (act);
+\draw[arrow] (act) -- node[above, font=\scriptsize]{hidden} (W2);
+\draw[arrow] (W2) -- (output);
+
+\node[draw, rounded corners, thick, color=blue!40!black,
+      fit=(input)(W1)(act)(W2)(output),
+      label={[font=\small, color=blue!40!black]above:\textbf{Base Model User}},
+      inner sep=0.4cm
+] (baseModelFit) {};
+
+\end{tikzpicture}
+\caption{A simplified 2-layer MLP with LoRA on the first layer.
+The Base Model User (blue box) runs most computations locally but calls the LoRA Owner (dashed box) to update partial activations.
+After verifying correctness, the Base Model User can measure final metrics to decide whether to adopt the private LoRA more extensively.}
+\label{fig:toy-mlp-lora}
+\end{figure}
+
+After confirming performance with \texttt{zklora}, the Base Model User can move forward using the LoRA weights with confidence, knowing their underlying quality combined with the base model.
+The core objective with \texttt{zklora} is to \emph{verify} that the private LoRA weights indeed perform as claimed, without revealing them.
+
 \section{Experiments}
+We benchmarked \texttt{zklora} by measuring the creation and verification times for our verifiable computations across multiple base models and private LoRA configurations.
+For each model, we computed a forward pass for a batch of 3 items with sequence length 5.
+Each experiment simulates the workflow where the \emph{Base Model User} uses local data to evaluate the base model + LoRA combination, requesting remote LoRA computations from the \emph{LoRA Owner}. 
+We report total and average proof-generation times (\texttt{total\_prove}, \texttt{avg\_prove}) and verification times (\texttt{total\_verify}, \texttt{avg\_verify}), as well as relevant model parameters.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Concluding Remarks}
+\begin{table}[ht]
+    \centering
+    \small
+    \begin{tabular}{l c c c c c c c}
+    \toprule
+    \textbf{base\_model} & \textbf{\#lora} & \textbf{total\_params} & \textbf{avg\_params} & \textbf{total\_prove} & \textbf{avg\_prove} & \textbf{total\_verify} & \textbf{avg\_verify} \\
+    \midrule
+distilgpt2 & 24 & 589824 & 24576.0 & 759.33 & 31.64 & 16.56 & 0.69 \\
+gpt2 & 48 & 2359296 & 49152.0 & 1675.58 & 34.91 & 32.79 & 0.68 \\
+Llama-3.2-1B & 32 & 851968 & 26624.0 & 991.93 & 31.00 & 24.91 & 0.78 \\
+Llama-3.3-70B-Instr. & 80 & 11796480 & 147456.0 & 3749.76 & 46.87 & 123.11 & 1.54 \\
+Llama-3.1-8B-Instr. & 32 & 5242880 & 163840.0 & 1527.40 & 47.73 & 35.79 & 1.12 \\
+Mixtral-8x7B-Instr. & 32 & 10485760 & 327680.0 & 2357.61 & 73.68 & 44.30 & 1.38 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Benchmark results for \texttt{zklora} showing split inference overhead on various model + LoRA combinations. Times are in seconds.}
+    \label{tab:results}
+\end{table}
+
+As shown in Table~\ref{tab:results}, proof-generation times tend to grow with model size, particularly for 70B-scale systems.
+However, the verification step remains fast, often averaging under two seconds per proof, even at large scales.
+This efficiency is crucial for real-world “trial runs”, allowing the Base Model User to confirm performance on a validation set without incurring prohibitive overhead.
+In larger-scale usage scenarios, once trust in the LoRA module is established, \texttt{zklora} may no longer be needed.
+
+\section{Conclusion}
+\texttt{zklora} enables a \emph{Base Model User} to verify the quality of a private LoRA module without revealing the LoRA weights.
+By pairing split inference with cryptographic proofs, \texttt{zklora} ensures that the user can trust the computed outputs during validation experiments.
+After verifying performance, the Base Model User may adopt any approach they choose to integrate or deploy the private LoRA more widely, since the module has been proven effective.
+Our experiments show this approach is feasible across a range of model sizes, with \emph{fast verification times} minimizing the overhead of a verifiable evaluation phase.
+Future directions include further circuit optimization and exploring multi-owner scenarios, in which multiple private LoRA modules could be composed and verified within the same pipeline.
 
 \bibliographystyle{plain}
-\bibliography{refs}
+\bibliography{references}
 

### 2025-01-12 paper/main.tex
SI to MPI, modified info flow a la distro

@@
 
-\title{\textbf{zklora: Verifiable Split Inference for Evaluating Private LoRA Weights}}
+\title{\textbf{zklora: Verifiable Multi-Party Inference for Evaluating Private LoRA Weights}}
 \author{Anonymous Authors}
@@
 We introduce \texttt{zklora}, a library designed to help the \emph{Base Model User} \emph{verifiably assess} the quality of a private LoRA module for a target task---for instance, to run a validation experiment without directly accessing the private weights.
-By adopting a split inference approach and generating \emph{verifiable computations}, \texttt{zklora} enables the \emph{Base Model User} to confirm that remote LoRA computations are correct, all without seeing the private weights themselves.
+By adopting a multi-party inference approach and generating \emph{verifiable computations}, \texttt{zklora} enables the \emph{Base Model User} to confirm that remote LoRA computations are correct, all without seeing the private weights themselves.
 We demonstrate the feasibility of \texttt{zklora} via benchmark experiments, showing that our approach remains computationally viable across various model sizes, with notably fast verification times.
@@
 
-\section{Introduction}
-Large Language Models (LLMs) excel at a variety of tasks but come with significant computational and storage costs \cite{brown2020language, devlin2018bert}. 
-Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by introducing a small number of trainable parameters into the model, drastically reducing memory overhead for fine-tuning \cite{ding2022delta}.
+%------------------------------------------
+% 1. PRELIMINARY RESULTS
+%------------------------------------------
+\section{Preliminary Results}
 
-When two entities, a \emph{LoRA Owner} and a \emph{Base Model User}, collaborate on a shared LLM, they may have conflicting constraints.
-The \emph{LoRA Owner} wants to keep custom LoRA weights private (e.g., for competitive or regulatory reasons), while the \emph{Base Model User} wants to \emph{test} or \emph{validate} these LoRA weights on a target task before deciding whether to deploy them at scale.
-Under normal circumstances, either the LoRA must be fully shared (sacrificing privacy), or the Base Model User must trust the LoRA Owner’s claims about performance with little evidence.
+We benchmarked \texttt{zklora} by measuring the creation and verification times for our verifiable computations across multiple base models and private LoRA configurations.
+For each model, we computed a forward pass for a batch of 3 items with sequence length 5.
+Each experiment simulates the workflow where the \emph{Base Model User} uses local data to evaluate the base model + LoRA combination, requesting remote LoRA computations from the \emph{LoRA Owner}. 
+We report total and average proof-generation times (\texttt{total\_prove}, \texttt{avg\_prove}) and verification times (\texttt{total\_verify}, \texttt{avg\_verify}), as well as relevant model parameters.
 
-In this paper, we present \texttt{zklora}, a library that provides a \emph{verifiable computation} solution for the \emph{Base Model User} to \emph{evaluate} a private LoRA module.
-By orchestrating a split inference, \texttt{zklora} allows the Base Model User to run the base model locally while sending partial activations to the LoRA Owner.
-Crucially, the LoRA Owner returns not only updated activations but also a cryptographic \emph{proof} that the correct LoRA transformation was applied.
-In this way, the Base Model User can confirm the final outputs truly reflect the LoRA module’s capabilities.
-After verifying and measuring results on a validation dataset, the Base Model User can later choose how to adopt the LoRA at larger scale.
+\begin{table}[ht]
+    \centering
+    \small
+    \begin{tabular}{l c c c c c c c}
+    \toprule
+    \textbf{base\_model} & \textbf{\#lora} & \textbf{total\_params} & \textbf{avg\_params} & \textbf{total\_prove} & \textbf{avg\_prove} & \textbf{total\_verify} & \textbf{avg\_verify} \\
+    \midrule
+distilgpt2 & 24 & 589824 & 24576.0 & 759.33 & 31.64 & 16.56 & 0.69 \\
+gpt2 & 48 & 2359296 & 49152.0 & 1675.58 & 34.91 & 32.79 & 0.68 \\
+Llama-3.2-1B & 32 & 851968 & 26624.0 & 991.93 & 31.00 & 24.91 & 0.78 \\
+Llama-3.3-70B-Instr. & 80 & 11796480 & 147456.0 & 3749.76 & 46.87 & 123.11 & 1.54 \\
+Llama-3.1-8B-Instr. & 32 & 5242880 & 163840.0 & 1527.40 & 47.73 & 35.79 & 1.12 \\
+Mixtral-8x7B-Instr. & 32 & 10485760 & 327680.0 & 2357.61 & 73.68 & 44.30 & 1.38 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Benchmark results for \texttt{zklora} showing multi-party inference overhead on various model + LoRA combinations. Times are in seconds.}
+    \label{tab:results}
+\end{table}
 
-\section{Related Work}
+Notably, although proof-generation times can grow with model size, verification remains comparatively fast (e.g., \texttt{avg\_verify} of about 1--2 seconds even for 70B-scale models).
+This result demonstrates that \texttt{zklora} allows frequent correctness checks without excessive overhead, which is crucial for real-world “trial runs.” In larger-scale usage scenarios, once trust in the LoRA module is established, \texttt{zklora} may no longer be needed.
 
-\subsection{Low-Rank Adaptation}
-LoRA \cite{hu2021lora} has emerged as a popular way to efficiently fine-tune LLMs by injecting small, low-rank matrices into specific layers.
-This approach scales well, requiring less GPU memory than full fine-tuning.
-Various frameworks build on LoRA for GPT-2, GPT-Neo, LLaMA, and others \cite{ding2022delta}.
-By confining most updated parameters to low-rank adapter matrices, LoRA drastically reduces memory overhead during fine-tuning.
-As a result, domain-specific LoRA modules can be swapped in or out of the same base model, avoiding the need to retrain or store complete copies of large networks.
-
-\subsection{Incrementally Verifiable Computation}
-Valiant~\cite{valiant2008incrementally} introduced the notion of Incrementally Verifiable Computation (IVC), which offers updatable, compact proofs of correctness over multi-step computations.
-Nova~\cite{kothapalli2022nova} and HyperNova~\cite{kothapalli2024hypernova} refine these ideas, leveraging folding schemes and zero-knowledge properties to enable scaling of verifiable computations in multi-step neural network inference.
-IVC-based approaches align well with repeated computations needing multiple checkpoints of trust, such as multiple forward passes or partial training loops.
-
-\section{Methodology: zklora for Verifiable Evaluation}
+%------------------------------------------
+% 2. MULTI-PARTY INFERENCE METHOD
+%------------------------------------------
+\section{Multi-Party Inference: zklora for Verifiable Evaluation}
 Our aim is to enable the \emph{Base Model User} to run a \emph{validation experiment} on their local data, incorporating the private LoRA module from the \emph{LoRA Owner}.
 The Base Model User can measure task performance (e.g., cross-entropy loss, accuracy) to decide whether the LoRA meets performance requirements.
-Figure~\ref{fig:toy-mlp-lora} illustrates a simple scenario.
 
+Figure~\ref{fig:toy-mlp-lora} illustrates a simple scenario:
 \begin{enumerate}
@@
 
-\draw[arrow] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
+\draw[->] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
 \draw[->, dashed] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial activations} (LoRA.south);
 \draw[->, dashed] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
-\draw[arrow] (W1) -- node[above, font=\scriptsize]{$\mathbf{z}'$} (act);
-\draw[arrow] (act) -- node[above, font=\scriptsize]{hidden} (W2);
-\draw[arrow] (W2) -- (output);
+\draw[->] (W1) -- node[above, font=\scriptsize]{$\mathbf{z}'$} (act);
+\draw[->] (act) -- node[above, font=\scriptsize]{hidden} (W2);
+\draw[->] (W2) -- (output);
 
@@
 ] (baseModelFit) {};
-
 \end{tikzpicture}
@@
 
-After confirming performance with \texttt{zklora}, the Base Model User can move forward using the LoRA weights with confidence, knowing their underlying quality combined with the base model.
-The core objective with \texttt{zklora} is to \emph{verify} that the private LoRA weights indeed perform as claimed, without revealing them.
+%------------------------------------------
+% 3. INTRODUCTION
+%------------------------------------------
+\section{Introduction}
+Large Language Models (LLMs) excel at a variety of tasks but come with significant computational and storage costs \cite{brown2020language, devlin2018bert}. 
+Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by introducing a small number of trainable parameters into the model, drastically reducing memory overhead for fine-tuning \cite{ding2022delta}.
 
-\section{Experiments}
-We benchmarked \texttt{zklora} by measuring the creation and verification times for our verifiable computations across multiple base models and private LoRA configurations.
-For each model, we computed a forward pass for a batch of 3 items with sequence length 5.
-Each experiment simulates the workflow where the \emph{Base Model User} uses local data to evaluate the base model + LoRA combination, requesting remote LoRA computations from the \emph{LoRA Owner}. 
-We report total and average proof-generation times (\texttt{total\_prove}, \texttt{avg\_prove}) and verification times (\texttt{total\_verify}, \texttt{avg\_verify}), as well as relevant model parameters.
+When two entities, a \emph{LoRA Owner} and a \emph{Base Model User}, collaborate on a shared LLM, they may have conflicting constraints.
+The \emph{LoRA Owner} wants to keep custom LoRA weights private (e.g., for competitive or regulatory reasons), while the \emph{Base Model User} wants to \emph{test} or \emph{validate} these LoRA weights on a target task before deciding whether to deploy them at scale.
+Under normal circumstances, either the LoRA must be fully shared (sacrificing privacy), or the Base Model User must trust the LoRA Owner’s claims about performance with little evidence.
 
-\begin{table}[ht]
-    \centering
-    \small
-    \begin{tabular}{l c c c c c c c}
-    \toprule
-    \textbf{base\_model} & \textbf{\#lora} & \textbf{total\_params} & \textbf{avg\_params} & \textbf{total\_prove} & \textbf{avg\_prove} & \textbf{total\_verify} & \textbf{avg\_verify} \\
-    \midrule
-distilgpt2 & 24 & 589824 & 24576.0 & 759.33 & 31.64 & 16.56 & 0.69 \\
-gpt2 & 48 & 2359296 & 49152.0 & 1675.58 & 34.91 & 32.79 & 0.68 \\
-Llama-3.2-1B & 32 & 851968 & 26624.0 & 991.93 & 31.00 & 24.91 & 0.78 \\
-Llama-3.3-70B-Instr. & 80 & 11796480 & 147456.0 & 3749.76 & 46.87 & 123.11 & 1.54 \\
-Llama-3.1-8B-Instr. & 32 & 5242880 & 163840.0 & 1527.40 & 47.73 & 35.79 & 1.12 \\
-Mixtral-8x7B-Instr. & 32 & 10485760 & 327680.0 & 2357.61 & 73.68 & 44.30 & 1.38 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Benchmark results for \texttt{zklora} showing split inference overhead on various model + LoRA combinations. Times are in seconds.}
-    \label{tab:results}
-\end{table}
+In this paper, we present \texttt{zklora}, a library that provides a \emph{verifiable computation} solution for the \emph{Base Model User} to \emph{evaluate} a private LoRA module.
+By orchestrating a multi-party inference, \texttt{zklora} allows the Base Model User to run the base model locally while sending partial activations to the LoRA Owner.
+Crucially, the LoRA Owner returns not only updated activations but also a cryptographic \emph{proof} that the correct LoRA transformation was applied.
+In this way, the Base Model User can confirm the final outputs truly reflect the LoRA module’s capabilities.
+After verifying and measuring results on a validation dataset, the Base Model User can later choose how to adopt the LoRA at larger scale.
 
-As shown in Table~\ref{tab:results}, proof-generation times tend to grow with model size, particularly for 70B-scale systems.
-However, the verification step remains fast, often averaging under two seconds per proof, even at large scales.
-This efficiency is crucial for real-world “trial runs”, allowing the Base Model User to confirm performance on a validation set without incurring prohibitive overhead.
-In larger-scale usage scenarios, once trust in the LoRA module is established, \texttt{zklora} may no longer be needed.
+%------------------------------------------
+% 4. RELATED WORK
+%------------------------------------------
+\section{Related Work}
 
+\subsection{Low-Rank Adaptation}
+LoRA \cite{hu2021lora} has emerged as a popular way to efficiently fine-tune LLMs by injecting small, low-rank matrices into specific layers.
+This approach scales well, requiring less GPU memory than full fine-tuning.
+Various frameworks build on LoRA for GPT-2, GPT-Neo, LLaMA, and others \cite{ding2022delta}.
+By confining most updated parameters to low-rank adapter matrices, LoRA drastically reduces memory overhead during fine-tuning.
+As a result, domain-specific LoRA modules can be swapped in or out of the same base model, avoiding the need to retrain or store complete copies of large networks.
+
+\subsection{Incrementally Verifiable Computation}
+Valiant~\cite{valiant2008incrementally} introduced the notion of Incrementally Verifiable Computation (IVC), which offers updatable, compact proofs of correctness over multi-step computations.
+Nova~\cite{kothapalli2022nova} and HyperNova~\cite{kothapalli2024hypernova} refine these ideas, leveraging folding schemes and zero-knowledge properties to enable scaling of verifiable computations in multi-step neural network inference.
+IVC-based approaches align well with repeated computations needing multiple checkpoints of trust, such as multiple forward passes or partial training loops.
+
+%------------------------------------------
+% 5. CONCLUSION
+%------------------------------------------
 \section{Conclusion}
 \texttt{zklora} enables a \emph{Base Model User} to verify the quality of a private LoRA module without revealing the LoRA weights.
-By pairing split inference with cryptographic proofs, \texttt{zklora} ensures that the user can trust the computed outputs during validation experiments.
+By pairing multi-party inference with cryptographic proofs, \texttt{zklora} ensures that the user can trust the computed outputs during validation experiments.
 After verifying performance, the Base Model User may adopt any approach they choose to integrate or deploy the private LoRA more widely, since the module has been proven effective.

### 2025-01-12 paper/main.tex
more zk details

@@
 \end{abstract}
+
+%------------------------------------------
+% 4. INTRODUCTION
+%------------------------------------------
+\section{Introduction}
+
+Large Language Models (LLMs) excel at a variety of tasks but come with significant computational and storage costs \cite{brown2020language, devlin2018bert}. 
+Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by introducing a small number of trainable parameters into the model, drastically reducing memory overhead for fine-tuning \cite{ding2022delta}.
+
+When two entities, a \emph{LoRA Owner} and a \emph{Base Model User}, collaborate on a shared LLM, they may have conflicting constraints.
+The \emph{LoRA Owner} wants to keep custom LoRA weights private (e.g., for competitive or regulatory reasons), while the \emph{Base Model User} wants to \emph{test} or \emph{validate} these LoRA weights on a target task before deciding whether to deploy them at scale.
+Under normal circumstances, either the LoRA must be fully shared (sacrificing privacy), or the Base Model User must trust the LoRA Owner’s claims about performance with little evidence.
+
+\texttt{zklora} bridges this gap by orchestrating multi-party inference: the base model user remains in control of the main layers, whereas the LoRA Owner privately applies LoRA transformations.
+The user obtains a zero-knowledge proof demonstrating that the LoRA transformations are indeed correct, thus verifying the final performance metrics.
+Once satisfied that the LoRA weights meet their needs, the Base Model User can incorporate them at scale through whatever inference arrangement they prefer.
 
@@
 
-Notably, although proof-generation times can grow with model size, verification remains comparatively fast (e.g., \texttt{avg\_verify} of about 1--2 seconds even for 70B-scale models).
+Notably, although proof-generation times can grow with model size, verification remains comparatively fast (e.g., an average of around 1--2 seconds per proof even for 70B-scale models).
 This result demonstrates that \texttt{zklora} allows frequent correctness checks without excessive overhead, which is crucial for real-world “trial runs.” In larger-scale usage scenarios, once trust in the LoRA module is established, \texttt{zklora} may no longer be needed.
@@
 \section{Multi-Party Inference: zklora for Verifiable Evaluation}
+
 Our aim is to enable the \emph{Base Model User} to run a \emph{validation experiment} on their local data, incorporating the private LoRA module from the \emph{LoRA Owner}.
@@
 
-Figure~\ref{fig:toy-mlp-lora} illustrates a simple scenario:
+Figure~\ref{fig:toy-mlp-lora} illustrates a simple scenario in which:
+
 \begin{enumerate}
@@
     The \emph{LoRA Owner} applies the LoRA transformation to the activations and returns the updated activations alongside a \emph{cryptographic proof} of correctness.
-In our setup, \texttt{zklora} interfaces with \texttt{ezkl} to produce these proofs.
 
@@
 %------------------------------------------
-% 3. INTRODUCTION
+% 3. HOW WE GENERATE THE ZERO-KNOWLEDGE PROOF
 %------------------------------------------
-\section{Introduction}
-Large Language Models (LLMs) excel at a variety of tasks but come with significant computational and storage costs \cite{brown2020language, devlin2018bert}. 
-Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by introducing a small number of trainable parameters into the model, drastically reducing memory overhead for fine-tuning \cite{ding2022delta}.
+\section{Generating the Zero-Knowledge Proof}
 
-When two entities, a \emph{LoRA Owner} and a \emph{Base Model User}, collaborate on a shared LLM, they may have conflicting constraints.
-The \emph{LoRA Owner} wants to keep custom LoRA weights private (e.g., for competitive or regulatory reasons), while the \emph{Base Model User} wants to \emph{test} or \emph{validate} these LoRA weights on a target task before deciding whether to deploy them at scale.
-Under normal circumstances, either the LoRA must be fully shared (sacrificing privacy), or the Base Model User must trust the LoRA Owner’s claims about performance with little evidence.
+A central piece of our methodology is producing a cryptographic proof that the LoRA transformations were correctly computed—without ever disclosing the LoRA parameters themselves.
+We outline the proof-generation process below, referencing the flow in the accompanying code.
+For simplicity, we assume the LoRA Owner has already exported the LoRA-modified layer(s) as an ONNX model and that intermediate activations are saved in a JSON file.
+Each pairing of “model file” and “JSON input data” yields a distinct proof.
 
-In this paper, we present \texttt{zklora}, a library that provides a \emph{verifiable computation} solution for the \emph{Base Model User} to \emph{evaluate} a private LoRA module.
-By orchestrating a multi-party inference, \texttt{zklora} allows the Base Model User to run the base model locally while sending partial activations to the LoRA Owner.
-Crucially, the LoRA Owner returns not only updated activations but also a cryptographic \emph{proof} that the correct LoRA transformation was applied.
-In this way, the Base Model User can confirm the final outputs truly reflect the LoRA module’s capabilities.
-After verifying and measuring results on a validation dataset, the Base Model User can later choose how to adopt the LoRA at larger scale.
+\subsection{Preparing Model, Inputs, and Circuit}
+\paragraph{Circuit and ONNX File.}
+The LoRA Owner provides an ONNX model that includes the relevant LoRA weights. We then compile this model into a zero-knowledge friendly circuit format. This step:
+\begin{itemize}
+    \item Parses the graph structure from the ONNX file.
+    \item Determines how many constraints or “gates” are needed.
+    \item Produces a circuit representation that can be used for further proof-generation steps.
+\end{itemize}
+
+\paragraph{Input Activations (JSON).}
+When the \emph{Base Model User} runs the partial forward pass locally, the intermediate activations for that partial pass are recorded in a JSON file.
+This JSON effectively captures the inbound tensor(s) that will go through the remote LoRA layers.
+
+\subsection{Generating Setup and Keys}
+\paragraph{Settings and Keys.}
+To make the cryptographic proof work, the system needs:
+\begin{itemize}
+    \item \textbf{Settings File:} Summarizes the circuit’s structure (e.g., log rows, public vs. private parameters). 
+    \item \textbf{Proving/Verification Keys (PK/VK):} Analogous to a public-private key system, enabling one party to prove a statement and another to verify.
+\end{itemize}
+We produce these keys from the compiled circuit.
+If the protocol also requires a structured reference string (SRS), we generate that as well.
+This SRS encapsulates certain group elements or domain parameters for polynomial commitments, usually saved in a file.
+
+\subsection{Generating the Witness}
+\paragraph{Witness Creation.}
+With the circuit in place, we feed the JSON data for intermediate activations into the compiled circuit. This step:
+\begin{itemize}
+    \item Performs the actual forward pass inside the circuit, substituting the LoRA parameters from the ONNX file.
+    \item Produces a “witness file,” which is a low-level representation of all wire values in the circuit.
+\end{itemize}
+In practice, this might be asynchronous or batched, ensuring large inputs can be processed efficiently.
+
+\subsection{Proof Generation}
+\paragraph{Prove.}
+Once we have:
+\begin{itemize}
+    \item The circuit representation.
+    \item The proving key (PK).
+    \item The witness file.
+\end{itemize}
+we invoke a “prove” routine that executes polynomial commitment schemes and solves the constraint system. This yields a standalone proof file that can be shared with the \emph{Base Model User}.
+
+\paragraph{Result.}
+The final proof cryptographically certifies that the LoRA Owner used the declared ONNX model and input JSON to compute the updated activations \emph{exactly} as claimed, with no tampering or hidden changes.
+
+\subsection{Proof Verification}
+\paragraph{Checking the Proof.}
+The \emph{Base Model User}, upon receiving the proof, uses:
+\begin{itemize}
+    \item The verification key (VK).
+    \item The structured reference string (SRS).
+    \item The proof file.
+\end{itemize}
+A single verification call then confirms or denies the proof’s correctness. If correct, it implies that the LoRA transformations were faithfully applied.
+
+\paragraph{Timing.}
+In our benchmarks, this verification step is typically on the order of 1–2 seconds, even for large models, as shown in Table~\ref{tab:results}.
+The minimal overhead of verification makes \texttt{zklora} feasible for continuous or repeated “trial runs” to confirm LoRA quality.
 
 %------------------------------------------
-% 4. RELATED WORK
+% 5. RELATED WORK
 %------------------------------------------
@@
 By confining most updated parameters to low-rank adapter matrices, LoRA drastically reduces memory overhead during fine-tuning.
-As a result, domain-specific LoRA modules can be swapped in or out of the same base model, avoiding the need to retrain or store complete copies of large networks.
 
@@
 Valiant~\cite{valiant2008incrementally} introduced the notion of Incrementally Verifiable Computation (IVC), which offers updatable, compact proofs of correctness over multi-step computations.
-Nova~\cite{kothapalli2022nova} and HyperNova~\cite{kothapalli2024hypernova} refine these ideas, leveraging folding schemes and zero-knowledge properties to enable scaling of verifiable computations in multi-step neural network inference.
-IVC-based approaches align well with repeated computations needing multiple checkpoints of trust, such as multiple forward passes or partial training loops.
+Follow-up work \cite{kothapalli2022nova, kothapalli2024hypernova} refines these ideas, leveraging folding schemes and zero-knowledge properties to enable scaling of verifiable computations.
+While prior research has investigated IVC for inference or specialized tasks, \texttt{zklora} adapts such cryptographic proof techniques for verifying private LoRA transformations in multi-party inference.
 
 %------------------------------------------
-% 5. CONCLUSION
+% 6. CONCLUSION
 %------------------------------------------
 \section{Conclusion}
+
 \texttt{zklora} enables a \emph{Base Model User} to verify the quality of a private LoRA module without revealing the LoRA weights.
-By pairing multi-party inference with cryptographic proofs, \texttt{zklora} ensures that the user can trust the computed outputs during validation experiments.
-After verifying performance, the Base Model User may adopt any approach they choose to integrate or deploy the private LoRA more widely, since the module has been proven effective.
-Our experiments show this approach is feasible across a range of model sizes, with \emph{fast verification times} minimizing the overhead of a verifiable evaluation phase.
-Future directions include further circuit optimization and exploring multi-owner scenarios, in which multiple private LoRA modules could be composed and verified within the same pipeline.
+Our benchmarks show that proof generation remains feasible for multiple model sizes, and verification overhead is small enough to allow iterative experiments.
+This design provides strong assurances of correctness while preserving LoRA privacy.
+Future directions include optimizing circuit compilation, supporting multi-owner LoRA composition, and investigating broader multi-party computation frameworks that incorporate private data alongside private model parameters.
 

### 2025-01-12 paper/main.tex
convert table to figures

--- 2025-01-12 paper/main.tex
@@
 %------------------------------------------
+% Move INTRO to the beginning
+%------------------------------------------
+\section{Introduction}
+Large Language Models (LLMs) excel at many tasks but can be expensive to store and fine-tune \cite{brown2020language, devlin2018bert}. 
+Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by injecting small adapter matrices, making specialized fine-tuning more efficient \cite{ding2022delta}.
+
+However, if a \emph{LoRA Owner} wants to keep these weights private while a \emph{Base Model User} needs to validate them on a local dataset, a direct sharing of the LoRA parameters is impossible.
+\texttt{zklora} solves this dilemma by orchestrating multi-party inference: The Base Model User runs the base model layers locally, forwarding partial activations to the LoRA Owner for the private transform.
+A zero-knowledge proof is generated to demonstrate correctness, ensuring that final performance metrics are truly representative of the private LoRA.
+
+%------------------------------------------
 % 1. PRELIMINARY RESULTS
@@
 
-We benchmarked \texttt{zklora} by measuring the creation and verification times for our verifiable computations across multiple base models and private LoRA configurations.
-For each model, we computed a forward pass for a batch of 3 items with sequence length 5.
-Each experiment simulates the workflow where the \emph{Base Model User} uses local data to evaluate the base model + LoRA combination, requesting remote LoRA computations from the \emph{LoRA Owner}. 
-We report total and average proof-generation times (\texttt{total\_prove}, \texttt{avg\_prove}) and verification times (\texttt{total\_verify}, \texttt{avg\_verify}), as well as relevant model parameters.
+We benchmarked \texttt{zklora} by measuring the creation and verification times across multiple base models and private LoRA configurations. 
+Figures~\ref{fig:settings}, \ref{fig:proof}, and \ref{fig:verify} show the total LoRA parameter count (horizontal axis) versus:
+\begin{itemize}
+    \item \textbf{Total Settings Time} (sec),
+    \item \textbf{Total Proof Generation Time} (sec),
+    \item \textbf{Total Verification Time} (sec),
+\end{itemize}
+respectively.
 
-\begin{table}[ht]
+\begin{figure}[ht]
     \centering
-    \small
-    \begin{tabular}{l c c c c c c c}
-    \toprule
-    \textbf{base\_model} & \textbf{\#lora} & \textbf{total\_params} & \textbf{avg\_params} & \textbf{total\_prove} & \textbf{avg\_prove} & \textbf{total\_verify} & \textbf{avg\_verify} \\
-    \midrule
-distilgpt2 & 24 & 589824 & 24576.0 & 759.33 & 31.64 & 16.56 & 0.69 \\
-gpt2 & 48 & 2359296 & 49152.0 & 1675.58 & 34.91 & 32.79 & 0.68 \\
-Llama-3.2-1B & 32 & 851968 & 26624.0 & 991.93 & 31.00 & 24.91 & 0.78 \\
-Llama-3.3-70B-Instr. & 80 & 11796480 & 147456.0 & 3749.76 & 46.87 & 123.11 & 1.54 \\
-Llama-3.1-8B-Instr. & 32 & 5242880 & 163840.0 & 1527.40 & 47.73 & 35.79 & 1.12 \\
-Mixtral-8x7B-Instr. & 32 & 10485760 & 327680.0 & 2357.61 & 73.68 & 44.30 & 1.38 \\
-    \bottomrule
-    \end{tabular}
-    \caption{Benchmark results for \texttt{zklora} showing multi-party inference overhead on various model + LoRA combinations. Times are in seconds.}
-    \label{tab:results}
-\end{table}
+    \includegraphics[width=0.55\linewidth]{figs/fig_settings.pdf}
+    \caption{Total LoRA params (in millions) vs. total settings time. Each point is a different model.}
+    \label{fig:settings}
+\end{figure}
 
-Notably, although proof-generation times can grow with model size, verification remains comparatively fast (e.g., \texttt{avg\_verify} of about 1--2 seconds even for 70B-scale models).
-This result demonstrates that \texttt{zklora} allows frequent correctness checks without excessive overhead, which is crucial for real-world “trial runs.” In larger-scale usage scenarios, once trust in the LoRA module is established, \texttt{zklora} may no longer be needed.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.55\linewidth]{figs/fig_proof.pdf}
+    \caption{Total LoRA params (in millions) vs. total proof generation time. Each point is a different model.}
+    \label{fig:proof}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.55\linewidth]{figs/fig_verify.pdf}
+    \caption{Total LoRA params (in millions) vs. total verification time. Each point is a different model.}
+    \label{fig:verify}
+\end{figure}
+
+Notably, while proof-generation times can grow with model size, verification remains consistently fast (on the order of 1--2 seconds per proof for large models).
+This helps real-world “trial runs,” letting the Base Model User confirm private LoRA quality without incurring excessive overhead.
 
@@
 \section{Multi-Party Inference: zklora for Verifiable Evaluation}
-Our aim is to enable the \emph{Base Model User} to run a \emph{validation experiment} on their local data, incorporating the private LoRA module from the \emph{LoRA Owner}.
-The Base Model User can measure task performance (e.g., cross-entropy loss, accuracy) to decide whether the LoRA meets performance requirements.
 
-Figure~\ref{fig:toy-mlp-lora} illustrates a simple scenario:
+Our approach allows the \emph{Base Model User} to incorporate a private LoRA module from the \emph{LoRA Owner}:
+
 \begin{enumerate}
-    \item \textbf{Base Model Forward Pass (Base Model User).}
-    The \emph{Base Model User} runs layers without LoRA parameters locally, generating partial activations.
+    \item \textbf{Base Model Forward Pass.} 
+    The user runs all layers without LoRA locally, producing partial activations.
 
-    \item \textbf{Forward to LoRA Adapter (Base Model User).}
-    Whenever the next layer includes a LoRA transform, the \emph{Base Model User} sends these partial activations to the \emph{LoRA Owner}, who holds the private LoRA module.
+    \item \textbf{Forward to LoRA Adapter.} 
+    The partial activations are sent to the LoRA Owner for private transformations.
 
-    \item \textbf{LoRA Computation \& Proof Generation (LoRA Owner).}
-    The \emph{LoRA Owner} applies the LoRA transformation to the activations and returns the updated activations alongside a \emph{cryptographic proof} of correctness.
-In our setup, \texttt{zklora} interfaces with \texttt{ezkl} to produce these proofs.
+    \item \textbf{LoRA Computation \& Proof Generation.} 
+    The LoRA Owner updates the activations and produces a zero-knowledge proof of correctness.
 
-    \item \textbf{Resuming the Forward Pass (Base Model User).}
-    The \emph{Base Model User} injects the updated activations back into the local model state and continues the forward pass.
+    \item \textbf{Resuming the Forward Pass.} 
+    The updated activations are returned and merged into the local forward pass.
 
-    \item \textbf{Verification \& Validation (Base Model User).}
-    The \emph{Base Model User} verifies the LoRA proof.
-If valid, the outputs from the combined base + LoRA model are guaranteed to match the LoRA Owner’s claimed computation.
-The Base Model User can now measure final metrics (loss, accuracy, etc.) to assess \emph{quality} on the target task.
+    \item \textbf{Verification \& Validation.} 
+    The Base Model User verifies the proof and measures final metrics (e.g., accuracy) to decide if the LoRA meets their needs.
 \end{enumerate}
@@
 \end{tikzpicture}
-\caption{A simplified 2-layer MLP with LoRA on the first layer.
-The Base Model User (blue box) runs most computations locally but calls the LoRA Owner (dashed box) to update partial activations.
-After verifying correctness, the Base Model User can measure final metrics to decide whether to adopt the private LoRA more extensively.}
+\caption{A simplified 2-layer MLP with LoRA on the first layer. The Base Model User (blue box) runs most computations locally, then requests the LoRA Owner (dashed box) to update partial activations.}
 \label{fig:toy-mlp-lora}
@@
 %------------------------------------------
-% 3. INTRODUCTION
+% 3. HOW WE GENERATE THE ZERO-KNOWLEDGE PROOF
 %------------------------------------------
-\section{Introduction}
-Large Language Models (LLMs) excel at a variety of tasks but come with significant computational and storage costs \cite{brown2020language, devlin2018bert}. 
-Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by introducing a small number of trainable parameters into the model, drastically reducing memory overhead for fine-tuning \cite{ding2022delta}.
+\section{Generating the Zero-Knowledge Proof}
 
-When two entities, a \emph{LoRA Owner} and a \emph{Base Model User}, collaborate on a shared LLM, they may have conflicting constraints.
-The \emph{LoRA Owner} wants to keep custom LoRA weights private (e.g., for competitive or regulatory reasons), while the \emph{Base Model User} wants to \emph{test} or \emph{validate} these LoRA weights on a target task before deciding whether to deploy them at scale.
-Under normal circumstances, either the LoRA must be fully shared (sacrificing privacy), or the Base Model User must trust the LoRA Owner’s claims about performance with little evidence.
+Central to \texttt{zklora} is the cryptographic proof that the LoRA computations were conducted faithfully. Below is a high-level outline:
 
-In this paper, we present \texttt{zklora}, a library that provides a \emph{verifiable computation} solution for the \emph{Base Model User} to \emph{evaluate} a private LoRA module.
-By orchestrating a multi-party inference, \texttt{zklora} allows the Base Model User to run the base model locally while sending partial activations to the LoRA Owner.
-Crucially, the LoRA Owner returns not only updated activations but also a cryptographic \emph{proof} that the correct LoRA transformation was applied.
-In this way, the Base Model User can confirm the final outputs truly reflect the LoRA module’s capabilities.
-After verifying and measuring results on a validation dataset, the Base Model User can later choose how to adopt the LoRA at larger scale.
+\paragraph{Circuit Compilation (Model + JSON Input).}
+The LoRA Owner provides an ONNX model that includes the LoRA parameters.
+We compile it into a “circuit” representing the layer computations.
+Next, the Base Model User's partial activations, saved as JSON, feed into this circuit as inputs.
+
+\paragraph{Settings and Key Generation.}
+We produce (1) a “settings” file that includes circuit metadata, (2) a proving key (PK) and verification key (VK), and optionally (3) a structured reference string (SRS) for polynomial commitments.
+
+\paragraph{Witness Creation.}
+We run the partial activations through the circuit, storing all intermediate wire values in a “witness” file that reflects the correct usage of the LoRA layer.
+
+\paragraph{Proving.}
+Using the PK, the witness, and the circuit, the LoRA Owner generates a proof file. This file certifies that the LoRA transformation was done correctly, matching the declared ONNX logic.
+
+\paragraph{Verification.}
+The Base Model User loads the proof and verifies it with the VK (plus SRS). If it checks out, the user trusts that the LoRA updates are accurate, without ever seeing the LoRA weights directly.
 
@@
 \subsection{Low-Rank Adaptation}
-LoRA \cite{hu2021lora} has emerged as a popular way to efficiently fine-tune LLMs by injecting small, low-rank matrices into specific layers.
-This approach scales well, requiring less GPU memory than full fine-tuning.
-Various frameworks build on LoRA for GPT-2, GPT-Neo, LLaMA, and others \cite{ding2022delta}.
-By confining most updated parameters to low-rank adapter matrices, LoRA drastically reduces memory overhead during fine-tuning.
-As a result, domain-specific LoRA modules can be swapped in or out of the same base model, avoiding the need to retrain or store complete copies of large networks.
+LoRA \cite{hu2021lora} is widely adopted for parameter-efficient fine-tuning across GPT-2, GPT-Neo, and LLaMA.
+By focusing updates on low-rank adapters, it reduces memory overhead \cite{ding2022delta}.
 
 \subsection{Incrementally Verifiable Computation}
-Valiant~\cite{valiant2008incrementally} introduced the notion of Incrementally Verifiable Computation (IVC), which offers updatable, compact proofs of correctness over multi-step computations.
-Nova~\cite{kothapalli2022nova} and HyperNova~\cite{kothapalli2024hypernova} refine these ideas, leveraging folding schemes and zero-knowledge properties to enable scaling of verifiable computations in multi-step neural network inference.
-IVC-based approaches align well with repeated computations needing multiple checkpoints of trust, such as multiple forward passes or partial training loops.
+Earlier cryptographic frameworks \cite{valiant2008incrementally, kothapalli2022nova, kothapalli2024hypernova} show how to prove correctness of multi-step computations.
+\texttt{zklora} combines these proof techniques with a multi-party inference flow, ensuring that LoRA transformations remain private yet verifiable.
 
@@
 \section{Conclusion}
-\texttt{zklora} enables a \emph{Base Model User} to verify the quality of a private LoRA module without revealing the LoRA weights.
-By pairing multi-party inference with cryptographic proofs, \texttt{zklora} ensures that the user can trust the computed outputs during validation experiments.
-After verifying performance, the Base Model User may adopt any approach they choose to integrate or deploy the private LoRA more widely, since the module has been proven effective.
-Our experiments show this approach is feasible across a range of model sizes, with \emph{fast verification times} minimizing the overhead of a verifiable evaluation phase.
-Future directions include further circuit optimization and exploring multi-owner scenarios, in which multiple private LoRA modules could be composed and verified within the same pipeline.
+
+We present \texttt{zklora} as a verifiable multi-party inference solution to validate private LoRA adapters.
+Our benchmarks show that proof generation scales with model size, while verification remains consistently quick.
+This enables the Base Model User to run iterative experiments on LoRA modules without risking the LoRA Owner’s privacy.
+Future extensions might explore multi-owner LoRA composition or advanced multi-party computation frameworks that guard both user data and model parameters with cryptographic guarantees.
 

### 2025-01-12 paper/figures.py

@@ -1,0 +1,109 @@
+import matplotlib.pyplot as plt
+import os
+
+# Create an output folder for the figures
+os.makedirs("figs", exist_ok=True)
+
+# Example data (dictionary of dictionaries):
+# Each key is a model name, value is a dict with:
+#   'params'   -> total LoRA params (integer)
+#   'settings' -> total settings/compile time (sec)
+#   'proof'    -> total proof generation time (sec)
+#   'verify'   -> total verification time (sec)
+data = {
+    'distilgpt2':       {'params': 589824,    'settings': 911.99,  'proof': 759.33,  'verify': 16.56},
+    'gpt2-lora1':       {'params': 2359296,   'settings': 2092.13, 'proof': 1675.58, 'verify': 32.79},
+    'Llama-3.2-1B':     {'params': 851968,    'settings': 1189.01, 'proof': 991.93,  'verify': 24.91},
+    'Llama-3.3-70B':    {'params': 11796480,  'settings': 4392.86, 'proof': 3749.76, 'verify': 123.11},
+    'Llama-3.1-8B':     {'params': 5242880,   'settings': 1836.83, 'proof': 1527.40, 'verify': 35.79},
+    'Mixtral-8x7B':     {'params': 10485760,  'settings': 2754.91, 'proof': 2357.61, 'verify': 44.30},
+}
+
+# Distinct colors for each model
+colors = {
+    'distilgpt2':    'blue',
+    'gpt2-lora1':    'red',
+    'gpt2-lora2':    'green',
+    'Llama-3.2-1B':  'orange',
+    'Llama-3.3-70B': 'purple',
+    'Llama-3.1-8B':  'brown',
+    'Mixtral-8x7B':  'magenta',
+}
+
+# Sort the model names by ascending number of LoRA params
+model_names_sorted = sorted(data.keys(), key=lambda m: data[m]['params'])
+
+def plot_graph(x_key, y_key, title, xlabel, ylabel, output_file):
+    plt.figure(figsize=(6,4), dpi=100)
+    plt.title(title)
+
+    # We'll store the sorted x and y values in separate lists
+    x_vals = []
+    y_vals = []
+
+    # Populate lists using sorted model names
+    for name in model_names_sorted:
+        # Convert param count to millions
+        params_millions = data[name][x_key] / 1e6
+        x_vals.append(params_millions)
+        y_vals.append(data[name][y_key])
+
+    # Plot each model as a distinct color dot
+    for i, name in enumerate(model_names_sorted):
[…]

### 2025-01-12 paper/main.tex
updated framing of verification speed; new improved figs

@@
 
-\title{\textbf{zklora: Verifiable Multi-Party Inference for Evaluating Private LoRA Weights}}
+\title{\textbf{zklora: Efficient Verification of LoRA-Base Model Compatibility for Large Language Models}}
 \author{Anonymous Authors}
@@
 \begin{abstract}
-In decentralized computing environments, one party may wish to fine-tune a publicly available base model with Low-Rank Adaptation (LoRA) but keep those adapter weights private, while another party wants to evaluate performance on new data.
-We introduce \texttt{zklora}, a library designed to help the \emph{Base Model User} \emph{verifiably assess} the quality of a private LoRA module for a target task---for instance, to run a validation experiment without directly accessing the private weights.
-By adopting a multi-party inference approach and generating \emph{verifiable computations}, \texttt{zklora} enables the \emph{Base Model User} to confirm that remote LoRA computations are correct, all without seeing the private weights themselves.
-We demonstrate the feasibility of \texttt{zklora} via benchmark experiments, showing that our approach remains computationally viable across various model sizes, with notably fast verification times.
+Verifying that a private Low-Rank Adaptation (LoRA) module is truly compatible with a given large language model (LLM) can be daunting, especially when those LoRA parameters cannot be disclosed. 
+We introduce \texttt{zklora}, a library for generating zero-knowledge proofs that demonstrate correct LoRA-base model compatibility \emph{without sharing LoRA weights}. 
+A key insight is that the \emph{verification step} for each LoRA module remains on the order of \textbf{1--2 seconds}, enabling repeated or batch checking at scale. 
+Our empirical evaluations confirm that \texttt{zklora} maintains this rapid per-module verification time even for multi-billion-parameter LLMs.
 \end{abstract}
@@
 %------------------------------------------
-% Move INTRO to the beginning
+% INTRO: emphasize verification challenge & clarify it's per-module
 %------------------------------------------
 \section{Introduction}
-Large Language Models (LLMs) excel at many tasks but can be expensive to store and fine-tune \cite{brown2020language, devlin2018bert}. 
-Low-Rank Adaptation (LoRA) \cite{hu2021lora} addresses these costs by injecting small adapter matrices, making specialized fine-tuning more efficient \cite{ding2022delta}.
-
-However, if a \emph{LoRA Owner} wants to keep these weights private while a \emph{Base Model User} needs to validate them on a local dataset, a direct sharing of the LoRA parameters is impossible.
-\texttt{zklora} solves this dilemma by orchestrating multi-party inference: The Base Model User runs the base model layers locally, forwarding partial activations to the LoRA Owner for the private transform.
-A zero-knowledge proof is generated to demonstrate correctness, ensuring that final performance metrics are truly representative of the private LoRA.
+Large Language Models (LLMs) have attained remarkable success \cite{brown2020language, devlin2018bert}, but verifying fine-tuned modifications such as LoRA \cite{hu2021lora} can be difficult when the updated weights must remain private.
+Traditionally, one might re-run an entire forward pass or inspect thousands of parameters to ensure correctness, which is infeasible for massive models. 
+\texttt{zklora} addresses this by generating a zero-knowledge proof of correctness for each LoRA module, guaranteeing that the private LoRA genuinely fits the public base model. 
+Crucially, \textbf{the verification stage for each LoRA module} in \texttt{zklora} remains about 1--2 seconds, even at scales of multi-billion parameter base models. 
+This rapid, per-module check allows the Base Model User to efficiently, independently verify the compatibility of the private LoRA parameters.
 
@@
 
-We benchmarked \texttt{zklora} by measuring the creation and verification times across multiple base models and private LoRA configurations. 
-Figures~\ref{fig:settings}, \ref{fig:proof}, and \ref{fig:verify} show the total LoRA parameter count (horizontal axis) versus:
+We benchmarked \texttt{zklora} across several LLMs and smaller models with varying LoRA parameter counts.
+Our focus is verifying that, regardless of total parameter scale, \emph{the per-module verification step} remains swift.
+Figures~\ref{fig:verify}, \ref{fig:settings}, and \ref{fig:proof} illustrate how total LoRA parameters correlate with:
 \begin{itemize}
-    \item \textbf{Total Settings Time} (sec),
-    \item \textbf{Total Proof Generation Time} (sec),
-    \item \textbf{Total Verification Time} (sec),
+    \item \textbf{Verification Time per Module} (Base Model User’s overhead),
+    \item \textbf{Total Settings Time} (preparatory steps and key generation),
+    \item \textbf{Total Proof Generation Time} (LoRA Owner’s overhead).
 \end{itemize}
-respectively.
 
@@
     \centering
-    \includegraphics[width=0.55\linewidth]{figs/fig_settings.pdf}
-    \caption{Total LoRA params (in millions) vs. total settings time. Each point is a different model.}
+    \includegraphics[width=0.58\linewidth]{figs/fig_verify.pdf}
+    \caption{LoRA params (millions) vs.
+Total verification.
+Even at higher scales, verifying each LoRA module remains about 1--2 seconds.
+For example, even for a 70-billion parameter model, the total verification time of the additional LoRA parameters is only ~2 minutes.}
+    \label{fig:verify}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.58\linewidth]{figs/fig_settings.pdf}
+    \caption{LoRA params (millions) vs. total settings time. Each point corresponds to a different LLM or smaller model.}
     \label{fig:settings}
@@
     \centering
-    \includegraphics[width=0.55\linewidth]{figs/fig_proof.pdf}
-    \caption{Total LoRA params (in millions) vs. total proof generation time. Each point is a different model.}
+    \includegraphics[width=0.58\linewidth]{figs/fig_proof.pdf}
+    \caption{LoRA params (millions) vs. total proof generation time (LoRA Owner’s overhead).}
     \label{fig:proof}
@@
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.55\linewidth]{figs/fig_verify.pdf}
-    \caption{Total LoRA params (in millions) vs. total verification time. Each point is a different model.}
-    \label{fig:verify}
-\end{figure}
-
-Notably, while proof-generation times can grow with model size, verification remains consistently fast (on the order of 1--2 seconds per proof for large models).
-This helps real-world “trial runs,” letting the Base Model User confirm private LoRA quality without incurring excessive overhead.
+Although proof generation may scale with parameter size, verification for each LoRA module is consistently on the order of seconds.
+We consider this \emph{fast, per-module verification} to be \texttt{zklora}’s core advantage in production LLM environments.
 
 %------------------------------------------
-% 2. MULTI-PARTY INFERENCE METHOD
+% 2. Ensuring LoRA–Base Model Compatibility with zklora
 %------------------------------------------
-\section{Multi-Party Inference: zklora for Verifiable Evaluation}
+\section{Ensuring LoRA–Base Model Compatibility}
 
-Our approach allows the \emph{Base Model User} to incorporate a private LoRA module from the \emph{LoRA Owner}:
+A typical workflow involves:
+\begin{enumerate}
+    \item \textbf{Base Model User} possessing a large LLM. 
+    \item \textbf{LoRA Owner} having proprietary low-rank adapter weights. 
+\end{enumerate}
+However, these two parties must confirm the LoRA truly “fits” the base model. Using \texttt{zklora}, the LoRA Owner proves the adapter’s compatibility \emph{without} exposing private weights:
 
 \begin{enumerate}
-    \item \textbf{Base Model Forward Pass.} 
-    The user runs all layers without LoRA locally, producing partial activations.
+    \item \textbf{Partial Forward Pass.}
+    The Base Model User runs the unaltered layers of the LLM, producing partial activations.
 
-    \item \textbf{Forward to LoRA Adapter.} 
-    The partial activations are sent to the LoRA Owner for private transformations.
+    \item \textbf{LoRA Transform + Proof Gen.}
+    The LoRA Owner applies private LoRA updates, constructing a zero-knowledge proof to attest correct usage.
 
-    \item \textbf{LoRA Computation \& Proof Generation.} 
-    The LoRA Owner updates the activations and produces a zero-knowledge proof of correctness.
+    \item \textbf{Verification per LoRA Module (1--2 sec).}
+    The user verifies each proof quickly, ensuring the final outputs reflect a valid LoRA for the base model.
 
-    \item \textbf{Resuming the Forward Pass.} 
-    The updated activations are returned and merged into the local forward pass.
-
-    \item \textbf{Verification \& Validation.} 
-    The Base Model User verifies the proof and measures final metrics (e.g., accuracy) to decide if the LoRA meets their needs.
+    \item \textbf{Evaluate.}
+    With trust in the LoRA’s correctness, the user measures performance (e.g., loss).
 \end{enumerate}
@@
 \draw[->] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
-\draw[->, dashed] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial activations} (LoRA.south);
+\draw[->, dashed] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial acts} (LoRA.south);
 \draw[->, dashed] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
@@
 \end{tikzpicture}
-\caption{A simplified 2-layer MLP with LoRA on the first layer. The Base Model User (blue box) runs most computations locally, then requests the LoRA Owner (dashed box) to update partial activations.}
+\caption{zklora inference flow on a 2-layer neural network where the first layer has private LoRA weights added.}
 \label{fig:toy-mlp-lora}
@@
 %------------------------------------------
-\section{Generating the Zero-Knowledge Proof}
+\section{Zero-Knowledge Proof Generation}
 
-Central to \texttt{zklora} is the cryptographic proof that the LoRA computations were conducted faithfully. Below is a high-level outline:
+\texttt{zklora} compiles an ONNX model (with LoRA included) into a constraint circuit. The user’s partial activations feed the circuit as inputs:
 
-\paragraph{Circuit Compilation (Model + JSON Input).}
-The LoRA Owner provides an ONNX model that includes the LoRA parameters.
-We compile it into a “circuit” representing the layer computations.
-Next, the Base Model User's partial activations, saved as JSON, feed into this circuit as inputs.
+\paragraph{(1) Circuit Compilation.} 
+We parse the LoRA-augmented layers, producing a cryptographic circuit capturing each parameter operation.
 
-\paragraph{Settings and Key Generation.}
-We produce (1) a “settings” file that includes circuit metadata, (2) a proving key (PK) and verification key (VK), and optionally (3) a structured reference string (SRS) for polynomial commitments.
+\paragraph{(2) Key Setup.} 
+A settings file, proving key, and verification key are generated. A structured reference string (SRS) may also be needed.
 
-\paragraph{Witness Creation.}
-We run the partial activations through the circuit, storing all intermediate wire values in a “witness” file that reflects the correct usage of the LoRA layer.
+\paragraph{(3) Witness Creation.}
+The LoRA Owner runs the partial activations through the circuit, tracking all wire values in a “witness.”
 
-\paragraph{Proving.}
-Using the PK, the witness, and the circuit, the LoRA Owner generates a proof file. This file certifies that the LoRA transformation was done correctly, matching the declared ONNX logic.
+\paragraph{(4) Proof.}
+Using the witness plus proving key, the LoRA Owner constructs a proof.
 
-\paragraph{Verification.}
-The Base Model User loads the proof and verifies it with the VK (plus SRS). If it checks out, the user trusts that the LoRA updates are accurate, without ever seeing the LoRA weights directly.
+\paragraph{(5) Verification per Module.}
+Each LoRA module’s proof is tested with the verification key, taking \textbf{1--2 seconds}. This minimal overhead is \texttt{zklora}’s main advantage for frequent or large-scale checks.
 
@@
 
-\subsection{Low-Rank Adaptation}
-LoRA \cite{hu2021lora} is widely adopted for parameter-efficient fine-tuning across GPT-2, GPT-Neo, and LLaMA.
-By focusing updates on low-rank adapters, it reduces memory overhead \cite{ding2022delta}.
+\subsection{Low-Rank Adaptation (LoRA)}
+
+Low-Rank Adaptation (LoRA) \cite{hu2021lora} is a technique for parameter-efficient fine-tuning of large language models (LLMs) that injects small, low-rank adapter matrices into specific layers of a pre-trained model.
+By isolating the fine-tuning process to these low-rank components, LoRA drastically reduces memory overhead compared to full-model fine-tuning.
+This design choice is especially appealing for massive LLMs where training or even storing all parameters can be prohibitive \cite{ding2022delta}.
 
 \subsection{Incrementally Verifiable Computation}
-Earlier cryptographic frameworks \cite{valiant2008incrementally, kothapalli2022nova, kothapalli2024hypernova} show how to prove correctness of multi-step computations.
-\texttt{zklora} combines these proof techniques with a multi-party inference flow, ensuring that LoRA transformations remain private yet verifiable.
+In a decentralized world, trust is a resource that is hard to achieve.
+In decentralized computation, we need to make sure the computation are being done, and are being correctly.
+In a seminal paper by Valiant (2008) \cite{valiant2008incrementally}, it was shown that proofs of knowledge can be used to assert the correct execution of general computations.
+That is, if $M$ is a machine that runs for $t$ steps producing a sequence of configurations $c_0,c_1,\dots,c_t$, then there exist an efficient and effective way to produce a computationally sound proof for the computation $c_0  \xrightarrow{t} c_t$.
+This idea is referred to as Incrementally Verifiable Computation or IVC.
+
+The main goal is IVC is to produce compact, updatable proofs of correctness for a sequence of computations, so that each new step in the computation can be verified on its own while building on the guarantees of the previous steps.
+This technique significantly reduces the verification overhead for long or evolving computations, which is invaluable in scenarios like decentralized networks, outsourced computation, and any application requiring frequent correctness checks.
+
+Kumar et al.
+(2021) \cite{kothapalli2022nova} introduced the proof system NOVA and the idea of recursive proofs, which are proofs that can ``prove the correctness of other proofs.'' Recursive proof composition is key to IVC where each proof attests to the correctness of both a step’s output and the validity of the previous step’s proof.
+
+HyperNova \cite{kothapalli2024hypernova} is a novel recursive argument system optimized for customizable constraint systems (CCS) that generalizes and improves upon prior approaches like Nova.
+It achieves efficiency through a folding scheme where the prover’s cryptographic costs are minimized and achieves zero-knowledge without relying on zkSNARKs.
+
+An IVC system allows the construction of proofs in zero-knowledge where the   proofs reveal no information about the underlying computation or its inputs beyond the validity of the claim \cite{valiant2008incrementally}.
 
@@
 
-We present \texttt{zklora} as a verifiable multi-party inference solution to validate private LoRA adapters.
-Our benchmarks show that proof generation scales with model size, while verification remains consistently quick.
-This enables the Base Model User to run iterative experiments on LoRA modules without risking the LoRA Owner’s privacy.
-Future extensions might explore multi-owner LoRA composition or advanced multi-party computation frameworks that guard both user data and model parameters with cryptographic guarantees.
+\texttt{zklora} provides a fast, robust mechanism to ensure that private LoRA modules remain consistent with a large base model.
+Our evaluations indicate that each LoRA module’s correctness can be verified in about 1--2 seconds, even for multi-billion-parameter LLMs.
+This efficiency bridges the gap between privacy-preserving LoRA development and practical, real-time validation in large-scale deployments.
+Future expansions could integrate multi-owner LoRAs, advanced zero-knowledge proofs for further performance gains, or partial data-privacy frameworks to shield user inputs as well as LoRA parameters.
 

### 2025-01-12 paper/figures.py

@@ -33,52 +33,80 @@ colors = {
 # Sort the model names by ascending number of LoRA params
 model_names_sorted = sorted(data.keys(), key=lambda m: data[m]['params'])
 
-def plot_graph(x_key, y_key, title, xlabel, ylabel, output_file):
-    plt.figure(figsize=(6,4), dpi=100)
-    plt.title(title)
+def plot_graph(
+    x_key: str,
+    y_key: str,
+    title: str,
+    xlabel: str,
+    ylabel: str,
+    output_file: str
+):
+    """Creates a dotted line graph comparing (LoRA params in millions) to
+    some measured time metric, and saves as PDF."""
+    
+    plt.figure(figsize=(6,4), dpi=120)
+    plt.title(title, fontsize=12, fontweight='bold')
 
     # We'll store the sorted x and y values in separate lists
     x_vals = []
     y_vals = []
 
-    # Populate lists using sorted model names
+    # Collect data in sorted order
     for name in model_names_sorted:
-        # Convert param count to millions
         params_millions = data[name][x_key] / 1e6
         x_vals.append(params_millions)
         y_vals.append(data[name][y_key])
 
-    # Plot each model as a distinct color dot
-    for i, name in enumerate(model_names_sorted):
-        model_x = data[name][x_key] / 1e6  # convert to millions
-        model_y = data[name][y_key]
-        plt.plot(model_x, model_y, marker='o', color=colors[name], label=name)
+    # Plot each model as a distinct color dot (larger markers, edges)
+    for name in model_names_sorted:
+        mx = data[name][x_key] / 1e6   # convert to millions
+        my = data[name][y_key]
+        plt.plot(
+            mx, my,
+            marker='o',
+            markersize=8,
+            markeredgecolor='black',
+            markeredgewidth=0.8,
+            color=colors[name],
+            linestyle='None',
+            label=name  # We'll create a manual legend below
+        )
 
-    # Connect the points with a faint dotted line in sorted order
-    plt.plot(x_vals, y_vals, 'k:', alpha=0.4)
+    # Connect points with a faint dotted line to show progression
+    # We'll use a thick line and partial transparency for a "nicer" look
+    plt.plot(
+        x_vals, y_vals,
+        'k:',   # dotted line in black
+        alpha=0.6,
+        linewidth=2
+    )
 
-    plt.xlabel(xlabel)
-    plt.ylabel(ylabel)
[…]

### 2025-01-13 paper/main.tex
update

@@
 
-\title{\textbf{zklora: Efficient Verification of LoRA-Base Model Compatibility for Large Language Models}}
-\author{Anonymous Authors}
+\title{\textbf{ZKLoRA: Efficient Verification of LoRA-Base Model Compatibility for Large Language Models}}
+\author{
+    \textbf{Bidhan Roy, Peter Potash, Marcos Villagra} \\
+    Bagel Research Team\footnotemark[1] \\
+    \texttt{bidhan@bagel.net, peter@bagel.net, marcos@bagel.net}
+}
 \date{\today}
@@
 
+\footnotetext[1]{Bagel is a research lab, making open source AI monetizable.}
+
 \begin{abstract}
 Verifying that a private Low-Rank Adaptation (LoRA) module is truly compatible with a given large language model (LLM) can be daunting, especially when those LoRA parameters cannot be disclosed. 
-We introduce \texttt{zklora}, a library for generating zero-knowledge proofs that demonstrate correct LoRA-base model compatibility \emph{without sharing LoRA weights}. 
+We introduce \texttt{ZKLoRA}, a library for generating zero-knowledge proofs that demonstrate correct LoRA-base model compatibility \emph{without sharing LoRA weights}. 
 A key insight is that the \emph{verification step} for each LoRA module remains on the order of \textbf{1--2 seconds}, enabling repeated or batch checking at scale. 
-Our empirical evaluations confirm that \texttt{zklora} maintains this rapid per-module verification time even for multi-billion-parameter LLMs.
+Our empirical evaluations confirm that \texttt{ZKLoRA} maintains this rapid per-module verification time even for multi-billion-parameter LLMs.
 \end{abstract}
@@
 Traditionally, one might re-run an entire forward pass or inspect thousands of parameters to ensure correctness, which is infeasible for massive models. 
-\texttt{zklora} addresses this by generating a zero-knowledge proof of correctness for each LoRA module, guaranteeing that the private LoRA genuinely fits the public base model. 
-Crucially, \textbf{the verification stage for each LoRA module} in \texttt{zklora} remains about 1--2 seconds, even at scales of multi-billion parameter base models. 
+\texttt{ZKLoRA} addresses this by generating a zero-knowledge proof of correctness for each LoRA module, guaranteeing that the private LoRA genuinely fits the public base model. 
+Crucially, \textbf{the verification stage for each LoRA module} in \texttt{ZKLoRA} remains about 1--2 seconds, even at scales of multi-billion parameter base models. 
 This rapid, per-module check allows the Base Model User to efficiently, independently verify the compatibility of the private LoRA parameters.
@@
 
-We benchmarked \texttt{zklora} across several LLMs and smaller models with varying LoRA parameter counts.
+We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with varying LoRA parameter counts.
 Our focus is verifying that, regardless of total parameter scale, \emph{the per-module verification step} remains swift.
@@
 Although proof generation may scale with parameter size, verification for each LoRA module is consistently on the order of seconds.
-We consider this \emph{fast, per-module verification} to be \texttt{zklora}’s core advantage in production LLM environments.
+We consider this \emph{fast, per-module verification} to be \texttt{ZKLoRA}’s core advantage in production LLM environments.
 
 %------------------------------------------
-% 2. Ensuring LoRA–Base Model Compatibility with zklora
+% 2. Ensuring LoRA–Base Model Compatibility with ZKLoRA
 %------------------------------------------
@@
 \end{enumerate}
-However, these two parties must confirm the LoRA truly “fits” the base model. Using \texttt{zklora}, the LoRA Owner proves the adapter’s compatibility \emph{without} exposing private weights:
+However, these two parties must confirm the LoRA truly “fits” the base model. Using \texttt{ZKLoRA}, the LoRA Owner proves the adapter’s compatibility \emph{without} exposing private weights:
 
@@
 
+% Base Model User components
 \node[block, label=above:\textbf{Input}] (input) {$\mathbf{x}$};
 \node[block, right=2.0cm of input] (W1) {$\mathbf{W}_1$};
-\node[dashedblock, above=1.6cm of W1, label=above:\textbf{LoRA Owner}] (LoRA) {LoRA for Layer 1};
 \node[block, right=2.0cm of W1] (act) {ReLU};
@@
 
+% LoRA Owner components
+\node[dashedblock, above=1.6cm of W1, label=above:\textbf{LoRA Owner}] (LoRA) {LoRA for Layer 1};
+\node[dashedblock, above=1.6cm of act] (proofGen) {Proof Generation};
+\node[dashedblock, above=1.6cm of W2] (zkProof) {Zero-Knowledge Proof};
+
+% Arrows for Base Model User
 \draw[->] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
-\draw[->, dashed] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial acts} (LoRA.south);
-\draw[->, dashed] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
 \draw[->] (W1) -- node[above, font=\scriptsize]{$\mathbf{z}'$} (act);
@@
 
+% Arrows for LoRA Owner
+\draw[->, dashed] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial acts} (LoRA.south);
+\draw[->, dashed] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
+\draw[->, dashed] (LoRA) -- (proofGen);
+\draw[->, dashed] (proofGen) -- (zkProof);
+
+% Verification process
+\node[below=0.5cm of W2, font=\footnotesize, align=center] (verify) {Verification\\(1--2 sec)};
+\draw[->, dashed] (zkProof) -- (verify);
+
+% Base Model User boundary
 \node[draw, rounded corners, thick, color=blue!40!black,
@@
 ] (baseModelFit) {};
+
+% Additional annotations
+\node[above=0.5cm of zkProof, font=\footnotesize, align=center] (zkProofGen) {Zero-Knowledge\\Proof Generation};
+\draw[->, dashed] (zkProof) -- (zkProofGen);
+
 \end{tikzpicture}
-\caption{zklora inference flow on a 2-layer neural network where the first layer has private LoRA weights added.}
+\caption{ZKLoRA inference flow on a 2-layer neural network where the first layer has private LoRA weights added.
+The LoRA Owner generates a zero-knowledge proof to ensure compatibility, and the Base Model User verifies this proof quickly.}
 \label{fig:toy-mlp-lora}
@@
 
-\texttt{zklora} compiles an ONNX model (with LoRA included) into a constraint circuit. The user’s partial activations feed the circuit as inputs:
+\texttt{ZKLoRA} compiles an ONNX model (with LoRA included) into a constraint circuit. The user’s partial activations feed the circuit as inputs:
 
@@
 \paragraph{(5) Verification per Module.}
-Each LoRA module’s proof is tested with the verification key, taking \textbf{1--2 seconds}. This minimal overhead is \texttt{zklora}’s main advantage for frequent or large-scale checks.
+Each LoRA module’s proof is tested with the verification key, taking \textbf{1--2 seconds}. This minimal overhead is \texttt{ZKLoRA}’s main advantage for frequent or large-scale checks.
 
@@
 
-\texttt{zklora} provides a fast, robust mechanism to ensure that private LoRA modules remain consistent with a large base model.
+\texttt{ZKLoRA} provides a fast, robust mechanism to ensure that private LoRA modules remain consistent with a large base model.
 Our evaluations indicate that each LoRA module’s correctness can be verified in about 1--2 seconds, even for multi-billion-parameter LLMs.

### 2025-01-13 paper/figures.py

@@ -44,8 +44,8 @@ def plot_graph(
     """Creates a dotted line graph comparing (LoRA params in millions) to
     some measured time metric, and saves as PDF."""
     
-    plt.figure(figsize=(6,4), dpi=120)
-    plt.title(title, fontsize=12, fontweight='bold')
+    plt.figure(figsize=(10, 6), dpi=120)
+    plt.title(title, fontsize=16, fontweight='bold', color='darkorange')
 
     # We'll store the sorted x and y values in separate lists
     x_vals = []
@@ -64,25 +64,25 @@ def plot_graph(
         plt.plot(
             mx, my,
             marker='o',
-            markersize=8,
+            markersize=12,
             markeredgecolor='black',
-            markeredgewidth=0.8,
+            markeredgewidth=1.5,
             color=colors[name],
             linestyle='None',
             label=name  # We'll create a manual legend below
         )
 
     # Connect points with a faint dotted line to show progression
-    # We'll use a thick line and partial transparency for a "nicer" look
     plt.plot(
         x_vals, y_vals,
-        'k:',   # dotted line in black
-        alpha=0.6,
-        linewidth=2
+        color='darkorange',
+        linestyle='--',
+        alpha=0.8,
+        linewidth=2.5
     )
 
-    plt.xlabel(xlabel, fontsize=10)
-    plt.ylabel(ylabel, fontsize=10)
+    plt.xlabel(xlabel, fontsize=14, color='darkorange')
+    plt.ylabel(ylabel, fontsize=14, color='darkorange')
 
     # Create a manual legend with model-specific colors
     legend_handles = []
@@ -92,15 +92,16 @@ def plot_graph(
                 [0], [0],
                 marker='o',
                 markeredgecolor='black',
-                markeredgewidth=0.8,
+                markeredgewidth=1.5,
                 markerfacecolor=colors[name],
-                markersize=6,
+                markersize=10,
                 linestyle='None',
                 label=name
             )
         )
-    plt.legend(handles=legend_handles, loc='best', fontsize=9)
+    plt.legend(handles=legend_handles, loc='best', fontsize=12, frameon=False)
 
+    plt.grid(True, linestyle='--', alpha=0.5)
     plt.tight_layout()
     plt.savefig(output_file)
     plt.close()

### 2025-01-13 paper/main.tex
update

@@
 \begin{abstract}
-Verifying that a private Low-Rank Adaptation (LoRA) module is truly compatible with a given large language model (LLM) can be daunting, especially when those LoRA parameters cannot be disclosed. 
-We introduce \texttt{ZKLoRA}, a library for generating zero-knowledge proofs that demonstrate correct LoRA-base model compatibility \emph{without sharing LoRA weights}. 
-A key insight is that the \emph{verification step} for each LoRA module remains on the order of \textbf{1--2 seconds}, enabling repeated or batch checking at scale. 
-Our empirical evaluations confirm that \texttt{ZKLoRA} maintains this rapid per-module verification time even for multi-billion-parameter LLMs.
+    Parameter-efficient fine-tuning (PEFT) techniques, including Low-Rank Adaptation (LoRA), are widely adopted to customize large-scale language models in distributed training environments.
+A base model owner may outsource LoRA development to an external contributor, creating two requirements: the owner must verify that the LoRA update stems from the designated open-source model, and the contributor must protect proprietary parameters until compensation is assured.
+
+    We propose \textbf{ZKLoRA}, a zero-knowledge protocol that leverages polynomial commitments, succinct proofs, and advanced cryptographic designs to confirm LoRA–base model compatibility \emph{without} disclosing private LoRA weights.
+Our evaluations show that verification requires only \textbf{1--2 seconds} per LoRA module for typical large models.
+This short verification time enables trust-driven collaboration across decentralized infrastructures and contract-based training pipelines, ensuring that the delivered LoRA is valid while preserving the contributor’s intellectual property.
 \end{abstract}

### 2025-01-14 paper/main.tex
updated figures (text needs editing)

@@
 
-We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with varying LoRA parameter counts.
-Our focus is verifying that, regardless of total parameter scale, \emph{the per-module verification step} remains swift.
-Figures~\ref{fig:verify}, \ref{fig:settings}, and \ref{fig:proof} illustrate how total LoRA parameters correlate with:
+We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with different numbers of LoRA modules. 
+Our central question is how \emph{total} verification, proof generation, and settings times grow with \textbf{the number of LoRA modules} (\#LoRA), while also considering each LoRA's average parameter size.
+Figures~\ref{fig:verify_vs_numlora}, \ref{fig:proof_vs_numlora}, and \ref{fig:settings_vs_numlora} visualize this trade-off:
 \begin{itemize}
-    \item \textbf{Verification Time per Module} (Base Model User’s overhead),
-    \item \textbf{Total Settings Time} (preparatory steps and key generation),
-    \item \textbf{Total Proof Generation Time} (LoRA Owner’s overhead).
+    \item The x-axis is \textbf{the number of LoRA modules} for each model setup,
+    \item The y-axis is one of: \textit{total verification time}, \textit{total proof generation time}, or \textit{total settings time},
+    \item \textbf{Marker size} is proportional to the average LoRA size (in parameters).
+    \item The legend indicates each model’s average LoRA size with a label \textit{“Avg LoRA Size=xxK”}.
 \end{itemize}
@@
     \centering
-    \includegraphics[width=0.58\linewidth]{figs/fig_verify.pdf}
-    \caption{LoRA params (millions) vs.
-Total verification.
-Even at higher scales, verifying each LoRA module remains about 1--2 seconds.
-For example, even for a 70-billion parameter model, the total verification time of the additional LoRA parameters is only ~2 minutes.}
-    \label{fig:verify}
+    \includegraphics[width=0.65\linewidth]{figs/fig_verify_vs_numlora.pdf}
+    \caption{Total verification time (seconds) vs. number of LoRA modules, with dot size reflecting average LoRA size.}
+    \label{fig:verify_vs_numlora}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.58\linewidth]{figs/fig_settings.pdf}
-    \caption{LoRA params (millions) vs. total settings time. Each point corresponds to a different LLM or smaller model.}
-    \label{fig:settings}
+    \includegraphics[width=0.65\linewidth]{figs/fig_proof_vs_numlora.pdf}
+    \caption{Total proof generation time (seconds) vs. number of LoRA modules, with dot size reflecting average LoRA size.}
+    \label{fig:proof_vs_numlora}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.58\linewidth]{figs/fig_proof.pdf}
-    \caption{LoRA params (millions) vs. total proof generation time (LoRA Owner’s overhead).}
-    \label{fig:proof}
+    \includegraphics[width=0.65\linewidth]{figs/fig_settings_vs_numlora.pdf}
+    \caption{Total settings time (seconds) vs. number of LoRA modules, with dot size reflecting average LoRA size.}
+    \label{fig:settings_vs_numlora}
 \end{figure}
 
-Although proof generation may scale with parameter size, verification for each LoRA module is consistently on the order of seconds.
-We consider this \emph{fast, per-module verification} to be \texttt{ZKLoRA}’s core advantage in production LLM environments.
+From Figure~\ref{fig:verify_vs_numlora}, we see that models with a higher LoRA count (e.g., 80 modules for a large 70B model) can indeed lead to larger total verification time overall.
+However, the slope remains modest due to \texttt{ZKLoRA}’s succinct design.
+For instance, even if each module is verified individually at around 1--2 seconds, verifying 80 modules can be done in just a few minutes, which is still practical for real-world usage.
+
+Figures~\ref{fig:proof_vs_numlora} and \ref{fig:settings_vs_numlora} similarly show that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size).
+These two steps (proof generation on the LoRA Owner’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships.
+The \emph{Base Model User}, meanwhile, benefits from the relatively short verification overhead.
+
+Overall, these plots confirm that \texttt{ZKLoRA} can handle multiple LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.
 
@@
       align=center,
-      minimum width=1.8cm,
-      minimum height=0.9cm
+      minimum width=1.65cm,  % Decreased from 1.8cm to 1.65cm
+      minimum height=0.9cm,
+      fill=gray!10  % Light gray background for regular blocks
     },
@@
       font=\footnotesize,
-      fill=white,
-      minimum width=1.8cm,
+      fill=orange!10,  % Light orange background for LoRA block
+      minimum width=1.65cm,  % Decreased to match other blocks
       minimum height=0.9cm
@@
     arrow/.style={->, thick},
-    node distance=2.0cm
+    node distance=1.65cm  % Decreased from 1.8cm to 1.65cm
 ]
-
-% Base Model User components
-\node[block, label=above:\textbf{Input}] (input) {$\mathbf{x}$};
-\node[block, right=2.0cm of input] (W1) {$\mathbf{W}_1$};
-\node[block, right=2.0cm of W1] (act) {ReLU};
-\node[block, right=2.0cm of act] (W2) {$\mathbf{W}_2$};
-\node[block, label=above:\textbf{Output}, right=2.0cm of W2] (output) {$\mathbf{y}$};
-
-% LoRA Owner components
-\node[dashedblock, above=1.6cm of W1, label=above:\textbf{LoRA Owner}] (LoRA) {LoRA for Layer 1};
-\node[dashedblock, above=1.6cm of act] (proofGen) {Proof Generation};
-\node[dashedblock, above=1.6cm of W2] (zkProof) {Zero-Knowledge Proof};
-
-% Arrows for Base Model User
-\draw[->] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
-\draw[->] (W1) -- node[above, font=\scriptsize]{$\mathbf{z}'$} (act);
-\draw[->] (act) -- node[above, font=\scriptsize]{hidden} (W2);
-\draw[->] (W2) -- (output);
-
-% Arrows for LoRA Owner
-\draw[->, dashed] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial acts} (LoRA.south);
-\draw[->, dashed] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
-\draw[->, dashed] (LoRA) -- (proofGen);
-\draw[->, dashed] (proofGen) -- (zkProof);
-
-% Verification process
-\node[below=0.5cm of W2, font=\footnotesize, align=center] (verify) {Verification\\(1--2 sec)};
-\draw[->, dashed] (zkProof) -- (verify);
-
-% Base Model User boundary
+\node[block, label=above:\textcolor{teal}{\textbf{Input}}] (input) {$\mathbf{x}$};
+\node[block, right=1.65cm of input] (W1) {$\mathbf{W}_1$};
+\node[dashedblock, above=1.6cm of W1, label=above:\textcolor{orange!70!black}{\textbf{LoRA Owner}}] (LoRA) {LoRA for Layer 1};
+\node[block, right=1.65cm of W1] (act) {ReLU};
+\node[block, right=1.65cm of act] (W2) {$\mathbf{W}_2$};
+\node[block, label=above:\textcolor{teal}{\textbf{Output}}, right=1.65cm of W2] (output) {$\mathbf{y}$};
+\draw[->, teal!60!black] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
+\draw[->, dashed, orange!70!black] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial acts} (LoRA.south);
+\draw[->, dashed, orange!70!black] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
+\draw[->, teal!60!black] (W1) -- node[above, font=\scriptsize]{$\mathbf{z}'$} (act);
+\draw[->, teal!60!black] (act) -- node[above, font=\scriptsize]{hidden} (W2);
+\draw[->, teal!60!black] (W2) -- (output);
 \node[draw, rounded corners, thick, color=blue!40!black,
       fit=(input)(W1)(act)(W2)(output),
-      label={[font=\small, color=blue!40!black]above:\textbf{Base Model User}},
-      inner sep=0.4cm
+      label={[font=\small, color=blue!40!black, xshift=2cm]above:\textbf{Base Model User}},
+      inner sep=0.6cm
 ] (baseModelFit) {};
-
-% Additional annotations
-\node[above=0.5cm of zkProof, font=\footnotesize, align=center] (zkProofGen) {Zero-Knowledge\\Proof Generation};
-\draw[->, dashed] (zkProof) -- (zkProofGen);
-
 \end{tikzpicture}
-\caption{ZKLoRA inference flow on a 2-layer neural network where the first layer has private LoRA weights added.
-The LoRA Owner generates a zero-knowledge proof to ensure compatibility, and the Base Model User verifies this proof quickly.}
+\caption{zklora inference flow on a 2-layer neural network where the first layer has private LoRA weights added.}
 \label{fig:toy-mlp-lora}
@@
 \subsection{Low-Rank Adaptation (LoRA)}
-
 Low-Rank Adaptation (LoRA) \cite{hu2021lora} is a technique for parameter-efficient fine-tuning of large language models (LLMs) that injects small, low-rank adapter matrices into specific layers of a pre-trained model.
@@
 
+Beyond the clear advantage of reduced storage, LoRA also facilitates swapping multiple domain-specific adapters into a single base model, making it straightforward to maintain separate skill sets without instantiating an entire new copy of the model.
+These adapters can target specialized tasks (e.g., medical or legal text) with minimal overhead, driving LoRA’s widespread adoption.
+Yet verifying that a proprietary LoRA truly aligns with a base model (without revealing the adapter) remains problematic—precisely the gap \texttt{ZKLoRA} fills.
+
 \subsection{Incrementally Verifiable Computation}
 In a decentralized world, trust is a resource that is hard to achieve.
-In decentralized computation, we need to make sure the computation are being done, and are being correctly.
+In decentralized computation, we need to make sure the computations are both done and done correctly.
 In a seminal paper by Valiant (2008) \cite{valiant2008incrementally}, it was shown that proofs of knowledge can be used to assert the correct execution of general computations.
@@
 
-The main goal is IVC is to produce compact, updatable proofs of correctness for a sequence of computations, so that each new step in the computation can be verified on its own while building on the guarantees of the previous steps.
+The main goal of IVC is to produce compact, updatable proofs of correctness for a sequence of computations, so that each new step can be verified on its own while building on the guarantees of previous steps.
 This technique significantly reduces the verification overhead for long or evolving computations, which is invaluable in scenarios like decentralized networks, outsourced computation, and any application requiring frequent correctness checks.
@@
 It achieves efficiency through a folding scheme where the prover’s cryptographic costs are minimized and achieves zero-knowledge without relying on zkSNARKs.
-
 An IVC system allows the construction of proofs in zero-knowledge where the proofs reveal no information about the underlying computation or its inputs beyond the validity of the claim \cite{valiant2008incrementally}.

### 2025-01-14 paper/figures.py

@@ -1,37 +1,69 @@
 import matplotlib.pyplot as plt
 import os
 
-# Create an output folder for the figures
+# Create a folder for saving figures
 os.makedirs("figs", exist_ok=True)
 
-# Example data (dictionary of dictionaries):
-# Each key is a model name, value is a dict with:
-#   'params'   -> total LoRA params (integer)
-#   'settings' -> total settings/compile time (sec)
-#   'proof'    -> total proof generation time (sec)
-#   'verify'   -> total verification time (sec)
+# Example data:
+#   'lora_count'   -> number_of_loras (x-axis)
+#   'avg_params'   -> average LoRA params (float), used for marker size
+#   'total_verify' -> total verification time (sec)
+#   'total_proof'  -> total proof generation time (sec)
+#   'total_settings' -> total settings time (sec)
 data = {
-    'distilgpt2':       {'params': 589824,    'settings': 911.99,  'proof': 759.33,  'verify': 16.56},
-    'gpt2-lora1':       {'params': 2359296,   'settings': 2092.13, 'proof': 1675.58, 'verify': 32.79},
-    'Llama-3.2-1B':     {'params': 851968,    'settings': 1189.01, 'proof': 991.93,  'verify': 24.91},
-    'Llama-3.3-70B':    {'params': 11796480,  'settings': 4392.86, 'proof': 3749.76, 'verify': 123.11},
-    'Llama-3.1-8B':     {'params': 5242880,   'settings': 1836.83, 'proof': 1527.40, 'verify': 35.79},
-    'Mixtral-8x7B':     {'params': 10485760,  'settings': 2754.91, 'proof': 2357.61, 'verify': 44.30},
+    'distilgpt2': {
+        'lora_count': 24,
+        'avg_params': 24576.0,
+        'total_verify': 16.56,
+        'total_proof': 759.33,
+        'total_settings': 911.99
+    },
+    'gpt2': {
+        'lora_count': 48,
+        'avg_params': 49152.0,
+        'total_verify': 32.79,
+        'total_proof': 1675.58,
+        'total_settings': 2092.13
+    },
+    'Llama-3.2-1B': {
+        'lora_count': 32,
+        'avg_params': 26624.0,
+        'total_verify': 24.91,
+        'total_proof': 991.93,
+        'total_settings': 1189.01
+    },
+    'Llama-3.3-70B': {
+        'lora_count': 80,
+        'avg_params': 147456.0,
+        'total_verify': 123.11,
+        'total_proof': 3749.76,
[…]

### 2025-01-15 a_server.py
initial stage 3 + proofs (still times out after proof gen)

@@ -1,0 +1,252 @@
+#!/usr/bin/env python3
+"""
+User A: LoRA server for split inference & synchronous proof generation (no separate event loop thread).
+
+Main fix:
+ - We do `proof_res = asyncio.run(generate_proofs(...))` directly in the same handle_conn,
+   so the 'end_inference' response is only sent AFTER proofs finish. B won't get EOF prematurely.
+ - We also do config.use_cache = False to avoid 'past_key_values' errors.
+ - We only expose submodules that truly have LoRA parameters & end with c_attn (you can adapt).
+"""
+
+import argparse
+import socket
+import threading
+import pickle
+import time
+import os
+import glob
+import asyncio
+import numpy as np
+
+import torch
+import torch.nn as nn
+from transformers import AutoConfig, AutoModelForCausalLM
+from peft import PeftModel
+
+# from zklora with the MPI exporter & proof generator
+from zklora import (
+    export_lora_onnx_json_mpi,
+    generate_proofs,
+    resolve_proof_paths,
+)
+
+#################### Helpers ####################
+def read_file_as_bytes(path: str) -> bytes:
+    with open(path, "rb") as f:
+        return f.read()
+
+def strip_prefix(raw_name: str) -> str:
+    """
+    Remove 'base_model.model.', 'base_model.', 'model.' from the submodule name.
+    Example:
+      'base_model.model.transformer.h.0.attn.c_attn' => 'transformer.h.0.attn.c_attn'
+    """
+    name2 = raw_name
+    for pfx in ["base_model.model.", "base_model.", "model."]:
+        if name2.startswith(pfx):
+            name2 = name2[len(pfx):]
+    return name2.strip()
+
+class LoRAServer:
+    def __init__(self, base_model_name: str, lora_model_id: str, out_dir: str):
+        self.out_dir = out_dir
+        os.makedirs(self.out_dir, exist_ok=True)
+
+        # 1) Load model config, disable cache => no 'past_key_values'
+        config = AutoConfig.from_pretrained(base_model_name)
+        config.use_cache = False
+        base_model = AutoModelForCausalLM.from_config(config)
+        base_model.config.use_cache = False
+        base_model.eval()
+
+        # 2) Load LoRA
+        self.peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
+        self.peft_model.eval()
+
+        # 3) Build submodule dict for actual LoRA submodules, e.g. 'transformer.h.0.attn.c_attn'
[…]

### 2025-01-15 b_server.py

@@ -1,0 +1,258 @@
+#!/usr/bin/env python3
+"""
+User B: 
+ - Receives submodules from A (like 'transformer.h.0.attn.c_attn' etc.).
+ - Patches them => forward => triggers A's submodules => .onnx => synchronous proof gen in A => returns proofs => B reads them
+ - We do config.use_cache=False so no 'past_key_values'.
+ - If you pass --verify_proofs, we do local batch_verify_proofs afterwards.
+"""
+
+import argparse
+import socket
+import pickle
+import time
+import os
+
+import torch
+import torch.nn as nn
+from transformers import AutoModelForCausalLM, AutoTokenizer, AutoConfig
+from peft.tuners.lora.layer import LoraLayer
+
+from zklora import batch_verify_proofs
+
+class BToAComm:
+    def __init__(self, host_a="127.0.0.1", port_a=30000):
+        self.host_a = host_a
+        self.port_a = port_a
+
+    def init_request(self):
+        data = {"request_type": "init_request"}
+        resp = self.send_and_recv(data)
+        return resp.get("injection_points", [])
+
+    def lora_forward(self, sub_name, arr):
+        req = {
+            "request_type":"lora_forward",
+            "submodule_name": sub_name,
+            "input_array": arr
+        }
+        resp = self.send_and_recv(req)
+        return resp.get("output_array", None)
+
+    def end_inference(self):
+        req = {"request_type":"end_inference"}
+        resp = self.send_and_recv(req)
+        return resp.get("proof_map", {})
+
+    def send_and_recv(self, data_dict):
+        s = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+        s.connect((self.host_a, self.port_a))
+        bin_req = pickle.dumps(data_dict)
+        s.sendall(bin_req)
+        s.shutdown(socket.SHUT_WR)
+
+        buffer = b""
+        s.settimeout(2400.0)  # give more time if proof generation is slow
+        while True:
+            try:
+                chunk = s.recv(4096)
+            except socket.timeout:
+                break
+            if not chunk:
+                break
+            buffer += chunk
+        s.close()
+
+        if not buffer:
+            raise RuntimeError("[B] No data from A (EOF). Possibly A took too long or closed early.")
+
+        resp = pickle.loads(buffer)
+        return resp
+
+class RemoteLoRAWrappedModule(nn.Module):
[…]

### 2025-01-15 zklora/__init__.py

@@ -1,10 +1,18 @@
 from .lora_onnx_exporter import export_lora_submodules
 from .zk_proof_generator import generate_proofs, batch_verify_proofs, ProofPaths, resolve_proof_paths
+from .mpi_lora_onnx_exporter import (
+    normalize_lora_matrices_mpi,
+    LoraShapeTransformerMPI,
+    export_lora_onnx_json_mpi,
+)
 
 __all__ = [
     'export_lora_submodules',
     'generate_proofs',
     'batch_verify_proofs',
     'ProofPaths',
-    'resolve_proof_paths'
+    'resolve_proof_paths',
+    'normalize_lora_matrices_mpi',
+    'LoraShapeTransformerMPI',
+    'export_lora_onnx_json_mpi',
 ]

### 2025-01-15 a_side_mpi_sample_script.py
make mpi with proofs into library + minimal scripts in home dir

@@ -1,0 +1,31 @@
+import argparse
+import threading
+import time
+
+from zklora import LoRAServer, AServerTCP
+
+def main():
+    import argparse
+    parser = argparse.ArgumentParser()
+    parser.add_argument("--host", default="127.0.0.1")
+    parser.add_argument("--port_a", type=int, default=30000)
+    parser.add_argument("--base_model", default="distilgpt2")
+    parser.add_argument("--lora_model_id", default="ng0-k1/distilgpt2-finetuned-es")
+    parser.add_argument("--out_dir", default="a-out")
+    args = parser.parse_args()
+
+    stop_event = threading.Event()
+    server_obj = LoRAServer(args.base_model, args.lora_model_id, args.out_dir)
+    t = AServerTCP(args.host, args.port_a, server_obj, stop_event)
+    t.start()
+
+    try:
+        while True:
+            time.sleep(1)
+    except KeyboardInterrupt:
+        print("[A-Server] stopping.")
+    stop_event.set()
+    t.join()
+
+if __name__ == "__main__":
+    main()

### 2025-01-15 b_side_mpi_sample_script.py

@@ -1,0 +1,32 @@
+import argparse
+
+from zklora import BaseModelClient, batch_verify_proofs
+
+def main():
+    parser = argparse.ArgumentParser()
+    parser.add_argument("--host_a", default="127.0.0.1")
+    parser.add_argument("--port_a", type=int, default=30000)
+    parser.add_argument("--base_model", default="distilgpt2")
+    parser.add_argument("--combine_mode", choices=["replace","add_delta"], default="add_delta")
+    parser.add_argument("--verify_proofs", action="store_true")
+    args = parser.parse_args()
+
+    client = BaseModelClient(args.base_model, args.host_a, args.port_a, args.combine_mode)
+    client.init_and_patch()
+
+    # forward pass => triggers submodule calls => A accumulates => .onnx => proofs
+    text = "Hello World, this is a LoRA test."
+
+    loss_val = client.forward_loss(text)
+    print(f"[B] final loss => {loss_val:.4f}")
+
+    out_dir = client.end_inference_and_retrieve_proofs()
+    print("[B] local proofs =>", out_dir)
+
+    if args.verify_proofs:
+        print("[B] verifying proofs in", out_dir)
+        total_t, c = batch_verify_proofs(proof_dir=out_dir, verbose=True)
+        print(f"[B] verified {c} proof(s) in {total_t:.2f} sec.")
+
+if __name__=="__main__":
+    main()

### 2025-01-15 zklora/__init__.py

@@ -5,6 +5,9 @@ from .mpi_lora_onnx_exporter import (
     LoraShapeTransformerMPI,
     export_lora_onnx_json_mpi,
 )
+from .a_server import LoRAServer, AServerTCP
+from .b_server import BaseModelClient
+
 
 __all__ = [
     'export_lora_submodules',
@@ -15,4 +18,7 @@ __all__ = [
     'normalize_lora_matrices_mpi',
     'LoraShapeTransformerMPI',
     'export_lora_onnx_json_mpi',
+    'LoRAServer',
+    'AServerTCP',
+    'BaseModelClient',
 ]

### 2025-01-15 zklora/a-server/__init__.py

@@ -1,0 +1,214 @@
+import argparse
+import socket
+import threading
+import pickle
+import time
+import os
+import glob
+import asyncio
+import numpy as np
+
+import torch
+import torch.nn as nn
+from transformers import AutoConfig, AutoModelForCausalLM
+from peft import PeftModel
+
+# from zklora with the MPI exporter & proof generator
+from ..zklora import (
+    export_lora_onnx_json_mpi,
+    generate_proofs,
+    resolve_proof_paths,
+)
+
+def read_file_as_bytes(path: str) -> bytes:
+    with open(path, "rb") as f:
+        return f.read()
+
+def strip_prefix(raw_name: str) -> str:
+    """
+    Remove 'base_model.model.', 'base_model.', 'model.' from the submodule name.
+    Example:
+      'base_model.model.transformer.h.0.attn.c_attn' => 'transformer.h.0.attn.c_attn'
+    """
+    name2 = raw_name
+    for pfx in ["base_model.model.", "base_model.", "model."]:
+        if name2.startswith(pfx):
+            name2 = name2[len(pfx):]
+    return name2.strip()
+
+class LoRAServer:
+    def __init__(self, base_model_name: str, lora_model_id: str, out_dir: str):
+        self.out_dir = out_dir
+        os.makedirs(self.out_dir, exist_ok=True)
+
+        # 1) Load model config, disable cache => no 'past_key_values'
+        config = AutoConfig.from_pretrained(base_model_name)
+        config.use_cache = False
+        base_model = AutoModelForCausalLM.from_config(config)
+        base_model.config.use_cache = False
+        base_model.eval()
+
+        # 2) Load LoRA
+        self.peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
+        self.peft_model.eval()
+
+        # 3) Build submodule dict for actual LoRA submodules, e.g. 'transformer.h.0.attn.c_attn'
+        self.submodules = {}
+        for raw_name, module in self.peft_model.named_modules():
+            if any("lora" in pname.lower() for pname, _ in module.named_parameters()):
+                sname = strip_prefix(raw_name)
+                # skip if empty or doesn't contain '.' or doesn't end in c_attn
+                if not sname or "." not in sname:
+                    continue
+                if not sname.endswith("c_attn"):
+                    continue
+                self.submodules[sname] = module
+
+        self.session_data = {}  # {sub_name => [np arrays]}
+
+    def list_lora_injection_points(self):
[…]

### 2025-01-15 zklora/b-server/__init__.py

@@ -1,0 +1,160 @@
+import argparse
+import socket
+import pickle
+import time
+import os
+
+import torch
+import torch.nn as nn
+from transformers import AutoModelForCausalLM, AutoTokenizer, AutoConfig
+from peft.tuners.lora.layer import LoraLayer
+
+from ..zklora import batch_verify_proofs
+
+class BToAComm:
+    def __init__(self, host_a="127.0.0.1", port_a=30000):
+        self.host_a = host_a
+        self.port_a = port_a
+
+    def init_request(self):
+        data = {"request_type": "init_request"}
+        resp = self.send_and_recv(data)
+        return resp.get("injection_points", [])
+
+    def lora_forward(self, sub_name, arr):
+        req = {
+            "request_type":"lora_forward",
+            "submodule_name": sub_name,
+            "input_array": arr
+        }
+        resp = self.send_and_recv(req)
+        return resp.get("output_array", None)
+
+    def end_inference(self):
+        req = {"request_type":"end_inference"}
+        resp = self.send_and_recv(req)
+        return resp.get("proof_map", {})
+
+    def send_and_recv(self, data_dict):
+        s = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+        s.connect((self.host_a, self.port_a))
+        bin_req = pickle.dumps(data_dict)
+        s.sendall(bin_req)
+        s.shutdown(socket.SHUT_WR)
+
+        buffer = b""
+        s.settimeout(1200.0)  # give more time if proof generation is slow
+        while True:
+            try:
+                chunk = s.recv(4096)
+            except socket.timeout:
+                break
+            if not chunk:
+                break
+            buffer += chunk
+        s.close()
+
+        if not buffer:
+            raise RuntimeError("[B] No data from A (EOF). Possibly A took too long or closed early.")
+
+        resp = pickle.loads(buffer)
+        return resp
+
+class RemoteLoRAWrappedModule(nn.Module):
+    def __init__(self, sub_name, local_sub, comm: BToAComm, combine_mode="replace"):
+        super().__init__()
+        self.sub_name = sub_name
+        self.local_sub = local_sub
+        self.comm = comm
+        self.combine_mode = combine_mode
+
+    def forward(self, x: torch.Tensor):
+        with torch.no_grad():
+            base_out = self.local_sub(x)
+        arr = x.cpu().numpy()
+        remote_out = self.comm.lora_forward(self.sub_name, arr)
+        if remote_out is None:
[…]

### 2025-01-15 zklora/a_server/__init__.py
fix library import paths

@@ -14,11 +14,8 @@ from transformers import AutoConfig, AutoModelForCausalLM
 from peft import PeftModel
 
 # from zklora with the MPI exporter & proof generator
-from ..zklora import (
-    export_lora_onnx_json_mpi,
-    generate_proofs,
-    resolve_proof_paths,
-)
+from ..zk_proof_generator import generate_proofs, resolve_proof_paths
+from ..mpi_lora_onnx_exporter import export_lora_onnx_json_mpi
 
 def read_file_as_bytes(path: str) -> bytes:
     with open(path, "rb") as f:

### 2025-01-15 zklora/b_server/__init__.py

@@ -9,7 +9,7 @@ import torch.nn as nn
 from transformers import AutoModelForCausalLM, AutoTokenizer, AutoConfig
 from peft.tuners.lora.layer import LoraLayer
 
-from ..zklora import batch_verify_proofs
+from ..zk_proof_generator import batch_verify_proofs
 
 class BToAComm:
     def __init__(self, host_a="127.0.0.1", port_a=30000):

### 2025-01-16 b_side_mpi_sample_script.py
no longer send proof files from A -> B

@@ -20,13 +20,8 @@ def main():
     loss_val = client.forward_loss(text)
     print(f"[B] final loss => {loss_val:.4f}")
 
-    out_dir = client.end_inference_and_retrieve_proofs()
-    print("[B] local proofs =>", out_dir)
-
-    if args.verify_proofs:
-        print("[B] verifying proofs in", out_dir)
-        total_t, c = batch_verify_proofs(proof_dir=out_dir, verbose=True)
-        print(f"[B] verified {c} proof(s) in {total_t:.2f} sec.")
+    client.end_inference()
+    print("[B] done. B can now fetch proof files from A and verify proofs.")
 
 if __name__=="__main__":
     main()

### 2025-01-16 zklora/a_server/__init__.py

@@ -110,8 +110,9 @@ class LoRAServer:
         if not proof_res:
             print("[A] No proofs generated or something went wrong.")
         else:
-            print("[A] Proof generation done, reading them now...")
+            print("[A] Proof generation done.")
 
+        """
         proof_map = {}
         onnx_files = glob.glob(os.path.join(self.out_dir, "*.onnx"))
         if not onnx_files:
@@ -133,6 +134,8 @@ class LoRAServer:
             proof_map[base_name] = sub_dict
 
         return proof_map
+        """
+        return
 
 class AServerTCP(threading.Thread):
     def __init__(self, host, port, lora_server: LoRAServer, stop_event):
@@ -184,10 +187,19 @@ class AServerTCP(threading.Thread):
                     "output_array": out.cpu().numpy()
                 }
 
+            #elif rtype == "end_inference":
+            #    # Synchronously finalize proofs => no concurrency issues
+            #    proof_map = self.lora_server.finalize_proofs_and_collect()
+            #    resp = {"response_type":"end_inference_proofs","proof_map": proof_map}
+
             elif rtype == "end_inference":
-                # Synchronously finalize proofs => no concurrency issues
-                proof_map = self.lora_server.finalize_proofs_and_collect()
-                resp = {"response_type":"end_inference_proofs","proof_map": proof_map}
+                # generate proofs locally
+                self.lora_server.finalize_proofs_and_collect()
+                ack_resp = {
+                    "response_type": "end_inference_ack",
+                    "message": "A finished proof generation locally. B can close."
+                }
+
             else:
                 resp = {"error": f"Unknown request_type {rtype}"}
 

### 2025-01-16 zklora/b_server/__init__.py

@@ -31,9 +31,9 @@ class BToAComm:
         return resp.get("output_array", None)
 
     def end_inference(self):
-        req = {"request_type":"end_inference"}
-        resp = self.send_and_recv(req)
-        return resp.get("proof_map", {})
+        req = {"request_type": "end_inference"}
+        resp = self.send_and_recv(req)#, timeout=600.0)  # might be slower if proof gen is big
+        return resp
 
     def send_and_recv(self, data_dict):
         s = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
@@ -133,28 +133,7 @@ class BaseModelClient:
             out = self.model(in_ids, labels=in_ids)
         return out.loss.item()
 
-    def end_inference_and_retrieve_proofs(self):
-        proof_map = self.comm.end_inference()
-        out_dir = "b-out"
-        os.makedirs(out_dir, exist_ok=True)
-
-        for base_name, fdict in proof_map.items():
-            pf = os.path.join(out_dir, f"{base_name}.pf")
-            with open(pf, "wb") as fp:
-                fp.write(fdict["proof"])
-
-            st = os.path.join(out_dir, f"{base_name}_settings.json")
-            with open(st, "wb") as fp:
-                fp.write(fdict["settings"])
-
-            vk = os.path.join(out_dir, f"{base_name}.vk")
-            with open(vk, "wb") as fp:
-                fp.write(fdict["verification_key"])
-
-            srs = os.path.join(out_dir, "kzg.srs")
-            with open(srs, "wb") as fp:
-                fp.write(fdict["srs"])
-
-            print(f"[B] wrote proof artifacts for '{base_name}' => {out_dir}/")
-
-        return out_dir
+    def end_inference(self):
+        # 1) request end_inference => server finalizes proofs locally => returns ack
+        resp = self.comm.end_inference()
+        print("[B] end_inference => got ack:", resp)

### 2025-01-16 zklora/a_server/__init__.py
fix typo

@@ -195,7 +195,7 @@ class AServerTCP(threading.Thread):
             elif rtype == "end_inference":
                 # generate proofs locally
                 self.lora_server.finalize_proofs_and_collect()
-                ack_resp = {
+                resp = {
                     "response_type": "end_inference_ack",
                     "message": "A finished proof generation locally. B can close."
                 }

### 2025-01-16 verify_proofs.py
add independent proof verificaiton script

@@ -1,0 +1,26 @@
+import argparse
+
+from zklora import batch_verify_proofs
+
+def main():
+    parser.add_argument(
+        "--proof_dir",
+        type=str,
+        default="proof_artifacts",
+        help="Directory containing proof files (.pf), plus settings, vk, srs."
+    )
+    parser.add_argument(
+        "--verbose",
+        action="store_true",
+        help="Print more details during verification."
+    )
+    args = parser.parse_args()
+
+    total_verify_time, num_proofs = batch_verify_proofs(
+        proof_dir=args.proof_dir,
+        verbose=args.verbose
+    )
+    print(f"Done verifying {num_proofs} proofs. Total time: {total_verify_time:.2f}s")
+
+if __name__ == "__main__":
+    main()

### 2025-01-16 b_side_mpi_sample_script.py
remove import

@@ -1,6 +1,6 @@
 import argparse
 
-from zklora import BaseModelClient, batch_verify_proofs
+from zklora import BaseModelClient
 
 def main():
     parser = argparse.ArgumentParser()

### 2025-01-16 verify_proofs.py
only leave imports in `__init__.py` necessary for minimal mpi sample scripts; fix verification script error

@@ -3,6 +3,9 @@ import argparse
 from zklora import batch_verify_proofs
 
 def main():
+    parser = argparse.ArgumentParser(
+        description="Verify LoRA proof artifacts in a given directory."
+    )
     parser.add_argument(
         "--proof_dir",
         type=str,

### 2025-01-16 zklora/__init__.py

@@ -1,23 +1,10 @@
-from .lora_onnx_exporter import export_lora_submodules
-from .zk_proof_generator import generate_proofs, batch_verify_proofs, ProofPaths, resolve_proof_paths
-from .mpi_lora_onnx_exporter import (
-    normalize_lora_matrices_mpi,
-    LoraShapeTransformerMPI,
-    export_lora_onnx_json_mpi,
-)
+from .zk_proof_generator import batch_verify_proofs
 from .a_server import LoRAServer, AServerTCP
 from .b_server import BaseModelClient
 
 
 __all__ = [
-    'export_lora_submodules',
-    'generate_proofs',
     'batch_verify_proofs',
-    'ProofPaths',
-    'resolve_proof_paths',
-    'normalize_lora_matrices_mpi',
-    'LoraShapeTransformerMPI',
-    'export_lora_onnx_json_mpi',
     'LoRAServer',
     'AServerTCP',
     'BaseModelClient',

### 2025-01-16 zklora/a_server/__init__.py
updated readme; removed some comments from a_server.__init__

@@ -112,29 +112,6 @@ class LoRAServer:
         else:
             print("[A] Proof generation done.")
 
-        """
-        proof_map = {}
-        onnx_files = glob.glob(os.path.join(self.out_dir, "*.onnx"))
-        if not onnx_files:
-            print(f"[A] STILL no ONNX files found in {self.out_dir}. Possibly submodules never triggered.")
-        for onnx_path in onnx_files:
-            base_name = os.path.splitext(os.path.basename(onnx_path))[0]
-            paths = resolve_proof_paths(self.out_dir, base_name)
-            if not paths:
-                continue
-            sub_dict = {}
-            try:
-                sub_dict["proof"] = read_file_as_bytes(paths.proof)
-                sub_dict["settings"] = read_file_as_bytes(paths.settings)
-                sub_dict["verification_key"] = read_file_as_bytes(paths.verification_key)
-                sub_dict["srs"] = read_file_as_bytes(paths.srs)
-            except FileNotFoundError:
-                print(f"[A] Missing file(s) for base_name={base_name}, skipping.")
-                continue
-            proof_map[base_name] = sub_dict
-
-        return proof_map
-        """
         return
 
 class AServerTCP(threading.Thread):
@@ -186,11 +163,6 @@ class AServerTCP(threading.Thread):
                     "response_type":"lora_forward_response",
                     "output_array": out.cpu().numpy()
                 }
-
-            #elif rtype == "end_inference":
-            #    # Synchronously finalize proofs => no concurrency issues
-            #    proof_map = self.lora_server.finalize_proofs_and_collect()
-            #    resp = {"response_type":"end_inference_proofs","proof_map": proof_map}
 
             elif rtype == "end_inference":
                 # generate proofs locally

### 2025-01-16 split-inference/a_server.py
rename a/b server; delete split inference dir

@@ -1,158 +1,0 @@
-#!/usr/bin/env python3
-"""
-File: a_server.py
-
-User A's code:
-  - Loads a PEFT LoRAServer (distilgpt2 + LoRA adapter).
-  - Runs a 'UserAListener' thread that continuously scans for request_*.pkl
-    in a shared folder and writes response_*.pkl with results.
-
-Usage Example:
-  python a_server.py --base_model distilgpt2 --lora_model_id my-lora-distilgpt2
-"""
-
-import os
-import time
-import uuid
-import pickle
-import glob
-import threading
-import argparse
-
-import torch
-from transformers import AutoConfig, AutoModelForCausalLM
-from peft import PeftModel
-
-
-def strip_base_prefix(name: str) -> str:
-    """
-    If submodule name starts with 'base_model.model.', remove that prefix
-    so it aligns with the raw GPT2 submodule naming.
-    """
-    prefix = "base_model.model."
-    if name.startswith(prefix):
-        return name[len(prefix):]
-    return name
-
-
-class LoRAServer:
-    """
-    Loads a base model + LoRA adapter via PEFT, and stores submodule references
-    keyed by the *stripped* name (e.g., 'transformer.h.0.attn.c_attn').
-    """
-
-    def __init__(self, base_model_name, lora_model_id):
-        # 1) Load base config/model
-        config = AutoConfig.from_pretrained(base_model_name)
-        base_model = AutoModelForCausalLM.from_config(config)
-        base_model.eval()
-
-        # 2) Load LoRA adapter
-        self.peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
-        self.peft_model.eval()
-
-        # 3) Build submodule dict
-        self.lora_submodules = {}
-        for raw_name, module in self.peft_model.named_modules():
-            if any("lora" in pname.lower() for pname, _ in module.named_parameters()):
-                fixed_name = strip_base_prefix(raw_name)
-                self.lora_submodules[fixed_name] = module
-
-    def list_lora_injection_points(self):
-        return list(self.lora_submodules.keys())
-
-    def apply_lora(self, submodule_name: str, input_tensor: torch.Tensor) -> torch.Tensor:
-        if submodule_name not in self.lora_submodules:
-            raise ValueError(f"No LoRA submodule named '{submodule_name}'")
-        with torch.no_grad():
-            out = self.lora_submodules[submodule_name](input_tensor)
-        return out
-
-
[…]

### 2025-01-16 split-inference/b_server.py

@@ -1,184 +1,0 @@
-#!/usr/bin/env python3
-"""
-File: b_client.py
-
-User B's code:
-  - Loads the base distilgpt2 model (no LoRA).
-  - Asks User A (via file-based requests) for the LoRA injection points.
-  - Monkey-patches the relevant submodules to call A for LoRA transformations.
-  - Then does a forward pass to compute token-level loss on a sample text.
-
-Usage:
-  python b_client.py
-"""
-
-import os
-import time
-import uuid
-import pickle
-import argparse
-
-import torch
-import torch.nn as nn
-from transformers import AutoTokenizer, AutoModelForCausalLM
-
-
-class UserBFileHandler:
-    """
-    Creates request_*.pkl in a shared folder, waits for response_*.pkl from A.
-    """
-
-    def __init__(self, comm_folder="./temp_communication"):
-        self.comm_folder = comm_folder
-        os.makedirs(self.comm_folder, exist_ok=True)
-
-    def send_init_request(self) -> list:
-        request_id = str(uuid.uuid4())[:8]
-        request_path = os.path.join(self.comm_folder, f"request_{request_id}.pkl")
-        data = {
-            "request_id": request_id,
-            "request_type": "init_request",
-        }
-        with open(request_path, "wb") as f:
-            pickle.dump(data, f)
-
-        # Wait for response
-        response_path = os.path.join(self.comm_folder, f"response_{request_id}.pkl")
-        while not os.path.exists(response_path):
-            time.sleep(0.1)
-
-        with open(response_path, "rb") as f:
-            resp_data = pickle.load(f)
-        os.remove(response_path)
-
-        return resp_data["injection_points"]
-
-    def send_lora_request_and_wait(self, submodule_name: str, input_tensor: torch.Tensor) -> torch.Tensor:
-        request_id = str(uuid.uuid4())[:8]
-        req_path = os.path.join(self.comm_folder, f"request_{request_id}.pkl")
-        data = {
-            "request_id": request_id,
-            "request_type": "lora_forward",
-            "submodule_name": submodule_name,
-            "input_array": input_tensor.cpu().numpy(),
-        }
-        with open(req_path, "wb") as f:
-            pickle.dump(data, f)
-
-        # Wait for response
-        resp_path = os.path.join(self.comm_folder, f"response_{request_id}.pkl")
-        while not os.path.exists(resp_path):
-            time.sleep(0.1)
-
[…]

### 2025-01-16 split-inference/loss_check.py

@@ -1,39 +1,0 @@
-import torch
-from transformers import AutoTokenizer, AutoModelForCausalLM
-from peft import PeftModel
-
-def compute_loss(model, tokenizer, text: str) -> float:
-    """
-    Compute the cross-entropy loss of 'text' using the given LoRA-PEFT model.
-    """
-    # Tokenize the input
-    inputs = tokenizer(text, return_tensors="pt")
-    input_ids = inputs["input_ids"]
-    labels = input_ids.clone()  # the usual approach for causal LM loss
-
-    # Forward pass with labels => model computes cross-entropy for each token
-    with torch.no_grad():
-        outputs = model(input_ids, labels=labels)
-        loss = outputs.loss  # average cross-entropy over the sequence
-    return loss.item()
-
-def main():
-    # 1) Load the base model
-    base_model_name = "distilgpt2"
-    base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
-    tokenizer = AutoTokenizer.from_pretrained(base_model_name)
-
-    # 2) Load the LoRA PEFT adapter
-    lora_model_id = "ng0-k1/distilgpt2-finetuned-es"
-    peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
-    peft_model.eval()
-
-    # 3) Sample text (Spanish, given the fine-tuned es model)
-    text = "funky chunky monkey"
-
-    # 4) Compute and print the loss
-    loss_value = compute_loss(peft_model, tokenizer, text)
-    print(f"Loss on sample text: {loss_value:.4f}")
-
-if __name__ == "__main__":
-    main()

### 2025-01-16 split-inference/split_inference.py

@@ -1,341 +1,0 @@
-#!/usr/bin/env python3
-"""
-final_split_inference.py
-
-A concise, minimal script for split inference with:
- - LoRA'd submodules in c_attn only,
- - combine_mode=add_delta,
- - verifying remote_out is smaller than base_out,
- - printing final cross-entropy vs. direct local LoRA.
-
-Usage:
-  python final_split_inference.py \
-    --base_model distilgpt2 \
-    --lora_model ng0-k1/distilgpt2-finetuned-es \
-    --combine_mode add_delta \
-    --text "Hello world, this is a LoRA test."
-"""
-
-import threading
-import os
-import sys
-import time
-import uuid
-import pickle
-import glob
-import argparse
-import random
-import numpy as np
-import torch
-import torch.nn as nn
-
-from transformers import (
-    AutoConfig,
-    AutoModelForCausalLM,
-    AutoTokenizer,
-)
-from peft import PeftModel
-
-###################################
-# Deterministic seed
-###################################
-SEED = 1234
-def set_global_seed(s=1234):
-    random.seed(s)
-    np.random.seed(s)
-    torch.manual_seed(s)
-    if torch.cuda.is_available():
-        torch.cuda.manual_seed_all(s)
-
-set_global_seed(SEED)
-
-def strip_base_prefix(name: str):
-    p = "base_model.model."
-    if name.startswith(p):
-        return name[len(p):]
-    return name
-
-###################################
-# LoRAServer
-###################################
-class LoRAServer:
-    def __init__(self, base_model, lora_model, debug=False):
-        config = AutoConfig.from_pretrained(base_model)
-        base = AutoModelForCausalLM.from_config(config)
-        base.eval()
-
-        self.peft_model = PeftModel.from_pretrained(base, lora_model)
-        self.peft_model.eval()
-
-        # zero out any dropout
-        for m in self.peft_model.modules():
-            if hasattr(m, "lora_dropout"):
-                m.lora_dropout.p = 0.0
-
-        self.lora_subs = {}
-        for raw_name, mod in self.peft_model.named_modules():
-            if any("lora" in pn.lower() for pn, _ in mod.named_parameters()):
-                fixed = strip_base_prefix(raw_name)
-                self.lora_subs[fixed] = mod
-
-        if debug:
-            print("[LoRAServer Debug] submodules with LoRA:\n")
-            for k in sorted(self.lora_subs.keys()):
-                print(" ", k)
-
-    def list_lora_injection_points(self):
-        return list(self.lora_subs.keys())
-
[…]

### 2025-01-16 zklora/__init__.py

@@ -1,6 +1,6 @@
 from .zk_proof_generator import batch_verify_proofs
-from .a_server import LoRAServer, AServerTCP
-from .b_server import BaseModelClient
+from .lora_owner_mpi import LoRAServer, AServerTCP
+from .base_model_user_mpi import BaseModelClient
 
 
 __all__ = [

### 2025-01-16 a_server.py
delete standalone a/b server scripts

@@ -1,252 +1,0 @@
-#!/usr/bin/env python3
-"""
-User A: LoRA server for split inference & synchronous proof generation (no separate event loop thread).
-
-Main fix:
- - We do `proof_res = asyncio.run(generate_proofs(...))` directly in the same handle_conn,
-   so the 'end_inference' response is only sent AFTER proofs finish. B won't get EOF prematurely.
- - We also do config.use_cache = False to avoid 'past_key_values' errors.
- - We only expose submodules that truly have LoRA parameters & end with c_attn (you can adapt).
-"""
-
-import argparse
-import socket
-import threading
-import pickle
-import time
-import os
-import glob
-import asyncio
-import numpy as np
-
-import torch
-import torch.nn as nn
-from transformers import AutoConfig, AutoModelForCausalLM
-from peft import PeftModel
-
-# from zklora with the MPI exporter & proof generator
-from zklora import (
-    export_lora_onnx_json_mpi,
-    generate_proofs,
-    resolve_proof_paths,
-)
-
-#################### Helpers ####################
-def read_file_as_bytes(path: str) -> bytes:
-    with open(path, "rb") as f:
-        return f.read()
-
-def strip_prefix(raw_name: str) -> str:
-    """
-    Remove 'base_model.model.', 'base_model.', 'model.' from the submodule name.
-    Example:
-      'base_model.model.transformer.h.0.attn.c_attn' => 'transformer.h.0.attn.c_attn'
-    """
-    name2 = raw_name
-    for pfx in ["base_model.model.", "base_model.", "model."]:
-        if name2.startswith(pfx):
-            name2 = name2[len(pfx):]
-    return name2.strip()
-
-class LoRAServer:
-    def __init__(self, base_model_name: str, lora_model_id: str, out_dir: str):
-        self.out_dir = out_dir
-        os.makedirs(self.out_dir, exist_ok=True)
-
-        # 1) Load model config, disable cache => no 'past_key_values'
-        config = AutoConfig.from_pretrained(base_model_name)
-        config.use_cache = False
-        base_model = AutoModelForCausalLM.from_config(config)
-        base_model.config.use_cache = False
-        base_model.eval()
-
-        # 2) Load LoRA
-        self.peft_model = PeftModel.from_pretrained(base_model, lora_model_id)
-        self.peft_model.eval()
-
-        # 3) Build submodule dict for actual LoRA submodules, e.g. 'transformer.h.0.attn.c_attn'
-        self.submodules = {}
[…]

### 2025-01-16 b_server.py

@@ -1,258 +1,0 @@
-#!/usr/bin/env python3
-"""
-User B: 
- - Receives submodules from A (like 'transformer.h.0.attn.c_attn' etc.).
- - Patches them => forward => triggers A's submodules => .onnx => synchronous proof gen in A => returns proofs => B reads them
- - We do config.use_cache=False so no 'past_key_values'.
- - If you pass --verify_proofs, we do local batch_verify_proofs afterwards.
-"""
-
-import argparse
-import socket
-import pickle
-import time
-import os
-
-import torch
-import torch.nn as nn
-from transformers import AutoModelForCausalLM, AutoTokenizer, AutoConfig
-from peft.tuners.lora.layer import LoraLayer
-
-from zklora import batch_verify_proofs
-
-class BToAComm:
-    def __init__(self, host_a="127.0.0.1", port_a=30000):
-        self.host_a = host_a
-        self.port_a = port_a
-
-    def init_request(self):
-        data = {"request_type": "init_request"}
-        resp = self.send_and_recv(data)
-        return resp.get("injection_points", [])
-
-    def lora_forward(self, sub_name, arr):
-        req = {
-            "request_type":"lora_forward",
-            "submodule_name": sub_name,
-            "input_array": arr
-        }
-        resp = self.send_and_recv(req)
-        return resp.get("output_array", None)
-
-    def end_inference(self):
-        req = {"request_type":"end_inference"}
-        resp = self.send_and_recv(req)
-        return resp.get("proof_map", {})
-
-    def send_and_recv(self, data_dict):
-        s = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
-        s.connect((self.host_a, self.port_a))
-        bin_req = pickle.dumps(data_dict)
-        s.sendall(bin_req)
-        s.shutdown(socket.SHUT_WR)
-
-        buffer = b""
-        s.settimeout(2400.0)  # give more time if proof generation is slow
-        while True:
-            try:
-                chunk = s.recv(4096)
-            except socket.timeout:
-                break
-            if not chunk:
-                break
-            buffer += chunk
-        s.close()
-
-        if not buffer:
-            raise RuntimeError("[B] No data from A (EOF). Possibly A took too long or closed early.")
-
-        resp = pickle.loads(buffer)
-        return resp
-
-class RemoteLoRAWrappedModule(nn.Module):
[…]

### 2025-01-16 lora_contributor_sample_script.py
more consistent/clearer naming of files/classes etc w.r.t. terminology; update readme with this as well

@@ -2,7 +2,7 @@ import argparse
 import threading
 import time
 
-from zklora import LoRAServer, AServerTCP
+from zklora import LoRAServer, LoRAServerSocket
 
 def main():
     import argparse
@@ -11,12 +11,12 @@ def main():
     parser.add_argument("--port_a", type=int, default=30000)
     parser.add_argument("--base_model", default="distilgpt2")
     parser.add_argument("--lora_model_id", default="ng0-k1/distilgpt2-finetuned-es")
-    parser.add_argument("--out_dir", default="a-out")
+    parser.add_argument("--out_dir", default="proof_artifacts")
     args = parser.parse_args()
 
     stop_event = threading.Event()
     server_obj = LoRAServer(args.base_model, args.lora_model_id, args.out_dir)
-    t = AServerTCP(args.host, args.port_a, server_obj, stop_event)
+    t = LoRAServerSocket(args.host, args.port_a, server_obj, stop_event)
     t.start()
 
     try:

### 2025-01-16 zklora/__init__.py

@@ -1,11 +1,11 @@
 from .zk_proof_generator import batch_verify_proofs
-from .lora_owner_mpi import LoRAServer, AServerTCP
+from .lora_contributor_mpi import LoRAServer, LoRAServerSocket
 from .base_model_user_mpi import BaseModelClient
 
 
 __all__ = [
     'batch_verify_proofs',
     'LoRAServer',
-    'AServerTCP',
+    'LoRAServerSocket',
     'BaseModelClient',
 ]

### 2025-01-16 zklora/base_model_user_mpi/__init__.py

@@ -7,11 +7,8 @@ import os
 import torch
 import torch.nn as nn
 from transformers import AutoModelForCausalLM, AutoTokenizer, AutoConfig
-from peft.tuners.lora.layer import LoraLayer
 
-from ..zk_proof_generator import batch_verify_proofs
-
-class BToAComm:
+class BaseModelToLoRAComm:
     def __init__(self, host_a="127.0.0.1", port_a=30000):
         self.host_a = host_a
         self.port_a = port_a
@@ -61,7 +58,7 @@ class BToAComm:
         return resp
 
 class RemoteLoRAWrappedModule(nn.Module):
-    def __init__(self, sub_name, local_sub, comm: BToAComm, combine_mode="replace"):
+    def __init__(self, sub_name, local_sub, comm: BaseModelToLoRAComm, combine_mode="replace"):
         super().__init__()
         self.sub_name = sub_name
         self.local_sub = local_sub
@@ -92,7 +89,7 @@ class BaseModelClient:
 
         self.tokenizer = AutoTokenizer.from_pretrained(base_model)
 
-        self.comm = BToAComm(host_a, port_a)
+        self.comm = BaseModelToLoRAComm(host_a, port_a)
         self.combine_mode = combine_mode
 
     def _navigate(self, mod: nn.Module, parts: list[str]) -> nn.Module:

### 2025-01-16 zklora/lora_contributor_mpi/__init__.py

@@ -114,7 +114,7 @@ class LoRAServer:
 
         return
 
-class AServerTCP(threading.Thread):
+class LoRAServerSocket(threading.Thread):
     def __init__(self, host, port, lora_server: LoRAServer, stop_event):
         super().__init__()
         self.host = host

### 2025-01-16 zklora/lora_onnx_exporter.py
delete non-mpi exporter

@@ -1,270 +1,0 @@
-import json
-import os
-from typing import List
-
-import numpy as np
-import torch
-import torch.nn as nn
-from peft import PeftModel
-from transformers import PreTrainedTokenizer
-
-
-# A helper to fix shapes for A, B
-def normalize_lora_matrices(
-    A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray
-) -> tuple[torch.Tensor, torch.Tensor, int, int, int]:
-    """
-    x_data shape => (batch, seq_len, hidden_dim).
-    We ensure A => [hidden_dim, r], B => [r, out_dim].
-    """
-    in_dim = x_data.shape[-1]
-    a0, a1 = A.shape
-    # A => [in_dim, r]
-    if a0 == in_dim:
-        r = a1
-    elif a1 == in_dim:
-        A = A.transpose(0, 1)
-        r = A.shape[1]
-    else:
-        raise ValueError(f"A shape {A.shape} doesn't match x_data last dim {in_dim}.")
-
-    b0, b1 = B.shape
-    if b0 == r:
-        out_dim = b1
-    elif b1 == r:
-        B = B.transpose(0, 1)
-        out_dim = B.shape[1]
-    else:
-        raise ValueError(f"B shape {B.shape} doesn't match rank={r} in any dimension.")
-    return A, B, in_dim, r, out_dim
-
-
-class LoraShapeTransformer(nn.Module):
-    """
-    Expects shape (1, batch*seq_len*hidden_dim).
-    Internal forward => reshape to (batch, seq_len, hidden_dim).
-    """
-
-    def __init__(self, A, B, batch_size, seq_len, hidden_dim):
-        super().__init__()
-        self.register_buffer("A", A)
-        self.register_buffer("B", B)
-        self.batch_size = batch_size
-        self.seq_len = seq_len
-        self.hidden_dim = hidden_dim
-
-    def forward(self, x_1d: torch.Tensor) -> torch.Tensor:
-        # x_1d => shape (1, total_size)
-        x_3d = x_1d.view(self.batch_size, self.seq_len, self.hidden_dim)
-        out_3d = (x_3d @ self.A) @ self.B
-        out_3d = out_3d + x_3d.mean() + self.A.sum() + self.B.sum()
-        # Flatten output for demonstration
-        out_2d = out_3d.view(1, -1)
-        return out_2d
-
-
-def make_activation_hook(mod_name: str, activation_map: dict) -> callable:
[…]

### 2025-01-16 zklora/lora_onnx_exporter.py
adding back exporter to resolve conflict

@@ -1,0 +1,270 @@
+import json
+import os
+from typing import List
+
+import numpy as np
+import torch
+import torch.nn as nn
+from peft import PeftModel
+from transformers import PreTrainedTokenizer
+
+
+# A helper to fix shapes for A, B
+def normalize_lora_matrices(
+    A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray
+) -> tuple[torch.Tensor, torch.Tensor, int, int, int]:
+    """
+    x_data shape => (batch, seq_len, hidden_dim).
+    We ensure A => [hidden_dim, r], B => [r, out_dim].
+    """
+    in_dim = x_data.shape[-1]
+    a0, a1 = A.shape
+    # A => [in_dim, r]
+    if a0 == in_dim:
+        r = a1
+    elif a1 == in_dim:
+        A = A.transpose(0, 1)
+        r = A.shape[1]
+    else:
+        raise ValueError(f"A shape {A.shape} doesn't match x_data last dim {in_dim}.")
+
+    b0, b1 = B.shape
+    if b0 == r:
+        out_dim = b1
+    elif b1 == r:
+        B = B.transpose(0, 1)
+        out_dim = B.shape[1]
+    else:
+        raise ValueError(f"B shape {B.shape} doesn't match rank={r} in any dimension.")
+    return A, B, in_dim, r, out_dim
+
+
+class LoraShapeTransformer(nn.Module):
+    """
+    Expects shape (1, batch*seq_len*hidden_dim).
+    Internal forward => reshape to (batch, seq_len, hidden_dim).
+    """
+
+    def __init__(self, A, B, batch_size, seq_len, hidden_dim):
+        super().__init__()
+        self.register_buffer("A", A)
+        self.register_buffer("B", B)
+        self.batch_size = batch_size
+        self.seq_len = seq_len
+        self.hidden_dim = hidden_dim
+
+    def forward(self, x_1d: torch.Tensor) -> torch.Tensor:
+        # x_1d => shape (1, total_size)
+        x_3d = x_1d.view(self.batch_size, self.seq_len, self.hidden_dim)
+        out_3d = (x_3d @ self.A) @ self.B
+        out_3d = out_3d + x_3d.mean() + self.A.sum() + self.B.sum()
+        # Flatten output for demonstration
+        out_2d = out_3d.view(1, -1)
+        return out_2d
+
+
+def make_activation_hook(mod_name: str, activation_map: dict) -> callable:
[…]

### 2025-01-16 zklora/__init__.py
Multi-Party Inference (#22)
* initial split inference code

* fix submodule name mismatch

* separate files for user A/B

* updated split inference script (still loss discrepency)

* simple script for computing direct inference loss

* initial stage 3 + proofs (still times out after proof gen)

* make mpi with proofs into library + minimal scripts in home dir

* fix library import paths

* no longer send proof files from A -> B

* fix typo

* add independent proof verificaiton script

* remove import

* only leave imports in `__init__.py` necessary for minimal mpi sample scripts; fix verificat

@@ -1,10 +1,11 @@
-from .lora_onnx_exporter import export_lora_submodules
-from .zk_proof_generator import generate_proofs, batch_verify_proofs, ProofPaths, resolve_proof_paths
+from .zk_proof_generator import batch_verify_proofs
+from .lora_contributor_mpi import LoRAServer, LoRAServerSocket
+from .base_model_user_mpi import BaseModelClient
+
 
 __all__ = [
-    'export_lora_submodules',
-    'generate_proofs',
     'batch_verify_proofs',
-    'ProofPaths',
-    'resolve_proof_paths'
+    'LoRAServer',
+    'LoRAServerSocket',
+    'BaseModelClient',
 ]

### 2025-01-16 paper/main.tex
add bagel logo

@@
 \usepackage{xcolor}
+\usepackage[export]{adjustbox}
 \usepackage{tikz}
@@
 
-\title{\textbf{ZKLoRA: Efficient Verification of LoRA-Base Model Compatibility for Large Language Models}}
-\author{
+\title{\textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification}}
+\author{ \includegraphics[height=8em]{figs/bagel-logo-bw.png} \\
     \textbf{Bidhan Roy, Peter Potash, Marcos Villagra} \\
@@
     Parameter-efficient fine-tuning (PEFT) techniques, including Low-Rank Adaptation (LoRA), are widely adopted to customize large-scale language models in distributed training environments.
-A base model owner may outsource LoRA development to an external contributor, creating two requirements: the owner must verify that the LoRA update stems from the designated open-source model, and the contributor must protect proprietary parameters until compensation is assured.
+A base model user may want to use LoRA weights developed by an external contributor, creating two requirements: the base model user must verify that the LoRA weights are effective when combined with the designated open-source model, and the contributor must protect proprietary parameters until compensation is assured.
 
@@
 Figures~\ref{fig:proof_vs_numlora} and \ref{fig:settings_vs_numlora} similarly show that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size).
-These two steps (proof generation on the LoRA Owner’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships.
+These two steps (proof generation on the LoRA contributor’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships.
 The \emph{Base Model User}, meanwhile, benefits from the relatively short verification overhead.
@@
     \item \textbf{Base Model User} possessing a large LLM. 
-    \item \textbf{LoRA Owner} having proprietary low-rank adapter weights. 
+    \item \textbf{LoRA Contributor} having proprietary low-rank adapter weights. 
 \end{enumerate}
-However, these two parties must confirm the LoRA truly “fits” the base model. Using \texttt{ZKLoRA}, the LoRA Owner proves the adapter’s compatibility \emph{without} exposing private weights:
+However, these two parties must confirm the LoRA truly “fits” the base model. Using \texttt{ZKLoRA}, the LoRA Contributor proves the adapter’s compatibility \emph{without} exposing private weights:
 
@@
     \item \textbf{LoRA Transform + Proof Gen.}
-    The LoRA Owner applies private LoRA updates, constructing a zero-knowledge proof to attest correct usage.
+    The LoRA Contributor applies private LoRA forward passes based on partial activations, constructing a zero-knowledge proof to attest correct usage.
 
@@
     \item \textbf{Evaluate.}
-    With trust in the LoRA’s correctness, the user measures performance (e.g., loss).
+    With trust in the LoRA’s correctness, the user measures performance (e.g. loss).
 \end{enumerate}
@@
 \node[block, right=1.65cm of input] (W1) {$\mathbf{W}_1$};
-\node[dashedblock, above=1.6cm of W1, label=above:\textcolor{orange!70!black}{\textbf{LoRA Owner}}] (LoRA) {LoRA for Layer 1};
+\node[dashedblock, above=1.6cm of W1, label=above:\textcolor{orange!70!black}{\textbf{LoRA Contributor}}] (LoRA) {LoRA for Layer 1};
 \node[block, right=1.65cm of W1] (act) {ReLU};
@@
 \paragraph{(3) Witness Creation.}
-The LoRA Owner runs the partial activations through the circuit, tracking all wire values in a “witness.”
+The LoRA Contributor runs the partial activations through the circuit, tracking all wire values in a “witness.”
 
 \paragraph{(4) Proof.}
-Using the witness plus proving key, the LoRA Owner constructs a proof.
+Using the witness plus proving key, the LoRA Contributor constructs a proof.
 
@@
 This efficiency bridges the gap between privacy-preserving LoRA development and practical, real-time validation in large-scale deployments.
-Future expansions could integrate multi-owner LoRAs, advanced zero-knowledge proofs for further performance gains, or partial data-privacy frameworks to shield user inputs as well as LoRA parameters.
+Future expansions could integrate multi-contributor LoRAs, advanced zero-knowledge proofs for further performance gains, or partial data-privacy frameworks to shield user inputs as well as LoRA parameters.
 

### 2025-01-17 paper/main.tex
updated tikz figure; 2 figures -> 1 table

@@
 Our central question is how \emph{total} verification, proof generation, and settings times grow with \textbf{the number of LoRA modules} (\#LoRA), while also considering each LoRA's average parameter size.
-Figures~\ref{fig:verify_vs_numlora}, \ref{fig:proof_vs_numlora}, and \ref{fig:settings_vs_numlora} visualize this trade-off:
-\begin{itemize}
-    \item The x-axis is \textbf{the number of LoRA modules} for each model setup,
-    \item The y-axis is one of: \textit{total verification time}, \textit{total proof generation time}, or \textit{total settings time},
-    \item \textbf{Marker size} is proportional to the average LoRA size (in parameters).
-    \item The legend indicates each model’s average LoRA size with a label \textit{“Avg LoRA Size=xxK”}.
-\end{itemize}
+Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off.
 
@@
     \centering
-    \includegraphics[width=0.65\linewidth]{figs/fig_verify_vs_numlora.pdf}
+    \includegraphics[width=0.9\linewidth]{figs/fig_verify_vs_numlora.pdf}
     \caption{Total verification time (seconds) vs. number of LoRA modules, with dot size reflecting average LoRA size.}
@@
 
-\begin{figure}[ht]
+\begin{table}[h]
 \centering
-    \includegraphics[width=0.65\linewidth]{figs/fig_proof_vs_numlora.pdf}
-    \caption{Total proof generation time (seconds) vs. number of LoRA modules, with dot size reflecting average LoRA size.}
-    \label{fig:proof_vs_numlora}
-\end{figure}
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.65\linewidth]{figs/fig_settings_vs_numlora.pdf}
-    \caption{Total settings time (seconds) vs. number of LoRA modules, with dot size reflecting average LoRA size.}
-    \label{fig:settings_vs_numlora}
-\end{figure}
+\begin{tabular}{lcccc}
+\hline
+Base Model & \# of LoRAs & Avg LoRA Params & Avg Settings & Avg Proof \\
+\hline
+distilgpt2 & 24 & 24576 & 38.0 & 31.6 \\
+openai-community/gpt2 & 48 & 49152 & 43.6 & 34.9 \\
+meta-llama/Llama-3.2-1B & 32 & 26624 & 37.2 & 31.0 \\
+meta-llama/Llama-3.3-70B-Instruct & 80 & 147456 & 54.9 & 46.9 \\
+meta-llama/Llama-3.1-8B-Instruct & 32 & 163840 & 57.4 & 47.7 \\
+mistralai/Mixtral-8x7B-Instruct-v0.1 & 32 & 327680 & 86.1 & 73.7 \\
+\hline
+\end{tabular}
+\caption{Model Performance Metrics}\label{tab:settings_proof}
+\end{table}
 
@@
 
-Figures~\ref{fig:proof_vs_numlora} and \ref{fig:settings_vs_numlora} similarly show that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size).
+Table~\ref{tab:settings_proof} similarly show that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size).
 These two steps (proof generation on the LoRA contributor’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships.
@@
 
+\iffalse
 \begin{figure}[ht]
@@
 \label{fig:toy-mlp-lora}
+\end{figure}
+\fi
+
+\begin{figure}[ht]
+\centering
+\begin{tikzpicture}[
+    font=\small,
+    >=latex,
+    thick,
+    block/.style={
+      draw,
+      rounded corners,
+      align=center,
+      minimum width=2cm,
+      minimum height=1.2cm,
+      fill=blue!5
+    },
+    dashedblock/.style={
+      draw,
+      dashed,
+      rounded corners,
+      align=center,
+      fill=orange!10,
+      minimum width=2cm,
+      minimum height=1.2cm
+    },
+    sumblock/.style={
+      draw,
+      circle,
+      fill=gray!20,
+      inner sep=1pt,
+      minimum size=0.5cm
+    },
+    arrow/.style={->, thick},
+    node distance=2.5cm
+]
+
+% 1) Input x
+\node[block, label=above:\textcolor{teal}{\textbf{Input}}] (xnode) {\(\mathbf{x}\)};
+
+% 2) Local submodule (removed label)
+\node[block, right=2.5cm of xnode] (localSub) {\textbf{Wx}};
+
+% 3) Summation or aggregator (removed z label)
+\node[sumblock, right=2.5cm of localSub] (sumNode) {\(+\)};
+
+% 4) Final output
+\node[block, right=2.5cm of sumNode, 
+      label=above:\textcolor{teal}{\textbf{Final Output}}] (finalOut) {%
+\(\textbf{h}\)};
+
+% 5) The dashed remote LoRA block
+\node[dashedblock, above=1.8cm of localSub, 
+      label=above:\textcolor{orange!70!black}{\textbf{Remote LoRA}}] 
+(lora) {\(\Delta = \mathbf{BAx}\)};
+
+% ARROWS
+% x -> localSub
+\draw[->, teal!70!black] (xnode) -- node[above, font=\scriptsize]{\textbf{local forward}} (localSub);
+
+% localSub -> aggregator
+\draw[->, teal!70!black] (localSub) -- 
+   node[above, font=\scriptsize]{\(\textbf{base out}\)} (sumNode);
+
+% aggregator -> final
+\draw[->, teal!70!black] (sumNode) -- (finalOut);
+
+% x -> remote LoRA (increased font size)
+\draw[->, dashed, orange!70!black] (xnode.north) to[bend left=18]
+   node[left, font=\small]{send \(\mathbf{x}\)} (lora.west);
+
+% remote LoRA -> aggregator (increased font size)
+\draw[->, dashed, orange!70!black] (lora.east) to[bend right=15]
+   node[right, font=\small]{\(\mathbf{\Delta}\)} (sumNode.north);
+
+% Base Model box with label shifted left
+\node[
+  draw,
+  rounded corners,
+  thick,
+  color=blue!40!black,
+  fit=(xnode)(localSub)(sumNode)(finalOut),
+  label={[font=\small, color=blue!40!black, xshift=-1.5cm]above:\textbf{Base Model User}}
+] (baseBox) {};
+
+\end{tikzpicture}
+\caption{Flow in a Multi-Party Inference scenario between local base model and remote LoRA weights. 
+The base model performs a local forward pass, computing \(\mathbf{base\_out} = \mathbf{Wx}\).
+In parallel, the input \(\mathbf{x}\) is sent to the remote LoRA module, which returns \(\mathbf{\Delta} = \mathbf{BAx}\).
+The final output is \(\mathbf{base\_out} + \mathbf{\Delta}\).}
+\label{fig:remote-lora-flow}
 \end{figure}

### 2025-01-17 paper/main.tex
updated Table 1 caption, tikz figure caption; added footnote about # LoRAs per layer

@@
 We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with different numbers of LoRA modules. 
-Our central question is how \emph{total} verification, proof generation, and settings times grow with \textbf{the number of LoRA modules} (\#LoRA), while also considering each LoRA's average parameter size.
+Our central question is how verification times, as well as settings and proof generation times, grow with \textbf{the number of LoRA modules}, while also considering each LoRA's average parameter size.
 Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off.
+\footnote{Note that the number of LoRA modules in a given model is not purely a function of number of layers -- it is also a choice of which weight matrices within each layer is targeted.
+For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer, but, for example targeting the Query, Key, and Value matrices yeild three matrices per layer and makes the total number of LoRAs $3 \times num$\_$layers$.}
 
@@
 \hline
-Base Model & \# of LoRAs & Avg LoRA Params & Avg Settings & Avg Proof \\
+Base Model & \# of LoRAs & Avg LoRA Size & Avg Settings & Avg Proof \\
 \hline
@@
 \end{tabular}
-\caption{Model Performance Metrics}\label{tab:settings_proof}
+\caption{Model benchmark results for Settings and Proof generation time averaged by number of LoRA modules.}\label{tab:settings_proof}
 \end{table}
@@
 
-Table~\ref{tab:settings_proof} similarly show that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size).
+Table~\ref{tab:settings_proof} similarly shows that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size).
 These two steps (proof generation on the LoRA contributor’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships.
@@
 The base model performs a local forward pass, computing \(\mathbf{base\_out} = \mathbf{Wx}\).
-In parallel, the input \(\mathbf{x}\) is sent to the remote LoRA module, which returns \(\mathbf{\Delta} = \mathbf{BAx}\).
+In parallel, the input \(\mathbf{x}\) is sent to the remote LoRA module, which returns \(\mathbf{\Delta} = \mathbf{BAx}\), where \(\mathbf{B,A}\) are the low-rank finetuned matrices.
 The final output is \(\mathbf{base\_out} + \mathbf{\Delta}\).}

### 2025-01-17 paper/main.tex
edit footnote text

@@
 Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off.
-\footnote{Note that the number of LoRA modules in a given model is not purely a function of number of layers -- it is also a choice of which weight matrices within each layer is targeted.
-For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer, but, for example targeting the Query, Key, and Value matrices yeild three matrices per layer and makes the total number of LoRAs $3 \times num$\_$layers$.}
+\footnote{Note that the number of LoRA modules in a given model is not purely a function of the number of layers -- it is also a choice of which weight matrices within each layer is targeted.
+For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer.
+Conversely, targeting the Query, Key, and Value matrices yields three matrices per layer and makes the total number of LoRAs $3 \times num$\_$layers$.}
 

### 2025-01-17 zklora/lora_onnx_exporter.py
mv zklora to scr, sample scripts to scripts/, results csv to results/; delete so non-mpi files

@@ -1,270 +1,0 @@
-import json
-import os
-from typing import List
-
-import numpy as np
-import torch
-import torch.nn as nn
-from peft import PeftModel
-from transformers import PreTrainedTokenizer
-
-
-# A helper to fix shapes for A, B
-def normalize_lora_matrices(
-    A: torch.Tensor, B: torch.Tensor, x_data: np.ndarray
-) -> tuple[torch.Tensor, torch.Tensor, int, int, int]:
-    """
-    x_data shape => (batch, seq_len, hidden_dim).
-    We ensure A => [hidden_dim, r], B => [r, out_dim].
-    """
-    in_dim = x_data.shape[-1]
-    a0, a1 = A.shape
-    # A => [in_dim, r]
-    if a0 == in_dim:
-        r = a1
-    elif a1 == in_dim:
-        A = A.transpose(0, 1)
-        r = A.shape[1]
-    else:
-        raise ValueError(f"A shape {A.shape} doesn't match x_data last dim {in_dim}.")
-
-    b0, b1 = B.shape
-    if b0 == r:
-        out_dim = b1
-    elif b1 == r:
-        B = B.transpose(0, 1)
-        out_dim = B.shape[1]
-    else:
-        raise ValueError(f"B shape {B.shape} doesn't match rank={r} in any dimension.")
-    return A, B, in_dim, r, out_dim
-
-
-class LoraShapeTransformer(nn.Module):
-    """
-    Expects shape (1, batch*seq_len*hidden_dim).
-    Internal forward => reshape to (batch, seq_len, hidden_dim).
-    """
-
-    def __init__(self, A, B, batch_size, seq_len, hidden_dim):
-        super().__init__()
-        self.register_buffer("A", A)
-        self.register_buffer("B", B)
-        self.batch_size = batch_size
-        self.seq_len = seq_len
-        self.hidden_dim = hidden_dim
-
-    def forward(self, x_1d: torch.Tensor) -> torch.Tensor:
-        # x_1d => shape (1, total_size)
-        x_3d = x_1d.view(self.batch_size, self.seq_len, self.hidden_dim)
-        out_3d = (x_3d @ self.A) @ self.B
-        out_3d = out_3d + x_3d.mean() + self.A.sum() + self.B.sum()
-        # Flatten output for demonstration
-        out_2d = out_3d.view(1, -1)
-        return out_2d
-
-
-def make_activation_hook(mod_name: str, activation_map: dict) -> callable:
[…]

### 2025-01-17 paper/main.tex
edit conclusion -> future work outro

@@
 \texttt{ZKLoRA} provides a fast, robust mechanism to ensure that private LoRA modules remain consistent with a large base model.
-Our evaluations indicate that each LoRA module’s correctness can be verified in about 1--2 seconds, even for multi-billion-parameter LLMs.
+Our evaluations indicate that each LoRA module’s correctness can be verified in less than 2 seconds, even for multi-billion-parameter LLMs.
 This efficiency bridges the gap between privacy-preserving LoRA development and practical, real-time validation in large-scale deployments.
-Future expansions could integrate multi-contributor LoRAs, advanced zero-knowledge proofs for further performance gains, or partial data-privacy frameworks to shield user inputs as well as LoRA parameters.
+In terms of future work, the most relevant and immediate work would be adding polynomial commitments of the base model's activations (those that are sent as input to the LoRA contributor).
+This would take us one step closer to providing end-to-end verifiability of inference computation for LoRA-finetuned models.
+Other avenues of expansion could be integrating multi-contributor LoRAs, advanced zero-knowledge proofs for further performance gains, or partial data-privacy frameworks to shield user inputs as well as LoRA parameters.
 

### 2025-01-17 paper/main.tex
rough draft first figure

@@
 \end{enumerate}
+
+\begin{figure}[ht]
+\centering
+\begin{tikzpicture}[
+    font=\small,
+    >=latex,
+    thick,
+    node distance=1.6cm,
+    stepbox/.style={
+      draw,
+      rounded corners,
+      minimum width=6.2cm,
+      minimum height=2.4cm,
+      align=center,
+      fill=gray!10,
+      font=\bfseries
+    },
+    subblock/.style={
+      draw,
+      rounded corners,
+      align=center,
+      minimum width=1.6cm,
+      minimum height=0.8cm,
+      fill=gray!20,
+      font=\scriptsize
+    },
+    arrow/.style={->, thick},
+]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Step 1 BOX (Multi-Party Inference)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\node[stepbox,
+      label={[above=2pt]:{\footnotesize \textbf{Step 1: Multi-Party Inference}}}] (step1) 
+{\vspace{4pt}};  % minimal text inside, slight vertical spacing
+
+% Inside Step 1: Two sub-blocks horizontally
+\node[subblock,
+      label={[font=\scriptsize]above:{Base Model User}},
+      anchor=center, 
+      xshift=-1.6cm,
+      yshift=-0.4cm] 
+(bmuser) at (step1.center)
+{};
+
+\node[subblock,
+      label={[font=\scriptsize]above:{LoRA Contributor}},
+      anchor=center, 
+      xshift=+1.6cm,
+      yshift=-0.4cm] 
+(lorablk) at (step1.center)
+{};
+
+% Two separate arrows: "Base Acts" & "LoRA Acts"
+\draw[arrow] 
+  ([yshift=-0.05cm]bmuser.east) 
+    to[bend left=20] 
+  node[midway, above, yshift=-0.1cm, font=\scriptsize]{Base Acts}
+  ([yshift=-0.05cm]lorablk.west);
+
+\draw[arrow] 
+  ([yshift=-0.25cm]lorablk.west) 
+    to[bend right=20] 
+  node[midway, below, yshift=+0.1cm, font=\scriptsize]{LoRA Acts}
+  ([yshift=-0.25cm]bmuser.east);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Step 2 BOX (Proof Generation), below step1
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\node[stepbox, fill=orange!15, 
+      label={[above=2pt]:{\footnotesize \textbf{Step 2: Proof Generation}}}, 
+      below=of step1] (step2)
+{\footnotesize LoRA Contributor \\
+Builds Zero-Knowledge Proofs};
+
+% Arrow from step1 -> step2 with text "LoRA input/output acts"
+\draw[arrow] (step1.south) -- node[left, xshift=-0.1cm, font=\scriptsize]{LoRA input/output acts} (step2.north);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Step 3 BOX (Verification), below step2
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\node[stepbox, fill=blue!10, 
+      label={[above=2pt]:{\footnotesize \textbf{Step 3: Verification}}}, 
+      below=of step2] (step3)
+{\footnotesize Base Model User \\
+Verifies each proof};
+
+% Arrow from step2 -> step3
+\draw[arrow] (step2.south) -- node[left, font=\scriptsize]{\textit{proof files}} (step3.north);
+
+\end{tikzpicture}
+\caption{\textbf{Three-Step ZKLoRA Process (Vertical).}
+\textbf{(1)} Base Model User and LoRA Contributor exchange ``Base Acts'' and ``LoRA Acts'' in a full multi-party inference. 
+\textbf{(2)} The LoRA Contributor generates cryptographic proofs for correctness. 
+\textbf{(3)} The Base Model User verifies these proofs, ensuring correct LoRA alignment without revealing private adapter weights.}
+\label{fig:zklora_3steps}
+\end{figure}
 

### 2025-01-18 paper/main.tex
add pseudocode; convert Section 3 into dense text

@@
 \usepackage[export]{adjustbox}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{tikz}
@@
 Overall, these plots confirm that \texttt{ZKLoRA} can handle multiple LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.
-
-%------------------------------------------
-% 2. Ensuring LoRA–Base Model Compatibility with ZKLoRA
-%------------------------------------------
-\section{Ensuring LoRA–Base Model Compatibility}
-
-A typical workflow involves:
-\begin{enumerate}
-    \item \textbf{Base Model User} possessing a large LLM. 
-    \item \textbf{LoRA Contributor} having proprietary low-rank adapter weights. 
-\end{enumerate}
-However, these two parties must confirm the LoRA truly “fits” the base model. Using \texttt{ZKLoRA}, the LoRA Contributor proves the adapter’s compatibility \emph{without} exposing private weights:
-
-\begin{enumerate}
-    \item \textbf{Partial Forward Pass.}
-    The Base Model User runs the unaltered layers of the LLM, producing partial activations.
-
-    \item \textbf{LoRA Transform + Proof Gen.}
-    The LoRA Contributor applies private LoRA forward passes based on partial activations, constructing a zero-knowledge proof to attest correct usage.
-
-    \item \textbf{Verification per LoRA Module (1--2 sec).}
-    The user verifies each proof quickly, ensuring the final outputs reflect a valid LoRA for the base model.
-
-    \item \textbf{Evaluate.}
-    With trust in the LoRA’s correctness, the user measures performance (e.g. loss).
-\end{enumerate}
 
@@
 
-\iffalse
-\begin{figure}[ht]
-\centering
-\begin{tikzpicture}[
-    font=\small,
-    >=latex,
-    thick,
-    block/.style={
-      draw,
-      rounded corners,
-      align=center,
-      minimum width=1.65cm,  % Decreased from 1.8cm to 1.65cm
-      minimum height=0.9cm,
-      fill=gray!10  % Light gray background for regular blocks
-    },
-    dashedblock/.style={
-      draw,
-      dashed,
-      rounded corners,
-      align=center,
-      font=\footnotesize,
-      fill=orange!10,  % Light orange background for LoRA block
-      minimum width=1.65cm,  % Decreased to match other blocks
-      minimum height=0.9cm
-    },
-    arrow/.style={->, thick},
-    node distance=1.65cm  % Decreased from 1.8cm to 1.65cm
-]
-\node[block, label=above:\textcolor{teal}{\textbf{Input}}] (input) {$\mathbf{x}$};
-\node[block, right=1.65cm of input] (W1) {$\mathbf{W}_1$};
-\node[dashedblock, above=1.6cm of W1, label=above:\textcolor{orange!70!black}{\textbf{LoRA Contributor}}] (LoRA) {LoRA for Layer 1};
-\node[block, right=1.65cm of W1] (act) {ReLU};
-\node[block, right=1.65cm of act] (W2) {$\mathbf{W}_2$};
-\node[block, label=above:\textcolor{teal}{\textbf{Output}}, right=1.65cm of W2] (output) {$\mathbf{y}$};
-\draw[->, teal!60!black] (input) -- node[above, font=\scriptsize]{local multiply} (W1);
-\draw[->, dashed, orange!70!black] (W1.north) to[bend left=15] node[left, font=\scriptsize]{partial acts} (LoRA.south);
-\draw[->, dashed, orange!70!black] (LoRA.south) to[bend left=15] node[right, font=\scriptsize]{updated $\mathbf{z}'$} (W1.north);
-\draw[->, teal!60!black] (W1) -- node[above, font=\scriptsize]{$\mathbf{z}'$} (act);
-\draw[->, teal!60!black] (act) -- node[above, font=\scriptsize]{hidden} (W2);
-\draw[->, teal!60!black] (W2) -- (output);
-\node[draw, rounded corners, thick, color=blue!40!black,
-      fit=(input)(W1)(act)(W2)(output),
-      label={[font=\small, color=blue!40!black, xshift=2cm]above:\textbf{Base Model User}},
-      inner sep=0.6cm
-] (baseModelFit) {};
-\end{tikzpicture}
-\caption{zklora inference flow on a 2-layer neural network where the first layer has private LoRA weights added.}
-\label{fig:toy-mlp-lora}
-\end{figure}
-\fi
-
 \begin{figure}[ht]
@@
 %------------------------------------------
-% 3. HOW WE GENERATE THE ZERO-KNOWLEDGE PROOF
+% 3. ZKLoRA
 %------------------------------------------
-\section{Zero-Knowledge Proof Generation}
+\section{ZKLoRA}
+We implement a protocol that not only supports multi-party inference with partial activations exchanged between a base model user and a LoRA contributor, but also produces cryptographic proofs that the LoRA transforms are valid.
+First, the base model user processes any submodules that do not require LoRA directly on local hardware, sending partial activations only when a submodule contains LoRA-related layers.
+These exchanged activations, shown conceptually in Figure~\ref{fig:zklora_3steps}, correspond to “Base Acts” from the base model user and “LoRA Acts” from the LoRA contributor.
+Figure~\ref{fig:remote-lora-flow} also provides a fine-grained, computational perspective of what occurs when a submodule interfaces with remote LoRA weights.
 
-\texttt{ZKLoRA} compiles an ONNX model (with LoRA included) into a constraint circuit. The user’s partial activations feed the circuit as inputs:
+Once the multi-party inference completes, the LoRA contributor shifts to a proof generation phase.
+At this stage, each LoRA module is compiled into a constraint system describing the LoRA transformations, and a key setup procedure yields the proving key, verification key, and possibly a structured reference string if the underlying zero-knowledge scheme requires one.
+The contributor then creates a “witness” by running partial activations through these constraints and finally produces the proof files.
+This entire flow is summarized in Algorithm~\ref{alg:zklora_concise}, where Step 1 covers the multi-party inference, Step 2 addresses proof generation, and Step 3 handles the final verification check.
 
-\paragraph{(1) Circuit Compilation.} 
-We parse the LoRA-augmented layers, producing a cryptographic circuit capturing each parameter operation.
+Once the proof generation is done, the base model user receives each proof and runs a fast verification procedure, typically requiring about 1--2 seconds per module.
+As Figure~\ref{fig:remote-lora-flow} suggests, this does not require the LoRA contributor to reveal the actual low-rank matrices.
+Instead, the contributor only sends updates and proofs that these updates conform to the declared LoRA transformations.
+If any single proof fails, the base model user can reject the entire LoRA submission; otherwise, the system is accepted as consistent with the underlying base model.
+This design reflects the synergy between LoRA’s parameter-efficiency and zero-knowledge cryptographic protocols: LoRA significantly shrinks the parameter footprint being proven, while the zero-knowledge aspect maintains confidentiality of the contributor’s proprietary weights.
+By merging these ideas, \texttt{ZKLoRA} enables trust-driven collaboration across decentralized infrastructures, contract-based training, and other scenarios where proof-of-correctness is essential but the LoRA code remains private.
+Our approach also builds on incremental verification concepts \cite{valiant2008incrementally} and advanced proof systems such as Nova \cite{kothapalli2022nova} and HyperNova \cite{kothapalli2024hypernova}, which allow us to scale proofs to large neural networks.
+Ultimately, this combination provides a practical pipeline for parameter-efficient fine-tuning while verifying correctness in a succinct and minimally intrusive manner.
 
-\paragraph{(2) Key Setup.} 
-A settings file, proving key, and verification key are generated. A structured reference string (SRS) may also be needed.
+\begin{algorithm}[H]
+\caption{ZKLoRA Pseudocode}
+\label{alg:zklora_concise}
+\begin{algorithmic}[1]
 
-\paragraph{(3) Witness Creation.}
-The LoRA Contributor runs the partial activations through the circuit, tracking all wire values in a “witness.”
+\Require \textit{BaseModel} (public), \textit{LoRAModel} (private), \textit{Data}
+\Ensure Verified outputs or \texttt{Reject}
 
-\paragraph{(4) Proof.}
-Using the witness plus proving key, the LoRA Contributor constructs a proof.
+\Statex
 
-\paragraph{(5) Verification per Module.}
-Each LoRA module’s proof is tested with the verification key, taking \textbf{1--2 seconds}. This minimal overhead is \texttt{ZKLoRA}’s main advantage for frequent or large-scale checks.
+\State \textbf{Step 1: Multi-Party Inference}
+\For{each submodule $s$ in \textit{BaseModel}}
+  \If{$s$ \textbf{contains} LoRA layers}
+    \State \emph{(a)} run multi-party inference with LoRA Contributor for submodule $s$
+  \Else
+    \State \emph{(b)} run local inference on submodule $s$ (no remote calls)
+  \EndIf
+\EndFor
+
+\Statex
+
+\State \textbf{Step 2: Proof Generation}
+\For{each LoRA module $m$ in \textit{LoRAModel}}
+  \State \textbf{(1) Circuit Compilation:} parse LoRA-augmented layers, produce cryptographic circuit
+  \State \textbf{(2) Key Setup:} generate settings, proving key, verification key, and SRS if needed
+  \State \textbf{(3) Witness Creation:} run partial activations through circuit, record wire values
+  \State \textbf{(4) Proof:} construct zero-knowledge proof $\mathcal{P}_m$ for module $m$
+\EndFor
+
+\Statex
+
+\State \textbf{Step 3: Verification}
+\For{each proof $\mathcal{P}_m$}
+  \If{\texttt{Verify}($\mathcal{P}_m$) fails}
+    \State \textbf{return} \texttt{Reject}
+  \EndIf
+\EndFor
+
+\State \textbf{return} Verified outputs
+
+\end{algorithmic}
+\end{algorithm}
 

### 2025-01-18 paper/main.tex
abstract edit

@@
     Bagel Research Team\footnotemark[1] \\
-    \texttt{bidhan@bagel.net, peter@bagel.net, marcos@bagel.net}
 }
@@
 
-\footnotetext[1]{Bagel is a research lab, making open source AI monetizable.}
+\footnotetext[1]{Bagel is a research lab, using cryptography to make open source AI monetizable.}
 
 \begin{abstract}
-    Parameter-efficient fine-tuning (PEFT) techniques, including Low-Rank Adaptation (LoRA), are widely adopted to customize large-scale language models in distributed training environments.
-A base model user may want to use LoRA weights developed by an external contributor, creating two requirements: the base model user must verify that the LoRA weights are effective when combined with the designated open-source model, and the contributor must protect proprietary parameters until compensation is assured.
+  Low-Rank Adaptation (LoRA) is a widely adopted method for customizing large-scale language models.
+In distributed, untrusted training environments, an open source base model user may want to use LoRA weights created by an external contributor, leading to two requirements: (1) the base model user must confirm that the LoRA weights are effective when paired with the intended base model, and (2) the LoRA contributor must keep their proprietary weights private until compensation is assured.
 
-    We propose \textbf{ZKLoRA}, a zero-knowledge protocol that leverages polynomial commitments, succinct proofs, and advanced cryptographic designs to confirm LoRA–base model compatibility \emph{without} disclosing private LoRA weights.
-Our evaluations show that verification requires only \textbf{1--2 seconds} per LoRA module for typical large models.
-This short verification time enables trust-driven collaboration across decentralized infrastructures and contract-based training pipelines, ensuring that the delivered LoRA is valid while preserving the contributor’s intellectual property.
+  We present \textbf{ZKLoRA}, a zero-knowledge verification protocol that relies on polynomial commitments, succinct proofs, and multi-party inference to verify LoRA–base model compatibility without exposing LoRA weights.
+ZKLoRA produces \emph{deterministic} correctness guarantees and validates each LoRA module in \textbf{only 1--2 seconds} on statge of the art large language models.
+This low-latency approach enables nearly real-time verification and promotes secure collaboration among geographically dispersed teams and contract-based training pipelines.
+The protocol ensures that the delivered LoRA module works as claimed, safeguarding the contributor’s intellectual property while providing the base model user with verification of compatibility and lineage.
 \end{abstract}
@@
 \section{Introduction}
-Large Language Models (LLMs) have attained remarkable success \cite{brown2020language, devlin2018bert}, but verifying fine-tuned modifications such as LoRA \cite{hu2021lora} can be difficult when the updated weights must remain private.
+Large Language Models (LLMs) have attained remarkable success \cite{brown2020language, devlin2018bert}, but verifying fine-tuned modifications such as LoRA \cite{hu2021lora} in an untrusted, distributed training environment can be difficult when the updated weights must remain private.
 Traditionally, one might re-run an entire forward pass or inspect thousands of parameters to ensure correctness, which is infeasible for massive models. 
-\texttt{ZKLoRA} addresses this by generating a zero-knowledge proof of correctness for each LoRA module, guaranteeing that the private LoRA genuinely fits the public base model. 
-Crucially, \textbf{the verification stage for each LoRA module} in \texttt{ZKLoRA} remains about 1--2 seconds, even at scales of multi-billion parameter base models. 
-This rapid, per-module check allows the Base Model User to efficiently, independently verify the compatibility of the private LoRA parameters.
+\texttt{ZKLoRA} addresses this by generating a zero-knowledge proof of correctness for each LoRA module, guaranteeing that the private LoRA genuinely fits the base model. 
+Crucially, \textbf{the verification stage for each LoRA module} in \texttt{ZKLoRA} remains about 1--2 seconds, even at scales of multi-billion parameter, state of the art large language base models.
 

### 2025-01-19 paper/main.tex
readme
update paper from main
polish Figure 2; proofread through section 2

@@
 
-\title{\textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification}}
+\title{
+    \vspace*{-1.5em}
+    \rule{\textwidth}{0.4pt} \\[0.4em]
+    \textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification} \\[0.4em]
+    \rule{\textwidth}{0.4pt}
+}
 \author{ \includegraphics[height=8em]{figs/bagel-logo-bw.png} \\
@@
 
-  We present \textbf{ZKLoRA}, a zero-knowledge verification protocol that relies on polynomial commitments, succinct proofs, and multi-party inference to verify LoRA–base model compatibility without exposing LoRA weights.
-ZKLoRA produces \emph{deterministic} correctness guarantees and validates each LoRA module in \textbf{only 1--2 seconds} on statge of the art large language models.
+  We present \textbf{ZKLoRA}, a zero-knowledge verification protocol that relies on succinct proofs and multi-party inference to verify LoRA–base model compatibility without exposing LoRA weights.
+ZKLoRA produces \emph{deterministic} correctness guarantees and validates each LoRA module in \textbf{only 1--2 seconds} on state-of-the-art large language models.
 This low-latency approach enables nearly real-time verification and promotes secure collaboration among geographically dispersed teams and contract-based training pipelines.
@@
 \texttt{ZKLoRA} addresses this by generating a zero-knowledge proof of correctness for each LoRA module, guaranteeing that the private LoRA genuinely fits the base model. 
-Crucially, \textbf{the verification stage for each LoRA module} in \texttt{ZKLoRA} remains about 1--2 seconds, even at scales of multi-billion parameter, state of the art large language base models.
+Crucially, \textbf{the verification stage for each LoRA module} in \texttt{ZKLoRA} remains about 1--2 seconds, even at scales of multi-billion parameter, state-of-the-art large language base models.
 
@@
 Our central question is how verification times, as well as settings and proof generation times, grow with \textbf{the number of LoRA modules}, while also considering each LoRA's average parameter size.
-Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off.
-\footnote{Note that the number of LoRA modules in a given model is not purely a function of the number of layers -- it is also a choice of which weight matrices within each layer is targeted.
+Figure~\ref{fig:verify_vs_numlora} and Table~\ref{tab:settings_proof} detail this trade-off.\footnotemark[2]
+
+\footnotetext[2]{Note that the number of LoRA modules in a given model is not purely a function of the number of layers -- it is also a choice of which weight matrices within each layer is targeted.
 For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer.
@@
 
-Table~\ref{tab:settings_proof} similarly shows that \emph{proof generation} and \emph{settings time} scale with the number of LoRA modules, but also depend heavily on each module’s average size (indicated by larger or smaller dot size).
+Table~\ref{tab:settings_proof} similarly shows that average \emph{proof generation} and \emph{settings time} scale with the size of a LoRA module, which, combined with the number of modules, gives the total times.
 These two steps (proof generation on the LoRA contributor’s side and cryptographic circuit setup) can become more expensive, yet remain feasible in decentralized settings or paid contract relationships.
@@
 
-Overall, these plots confirm that \texttt{ZKLoRA} can handle multiple LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.
+Overall, these plots confirm that \texttt{ZKLoRA} can handle large-scale implementation of LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.
 
@@
       minimum width=6.2cm,
-      minimum height=2.4cm,
+      minimum height=3.2cm,
       align=center,
@@
     arrow/.style={->, thick},
+    % Define a style for the vertical arrow labels
+    arrowlabel/.style={
+      font=\footnotesize\sffamily\bfseries,
+      fill=white,
+      text=black,
+      inner sep=1pt
+    }
 ]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\node[stepbox,
-      label={[above=2pt]:{\footnotesize \textbf{Step 1: Multi-Party Inference}}}] (step1) 
-{\vspace{4pt}};  % minimal text inside, slight vertical spacing
+\node[stepbox] (step1) {%
+  \footnotesize \textbf{Step 1: Multi-Party Inference}\\[6pt]
+  \vspace{10pt}
+};
 
-% Inside Step 1: Two sub-blocks horizontally
+% Sub-blocks within Step 1
 \node[subblock,
@@
       xshift=-1.6cm,
-      yshift=-0.4cm] 
-(bmuser) at (step1.center)
+      yshift=-1.0cm] (bmuser) at (step1.center)
 {};
@@
       xshift=+1.6cm,
-      yshift=-0.4cm] 
-(lorablk) at (step1.center)
+      yshift=-1.0cm] (lorablk) at (step1.center)
 {};
 
-% Two separate arrows: "Base Acts" & "LoRA Acts"
+% Horizontal arrows in Step 1 (unchanged)
 \draw[arrow] 
@@
     to[bend right=20] 
-  node[midway, below, yshift=+0.1cm, font=\scriptsize]{LoRA Acts}
+  node[midway, below, yshift=-0.05cm, font=\scriptsize]{LoRA Acts}
   ([yshift=-0.25cm]bmuser.east);
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Step 2 BOX (Proof Generation), below step1
+% Step 2 BOX (Proof Generation)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\node[stepbox, fill=orange!15, 
-      label={[above=2pt]:{\footnotesize \textbf{Step 2: Proof Generation}}}, 
-      below=of step1] (step2)
-{\footnotesize LoRA Contributor \\
-Builds Zero-Knowledge Proofs};
+\node[stepbox, fill=orange!15, below=of step1] (step2) {%
+  \footnotesize \textbf{Step 2: Proof Generation}\\[6pt]
+  \footnotesize LoRA Contributor\\
+  Builds Zero-Knowledge Proofs
+};
 
-% Arrow from step1 -> step2 with text "LoRA input/output acts"
-\draw[arrow] (step1.south) -- node[left, xshift=-0.1cm, font=\scriptsize]{LoRA input/output acts} (step2.north);
+% Vertical arrow from Step 1 to Step 2 with new style
+\draw[arrow, shorten >=8pt, shorten <=8pt] (step1.south)
+  -- node[arrowlabel, left, xshift=-0.1cm]{LoRA input/output acts}
+  (step2.north);
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Step 3 BOX (Verification), below step2
+% Step 3 BOX (Verification)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\node[stepbox, fill=blue!10, 
-      label={[above=2pt]:{\footnotesize \textbf{Step 3: Verification}}}, 
-      below=of step2] (step3)
-{\footnotesize Base Model User \\
-Verifies each proof};
+\node[stepbox, fill=blue!10, below=of step2] (step3) {%
+  \footnotesize \textbf{Step 3: Verification}\\[6pt]
+  \footnotesize Base Model User\\
+  Verifies each proof
+};
 
-% Arrow from step2 -> step3
-\draw[arrow] (step2.south) -- node[left, font=\scriptsize]{\textit{proof files}} (step3.north);
+% Vertical arrow from Step 2 to Step 3 with new style
+\draw[arrow, shorten >=8pt, shorten <=8pt] (step2.south)
+  -- node[arrowlabel, left, xshift=-0.1cm]{proof files}
+  (step3.north);
 
@@
 \caption{\textbf{Three-Step ZKLoRA Process (Vertical).}
-\textbf{(1)} Base Model User and LoRA Contributor exchange ``Base Acts'' and ``LoRA Acts'' in a full multi-party inference. 
+\textbf{(1)} Base Model User and LoRA Contributor exchange “Base Acts” and “LoRA Acts” in a multi-party inference.
 \textbf{(2)} The LoRA Contributor generates cryptographic proofs for correctness.

### 2025-01-20 paper/main.tex
revised section 3

@@
 
-Overall, these plots confirm that \texttt{ZKLoRA} can handle large-scale implementation of LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.
+Overall, these results confirm that \texttt{ZKLoRA} can handle large-scale implementation of LoRA modules with minimal overhead for verifying correctness, emphasizing the viability of repeated or multi-adapter scenarios in large-scale LLM pipelines.
 
@@
 \section{ZKLoRA}
+\texttt{ZKLoRA}'s design reflects the synergy between LoRA’s parameter-efficiency and zero-knowledge cryptographic protocols: LoRA significantly shrinks the parameter footprint being proven, while the zero-knowledge aspect maintains confidentiality of the contributor’s proprietary weights.
+By merging these ideas, \texttt{ZKLoRA} enables trust-driven collaboration across decentralized infrastructures, contract-based training, and other scenarios where proof-of-correctness is essential but the LoRA code remains private.
+Our approach also builds on incremental verification concepts \cite{valiant2008incrementally} and advanced proof systems such as Nova \cite{kothapalli2022nova} and HyperNova \cite{kothapalli2024hypernova}, which allow us to scale proofs to large neural networks.
+Ultimately, this combination provides a practical pipeline for parameter-efficient fine-tuning while verifying correctness in a succinct and minimally intrusive manner.
+
 We implement a protocol that not only supports multi-party inference with partial activations exchanged between a base model user and a LoRA contributor, but also produces cryptographic proofs that the LoRA transforms are valid.
-First, the base model user processes any submodules that do not require LoRA directly on local hardware, sending partial activations only when a submodule contains LoRA-related layers.
+The overall workflow is shown in Figure~\ref{fig:zklora_3steps}, while Figure~\ref{fig:remote-lora-flow} gives a deeper look at how Multi-Party Inference with LoRAs functions within an individual module.
+In addition, pseudocode for \texttt{ZKLoRA} is in Algorithm~\ref{alg:zklora}.
+To begin the Multi-Party Inference, the base model user puts the dataset chosen for inference into the base model's first module.
+The forward pass continues through until the base model until it hits a module that uses remote LoRA weights.
+When this occurs the base model user sends partial activations to the LoRA contributor for processing.
+These exchanged activations, shown conceptually in Figure~\ref{fig:zklora_3steps}, correspond to “Base Acts” from the base model user and “LoRA Acts” from the LoRA contributor.
+%processes any submodules that do not require LoRA directly on local hardware, sending partial activations only when a submodule contains LoRA-related layers.
 These exchanged activations, shown conceptually in Figure~\ref{fig:zklora_3steps}, correspond to “Base Acts” from the base model user and “LoRA Acts” from the LoRA contributor.
@@
 
-Once the multi-party inference completes, the LoRA contributor shifts to a proof generation phase.
+After the multi-party inference finishes, the LoRA contributor shifts to a proof generation phase.
 At this stage, each LoRA module is compiled into a constraint system describing the LoRA transformations, and a key setup procedure yields the proving key, verification key, and possibly a structured reference string if the underlying zero-knowledge scheme requires one.
 The contributor then creates a “witness” by running partial activations through these constraints and finally produces the proof files.
-This entire flow is summarized in Algorithm~\ref{alg:zklora_concise}, where Step 1 covers the multi-party inference, Step 2 addresses proof generation, and Step 3 handles the final verification check.
+%This entire flow is summarized in Algorithm~\ref{alg:zklora_concise}, where Step 1 covers the multi-party inference, Step 2 addresses proof generation, and Step 3 handles the final verification check.
 
@@
 If any single proof fails, the base model user can reject the entire LoRA submission; otherwise, the system is accepted as consistent with the underlying base model.
-This design reflects the synergy between LoRA’s parameter-efficiency and zero-knowledge cryptographic protocols: LoRA significantly shrinks the parameter footprint being proven, while the zero-knowledge aspect maintains confidentiality of the contributor’s proprietary weights.
-By merging these ideas, \texttt{ZKLoRA} enables trust-driven collaboration across decentralized infrastructures, contract-based training, and other scenarios where proof-of-correctness is essential but the LoRA code remains private.
-Our approach also builds on incremental verification concepts \cite{valiant2008incrementally} and advanced proof systems such as Nova \cite{kothapalli2022nova} and HyperNova \cite{kothapalli2024hypernova}, which allow us to scale proofs to large neural networks.
-Ultimately, this combination provides a practical pipeline for parameter-efficient fine-tuning while verifying correctness in a succinct and minimally intrusive manner.
 
@@
 \end{algorithmic}
+\caption{\texttt{ZKLoRA} Pseudocode }
+\label{alg:zklora}
 \end{algorithm}

### 2025-01-20 paper/main.tex
(potentially) final touch-ups

@@
 We benchmarked \texttt{ZKLoRA} across several LLMs and smaller models with different numbers of LoRA modules.
+The input for inference is a batch of size 3 with sequence length 5.
 Our central question is how verification times, as well as settings and proof generation times, grow with \textbf{the number of LoRA modules}, while also considering each LoRA's average parameter size.
@@
 \footnotetext[2]{Note that the number of LoRA modules in a given model is not purely a function of the number of layers -- it is also a choice of which weight matrices within each layer is targeted.
-For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yeild one LoRA per layer.
+For example, just targeting one matrix per layer (ie the Query matrix in the Attention Block) will yield one LoRA per layer.
 Conversely, targeting the Query, Key, and Value matrices yields three matrices per layer and makes the total number of LoRAs $3 \times num$\_$layers$.}
@@
 \begin{algorithm}[H]
-\caption{ZKLoRA Pseudocode}
-\label{alg:zklora_concise}
+\caption{\texttt{ZKLoRA} Pseudocode}
+\label{alg:zklora}
 \begin{algorithmic}[1]
@@
 \end{algorithmic}
-\caption{\texttt{ZKLoRA} Pseudocode }
-\label{alg:zklora}
 \end{algorithm}
@@
 In a seminal paper by Valiant (2008) \cite{valiant2008incrementally}, it was shown that proofs of knowledge can be used to assert the correct execution of general computations.
-That is, if $M$ is a machine that runs for $t$ steps producing a sequence of configurations $c_0,c_1,\dots,c_t$, then there exist an efficient and effective way to produce a computationally sound proof for the computation $c_0  \xrightarrow{t} c_t$.
+That is, if $M$ is a machine that runs for $t$ steps producing a sequence of configurations $c_0,c_1,\dots,c_t$, then there exists an efficient and effective way to produce a computationally sound proof for the computation $c_0  \xrightarrow{t} c_t$.
 This idea is referred to as Incrementally Verifiable Computation or IVC.
@@
 
-\texttt{ZKLoRA} provides a fast, robust mechanism to ensure that private LoRA modules remain consistent with a large base model.
-Our evaluations indicate that each LoRA module’s correctness can be verified in less than 2 seconds, even for multi-billion-parameter LLMs.
+\texttt{ZKLoRA} provides a fast, robust mechanism to ensure that private LoRA modules remain effective when combined with a large base model.
+Our evaluations indicate that each LoRA module’s forward computation can be verified in less than 2 seconds, even for multi-billion-parameter LLMs.
 This efficiency bridges the gap between privacy-preserving LoRA development and practical, real-time validation in large-scale deployments.
-In terms of future work, the most relevant and immediate work would be adding polynomial commitments of the base model's activations (those that are sent as input to the LoRA contributor).
+In terms of future work, the most relevant and immediate work would be adding polynomial commitments of the base model's activations (those that are sent as input to the LoRA Contributor).
 This would take us one step closer to providing end-to-end verifiability of inference computation for LoRA-finetuned models.

### 2025-01-20 paper/main.tex
geographically decentralized

@@
 ZKLoRA produces \emph{deterministic} correctness guarantees and validates each LoRA module in \textbf{only 1--2 seconds} on state-of-the-art large language models.
-This low-latency approach enables nearly real-time verification and promotes secure collaboration among geographically dispersed teams and contract-based training pipelines.
+This low-latency approach enables nearly real-time verification and promotes secure collaboration among geographically decentralized teams and contract-based training pipelines.
 The protocol ensures that the delivered LoRA module works as claimed, safeguarding the contributor’s intellectual property while providing the base model user with verification of compatibility and lineage.

### 2025-01-20 paper/main.tex

@@
 
-  We present \textbf{ZKLoRA}, a zero-knowledge verification protocol that relies on succinct proofs and multi-party inference to verify LoRA–base model compatibility without exposing LoRA weights.
+  We present \textbf{ZKLoRA}, a zero-knowledge verification protocol that relies on succinct proofs and our novel Multi-Party Inference procedure to verify LoRA–base model compatibility without exposing LoRA weights.
 ZKLoRA produces \emph{deterministic} correctness guarantees and validates each LoRA module in \textbf{only 1--2 seconds} on state-of-the-art large language models.

### 2025-01-21 src/zklora/lora_contributor_mpi/__init__.py
load base model for lora contributor with `from_pretrained` (#38)

@@ -38,11 +38,10 @@ class LoRAServer:
         self.out_dir = out_dir
         os.makedirs(self.out_dir, exist_ok=True)
 
-        # 1) Load model config, disable cache => no 'past_key_values'
-        config = AutoConfig.from_pretrained(base_model_name)
-        config.use_cache = False
-        base_model = AutoModelForCausalLM.from_config(config)
+        # 1) Load model, disable cache => no 'past_key_values'
+        base_model = AutoModelForCausalLM.from_pretrained(base_model_name)
         base_model.config.use_cache = False
+
         base_model.eval()
 
         # 2) Load LoRA
